### 2015-10-17 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
alles mal auf den neuesten

%\textsl{}%!TEX TS-options = --shell-escape
%!TEX TS-program = pdflatex
\documentclass[%
   10pt,              % Schriftgroesse
   ngerman,           % wird an andere Pakete weitergereicht
   a4paper,           % Seitengroesse
   DIV11,             % Textbereichsgroesse (siehe Koma Skript Dokumentation !)
]{scrartcl}%     Klassen: scrartcl, scrreprt, scrbook, article
% -------------------------------------------------------------------------

\usepackage[utf8]{inputenc} % Font Encoding, benoetigt fuer Umlaute
\usepackage[english]{babel}   % \textsl{}Spracheinstellung

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
\usepackage{TikZ} %phylogenetischer Baum
\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

% Definition des Headers
\usepackage{geometry}
\geometry{a4paper, top=3cm, left=3cm, right=3cm, bottom=3cm, headsep=0mm, footskip=0mm}
\renewcommand{\baselinestretch}{1.3}\normalsize

\def\header#1#2#3#4#5#6#7{\pagestyle{empty}
\noindent
\begin{minipage}[t]{0.6\textwidth}
\begin{flushleft}
\textbf{#4}\\% Fach
#6\\% Semester
Tutor: #2  % Tutor 
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright}
\points{#7}% Punktetabelle
\vspace*{0.2cm}
#5%  Names
\end{flushright}
\end{minipage}

\begin{center}
{\Large\textbf{ Blatt #1}} % Blatt

{(Abgabe am #3)} % Abgabedatum
\end{center}
}

\newenvironment{vartab}[1]
{
    \begin{tabular}{ |c@{} *{#1}{c|} } %\hline
}{
    \end{tabular}
}

\newcommand{\myformat}[1]{& #1}

\newcommand{\entry}[1]{
  \edef\result{\csvloop[\myformat]{#1}}
  \result \\ \hline
}

\newcommand{\numbers}[1]{
  \newcounter{ctra}
\setcounter{ctra}{1}
\whiledo {\value{ctra} < #1}%
{%
  \myformat{\thectra}
  \stepcounter{ctra}%
}
\myformat{\thectra}
}
\newcommand{\emptyLine}[1]{
  \newcounter{ctra1}
\setcounter{ctra}{1}
\whiledo {\value{ctra1} < #1}%
{%
  \myformat{\hspace*{0.5cm}}
  \stepcounter{ctra1}%
}
}

\newcommand{\points}[1]{
\newcounter{colmns}
\setcounter{colmns}{#1}
\stepcounter{colmns}
  \begin{vartab}{\thecolmns}
    \numbers{#1} & $\sum$\\\hline
    \emptyLine{\thecolmns}\\
  \end{vartab}
}

\begin{document}
%\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
\header{7}{Alexander Seitz}{19. October 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}

  \section*{Exercise 1 - \textsl{}}

  \section*{Exercise 2 - \textsl{DP Algorithm for finding motifs}}
  \emph{for} i = 0 \emph{to} \emph{length}(X)\\
  \indent \emph{if} X[i] == Y[0]\\
  \indent \indent Score = 0
  \indent \indent \emph{for} j = 0 \emph{to} \emph{length}(Y)\\
  \indent \indent \indent \emph{if} (X[i+j] == Y[j]) Score += 1\\
  \indent \indent if (Score > T) 
  \indent \indent \indent \emph{print}(motif found at position i)
  \indent \indent \indent i += \emph{length}(Y)

  \section*{Exercise 3 - \textsl{Programming assignment: Needleman-Wunsch alignment}}
  One task was to handle command line options. We wrote a new class to have a modular 
  and easy way to provide this functionality. The java package \textit{args4j} has everything
  we need. So we used that package to write our own option handler class. The code can 
  be found in \textit{CommandLineParser.java}. We did the same with gap penalties. A
  gap penalty class gives one the advantage of modular gap handling. If a gap penalties are
  needed, just reuse this class.\\
  A new member function of our NeedlemanWunsch class takes care of file writing. If a user 
  wants the resulting alignment in a FastA file, this function takes care of it.

\end{document}

### 2015-10-17 Material/NW_Code/CommandLineParser.java

@@ -13,14 +13,14 @@ import org.kohsuke.args4j.Option;
 
 public class CommandLineParser {
 
-    @Option(name="-i1", usage="input file, which stores the first sequence")
+    @Option(name="-i1", usage="input file, which stores the first sequence", required=true)
     private File inSeq1;
 
-    @Option(name="-i2", usage="input file, which stores the second sequence")
+    @Option(name="-i2", usage="input file, which stores the second sequence", required=true)
     private File inSeq2;
 
     @Option(name="-o", usage="output to this file")
-    private File out = new File(".");
+    private String out;
 
     @Option(name="-open", usage="set gap open penalty\nIf linear gap costs are used, this is the gap penalty")
     private int gapOpenPenalty = 1;

### 2015-10-17 Material/NW_Code/GapPenalty.java

@@ -40,7 +40,7 @@ public class GapPenalty {
       * set gap opening cost
       * @param gapOpening
       */
-     public void setOpeningCost(int gapOpening) {
+     public void setGapOpening(int gapOpening) {
          this.gapOpening = gapOpening;
      }
 
@@ -48,7 +48,7 @@ public class GapPenalty {
       * set gap extension cost
       * @param gapExtension
       */
-     public void setExtensionCost(int gapExtension) {
+     public void setGapExtension(int gapExtension) {
          this.gapExtension = gapExtension;
      }
 

### 2015-10-17 Material/NW_Code/NeedlemanWunsch.java

@@ -181,4 +181,30 @@ public class NeedlemanWunsch extends NeedlemanWunschBase {
 		else
 			return 4;
 	}
+
+    /**
+     * This funktion provide a easy way to write a computed alignment into a fasta file
+     * @param outFile
+     * @param single
+     */
+    public void writeAlignment(String outFile, boolean single) {
+        File outputFile = new File(outFile);
+        output = new BufferedWriter(new FileWriter(outputFile));
+        if(single) {
+            output.write(">SEQUENCE_1|Score:"); output.write(this.score); output.newLine();
+            output.write(this.aligned1[0]); output.newLine();
+            output.write(">SEQUENCE_2|Score:"); output.write(this.score); output.newLine();
+            output.write(this.aligned2[0]);
+        }else {
+            for(int i = 0; i < this.aligned1.size(); i++) {
+                output.write(">SEQUENCE_1|Alignment:"); output.write(i+1);
+                output.write("|Score:"); output.write(this.score); output.newLine();
+                output.write(this.aligned1[0]); output.newLine();
+                output.write(">SEQUENCE_2|Alignment:"); output.write(i+1);
+                output.write("|Score:"); output.write(this.score); output.newLine();
+                output.write(this.aligned2[0]); output.newLine();
+            }
+        }
+    }
+
 }

### 2015-10-17 Material/NW_Code/RunNeedlemanWunsch.java

@@ -20,30 +20,21 @@ public class RunNeedlemanWunsch {
      * @throws Exception
      */
     static public void main (String[] args) throws Exception {
-        if(args.length!=5)
-            throw new Exception("Usage: file1 file2 matchscore mismatchscore gappenalty");
         
-        /*
-         * \TODO
-         * Adapt this class such that it accepts command line switches
-         * e.g.
-         * -i		for input files
-         * -d		for gap penalty
-         * -ms		for match score
-         * -mms		for mismatch score
-         * -single	only output one best alignment
-         * -all		output all best alignments
-         * -o		write output to a fasta file instead of system.out
-         * 			in this case the alingments should be writen in fasta-format +
-         * 			store the score of the alignment in the header of each fasta entry
-         * -?		provide helpful usage information
-         */
-        
+        CommandLineParser options = new CommandLineParser(args);
+        CmdLineParser parser = new CmdLineParser(options);
+
+        try {
+            parser.parseArgument(args);
+        } catch (CmdLineException e) {
+            System.exit(1);
+        }
+
         FastA fasta1 = new FastA();
-        fasta1.read(new BufferedReader(new FileReader(new File(args[0]))));
+        fasta1.read(new BufferedReader(new FileReader(options.getSeq1())));
         
         FastA fasta2 = new FastA();
-        fasta2.read(new BufferedReader(new FileReader(new File(args[1]))));
+        fasta2.read(new BufferedReader(new FileReader(options.getSeq2())));
 
         // setup algorithm parameters:
         NeedlemanWunsch nw = new NeedlemanWunsch();
@@ -53,9 +44,9 @@ public class RunNeedlemanWunsch {
         nw.setSequence2(fasta2.getSequence(0));
 
         //set match, mismatch score and gap penalty
-        nw.setMatchScore(Integer.parseInt(args[2]));
-        nw.setMismatchScore(Integer.parseInt(args[3]));
-        nw.setGapPenalty(Integer.parseInt(args[4]));
+        nw.setMatchScore(options.getMatchScore());
+        nw.setMismatchScore(options.getMismatchScore());
+        nw.setGapPenalty(options.getOpeningCost());
 
         // display input
         System.out.println("Input:");
@@ -66,16 +57,31 @@ public class RunNeedlemanWunsch {
         // run algorithm
         nw.compute();
 
-     // display all possible optimal alignments
[…]

### 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
first citation ;)

@@
 
-  \section*{Exercise 1 - \textsl{}}
+  \section*{Exercise 1 - \textsl{Smith Waterman today}}
+	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics.
+This algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence.
+But the dynamic programmed algorithm has to face the problem of complexity of $O(n\times m)$.
+This complexity is getting a problem when starting to compare large sequences or even whole genomes.
+	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. \cite{blast}
 
@@
 
+\begin{thebibliography}{widestlabel}
+	\bibitem[Li, H., Homer, N.]{blast} 	
+	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
+\end{thebibliography}
+
 \end{document}

### 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
tzext text text

@@
 	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics.
-This algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence.
-But the dynamic programmed algorithm has to face the problem of complexity of $O(n\times m)$.
+This dynamic programming (DP) algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence.
+But the algorithm has to face the problem of complexity of $O(n\times m)$.
 This complexity is getting a problem when starting to compare large sequences or even whole genomes.
-	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. \cite{blast}
+Still today has this algorithm a high importance in bioinformatics, which can be seen in the following examples.
+	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm.
+Which uses algorithm for seed refinement.
+Thereby the algorithm is accelerated with vectorization process.
+Basically this is an improvment on the hardwarelevel of a computer, which can be adressed by the software for parallelizing the alignment.
+As a result, the Smith-Waterman algorithm is accelerated by a factor of 10 in comparison to the standard algorithm Novoalign (http://novocraft.com).
+Also an advantage in complexity mattes is constraining the algorithm around seeds from the seeding step.
+	   \cite{blast}
+	  Parallelizing is general a very modern topic for Smith-Waterman Algorithms.
+Some research groups try to accelerate the algorithm by paralelizing the algorithm via a heterogeneous platform.
+On this platform they use the graphics processing unit and the central processing unit for an enhanced speed of the algorithm.
+	  \cite{parallel}
 
@@
 	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
+	\bibitem[Chen, B. and Xu, Y. et al]{parallel} 		
+		Chen, B.
+and Xu, Y.
+and Yang, J.
+and Jiang, H.
+(2010).
+A New Parallel Method of Smith-Waterman Algorithm on a Heterogeneous Platform.
+Springer.
+Algorithms and Architectures for Parallel Processing.79–90
 \end{thebibliography}

### 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
Excercise 1 finished

--- 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
@@
 	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics.
-This algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence.
-But the dynamic programmed algorithm has to face the problem of complexity of $O(n\times m)$.
+This dynamic programming (DP) algorithm allows in a biological sense for example the detection of Domains in a protein or a protein in a larger sequence.
+But the algorithm has to face the problem of time and space complexity of $O(n\times m)$.
 This complexity is getting a problem when starting to compare large sequences or even whole genomes.
-	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. \cite{blast}
+In the paper of Sandes et al., there is a model, which describes the problems of the space complexity as follows:"  For instance, in order to compare two 33 MBP (Million Base Pairs) sequences, we would need at least
+	  4.3 PB of memory." \cite{GPU} which was shown by D. Hirschberg \cite{algoritm}. This amount of space is at least today a major problem.
+
+	  But the SW-algorithm has still a high importance in bioinformatics, which can be seen in the following examples.
+	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm.
+Which uses the algorithm for seed refinement.
+Thereby the algorithm is accelerated with a vectorization process.
+Basically this is an improvment on the hardwarelevel of a computer, which can be adressed by the software for parallelizing the alignment.
+As a result, the Smith-Waterman algorithm is accelerated by a factor of 10 in comparison to the standard algorithm Novoalign (http://novocraft.com).
+Also an advantage in complexity matters is constraining the algorithm around seeds from the seeding step.
+	   \cite{blast}
+
+	  Parallelizing is general a very modern topic for the Smith-Waterman Algorithm.
+Some research groups try to accelerate the algorithm by parallelizing the algorithm via the usage of the graphics processing unit (GPU).
+Some of the prominent algorithms are the CUDAlign1.0 \cite{CUD} or the Weiguo Liu algorithm \cite{Liu}.
+The CUDAlign Algorithm for example can align up to 32 MBP x 47 MBP.
+	  \cite{GPU}
 
@@
 	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
+	\bibitem[Chen, B. and Xu, Y. et al]{parallel} 		
+		Chen, B.
+and Xu, Y.
+and Yang, J.
+and Jiang, H.
+(2010).
+A New Parallel Method of Smith-Waterman Algorithm on a Heterogeneous Platform.
+Springer.
+Algorithms and Architectures for Parallel Processing.79–90
+	\bibitem[Edans Flavius de O. Sandes, Alba Cristina M.A. de Melo]{GPU} 	
+	Edans Flavius de O.
+Sandes, Alba Cristina M.A.
+de Melo (2013), "Retrieving Smith-Waterman Alignments with Optimizations for Megabase Biological Sequences Using GPU", IEEE Transactions on Parallel \& Distributed Systems, vol.24, no.
+5, pp.
+1009-1021, doi:10.1109/TPDS.2012.194
+	\bibitem[D.S. Hirschberg,]{algoritm}
+	D.S. Hirschberg, “A Linear Space Algorithm for Computing Maximal Common Subsequences,” Comm. ACM, vol. 18, no. 6, pp. 341-343, 1975
+
+	\bibitem[Sandes, E.F. de and Melo A.C.M.A. de]{CUD}
+	E.F. de, O. Sandes, and A.C.M.A. de Melo.(2010) “CUDAlign: Using GPU to Accelerate the Comparison of Megabase Genomic Sequence,”.	Proc. 15th ACM SIGPLAN Symp. Principles and Practice
+	of Parallel Programming (PPoPP). pp. 137-146
+	\bibitem[W. Liu, B. Schmidt, G. Voss et al]{Liu}
+	W. Liu, B. Schmidt, G. Voss, A. Schroder, and W. Muller-Wittig. (2006). “Bio-Sequence Database Scanning on a GPU”.	Proc. 20th Int’l Conf. Parallel and Distributed Processing (IPDPS).
 	\end{thebibliography}

### 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
kleine veränderung am tex file

--- 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
@@
 
-  \section*{Exercise 1 - \textsl{Smith Waterman today}}
-	  The 30 years old Smith-Waterman (SW) algorithm is one of the fundamental algorithms in bioinformatics.
-This algorithm allows in a biological sense for example the detection of Domains in a protein or a Protein in a larger sequence.
-But the dynamic programmed algorithm has to face the problem of complexity of $O(n\times m)$.
-This complexity is getting a problem when starting to compare large sequences or even whole genomes.
-	  The classical example for todays usage of the Smith Waterman algorithm is the BLAST algorithm. \cite{blast}
+  \section*{Exercise 1 - \textsl{}}
 
@@
   A new member function of our NeedlemanWunsch class takes care of file writing. If a user 
-  wants the resulting alignment in a FastA file, this function takes care of it.
-
-\begin{thebibliography}{widestlabel}
-	\bibitem[Li, H., Homer, N.]{blast} 	
-	Li, H., Homer, N. (2010). A survey of sequence alignment algorithms for next-generation sequencing. Briefings in Bioinformatics, 11(5), 473–483. http://doi.org/10.1093/bib/bbq015
-\end{thebibliography}
+  wants the resulting alignment in a FastA file, this function takes care of it. To fullfil 
+  that task it uses a BufferedWriter and FileWriter.
 

### 2015-10-19 Assignment II/Assignment1-Ditz_Schroeder-WS15-16.tex
Start_AssignmentII

--- 2015-10-18 Assignment I/Assignment1-Ditz_Schroeder-WS15-16.tex
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{7}{Alexander Seitz}{19. October 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
+\header{7}{Alexander Seitz}{26. October 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
 
@@
 
-  \section*{Exercise 2 - \textsl{DP Algorithm for finding motifs}}
-  \emph{for} i = 0 \emph{to} \emph{length}(X)\\
-  \indent \emph{if} X[i] == Y[0]\\
-  \indent \indent Score = 0
-  \indent \indent \emph{for} j = 0 \emph{to} \emph{length}(Y)\\
-  \indent \indent \indent \emph{if} (X[i+j] == Y[j]) Score += 1\\
-  \indent \indent if (Score > T) 
-  \indent \indent \indent \emph{print}(motif found at position i)
-  \indent \indent \indent i += \emph{length}(Y)
-
-  \section*{Exercise 3 - \textsl{Programming assignment: Needleman-Wunsch alignment}}
-  One task was to handle command line options. We wrote a new class to have a modular 
-  and easy way to provide this functionality. The java package \textit{args4j} has everything
-  we need. So we used that package to write our own option handler class. The code can 
-  be found in \textit{CommandLineParser.java}. We did the same with gap penalties. A
-  gap penalty class gives one the advantage of modular gap handling. If a gap penalties are
-  needed, just reuse this class.\\
-  A new member function of our NeedlemanWunsch class takes care of file writing. If a user 
-  wants the resulting alignment in a FastA file, this function takes care of it. To fullfil 
-  that task it uses a BufferedWriter and FileWriter.
-
 \end{document}

### 2015-10-21 Assignment II/Exercise_2-script-Benni.R
changes

@@ -14,3 +14,8 @@ PAMN<- read.table(file=paste0(basicPath,"material/substitution_matrices/PAMN.txt
   sumPAM250 <- sum(PAM250[0:20,0:20])/400
   sumPAMN <- sum(PAMN[0:20,0:20])/400
 
+  sumBLOSUM50aX <- sum(BLOSUM50[0:20,0:20])/400
+  sumBLOSUM62aX <- sum(BLOSUM62[0:20,0:20])/400
+  sumBLOSUM80aX <- sum(BLOSUM80[0:20,0:20])/400
+  sumPAM250aX <- sum(PAM250[0:20,0:20])/400
+  sumPAMNaX <- sum(PAMN[0:20,0:20])/400

### 2015-10-22 Assignment I/Material/NW_Code/CommandLineParser.java
pictureeeeeeeeeeeeees

@@ -27,7 +27,7 @@ public class CommandLineParser {
     private int gapOpenPenalty = 1;
 
     @Option(name="-epen", usage="set gap extention penalty")
-    private int gapExtPenalty = 0;
+    private int gapExtPenalty;
 
     @Option(name="-m", usage="set the score of a match")
     private int match = 1;

### 2015-10-22 Assignment I/Material/NW_Code/GapPenalty.java

@@ -72,5 +72,14 @@ public class GapPenalty {
        else if (affine & !gapOpen) return gapExtension;
        else return gapOpening;
      }
-    
+
+     /**
+      * get initialize gap costs
+      * @param index
+      * @return cost
+      */
+     public getInitCost(int index) {
+    	if(affine) return -(index-1)*this.gapExtension - this.gapOpening;
+    	return -index*this.gapOpening;
+     }
 }

### 2015-10-22 Assignment I/Material/NW_Code/NeedlemanWunschBase.java

@@ -9,7 +9,7 @@ import java.util.ArrayList;
  */
 public class NeedlemanWunschBase {
 	
-    public GapPenalty gapPenalty = new GapPenalty();
+    protected GapPenalty gapPenalty = new GapPenalty();
     private int matchScore = 1;
     private int mismatchScore = -1;
     private String sequence1 = null;

### 2015-10-22 Assignment I/Material/NW_Code/RunNeedlemanWunsch.java

@@ -51,8 +51,8 @@ public class RunNeedlemanWunsch {
         nw.setMatchScore(options.getMatchScore());
         nw.setMismatchScore(options.getMismatchScore());
         nw.gapPenalty.setGapOpening(options.getOpeningCost());
-        nw.gapPenalty.setGapExtension(options.getExtensionCost());
-        if(options.getExtensionCost() != 0) {
+        if(options.getExtensionCost() != null) {
+            nw.gapPenalty.setGapExtension(options.getExtensionCost());
             nw.gapPenalty.setPenaltyType(1);
         }else{
             nw.gapPenalty.setPenaltyType(0);

### 2015-10-22 Assignment II/Assignment2-Ditz_Schroeder-WS15-16.tex
renamed the latexfile

--- 2015-10-19 Assignment II/Assignment1-Ditz_Schroeder-WS15-16.tex
@@
    10pt,              % Schriftgroesse
-   ngerman,           % wird an andere Pakete weitergereicht
+   nenglish,           % wird an andere Pakete weitergereicht
    a4paper,           % Seitengroesse
@@
 
-  \section*{Exercise 1 - \textsl{}}
+ \section*{Exercise 1 - \textsl{Hirschberg algorithm for alignment in linear space}}
+
+ \section*{Exercise 2 - \textsl{Do scoring matrices have expected score smaller than zero?}}
+
+ The substitution matrices were evaluated according to the expectancy value formula given in the lecture, the substitution matrices were evaluated with the assumption of uniform distributed amino acids in two sequences.
+ \begin{equation*}
+ \sum_{a,b \in \Sigma}p_a p_b s(a,b)
+ <=>  (\sum_{a,b \in \Sigma} s(a,b))  p_a p_b
+ \label{expectance}
+ \end{equation*}
+
+ For the determination of one expectance value, $p_a$ and $p_b$ were each substituted with $1/20$, for the probabilistic occurrence in sequences with uniform distributed amino acids.
+The sum was calculated via R and the total summation of the substitution matrix \ref{expectance}.The result for each matrix can be seen in table \ref{Results-Expectance}.
+
+ \begin{table}[h]
+ \begin{tabular}{|c|c|}
+ 	\hline \rule[-2ex]{0pt}{5.5ex} Substitution Matrix & Expectance Value \\ 
+ 	\hline \rule[-2ex]{0pt}{5.5ex} BLSOUM50 & -1.155 \\ 
+ 	\hline \rule[-2ex]{0pt}{5.5ex} BLOSUM52 & -1.065 \\ 
+ 	\hline \rule[-2ex]{0pt}{5.5ex} BLOSUM80 & -2.3275 \\ 
+ 	\hline \rule[-2ex]{0pt}{5.5ex} PAM250 & -1.14 \\ 
+ 	\hline \rule[-2ex]{0pt}{5.5ex} PAMN & 0.155 \\ 
+ 	\hline 
+ \end{tabular}
+
+   	\label{Results-Expectance}
+   	\caption{Result of the calculation with each given substitution matrix according to equation}
+ \end{table}
+
+ As a conclusion we want to state, that all substitution matrices are possible feasible matrices.
+Except of the PAMN matrix, which has a positive expectancy value, which could lead to wrong conclusion.
+One Aspect we also want to state, is that we did not calculate the values for the matrices with the unknown sign x or X.
+and the B or Z sign,  which stands for two amino acids.
+Although it would be possbile to use the unknown sign, if they are also uniform distributed in a sequence.
+But as a result of the wanted comparison, between matrices which didn't contain these signs, we did not use these columns and rows in our calculations.
+
+ \section*{Exercise 3 - \textsl{Needleman-Wunsch algorithm for affine gap scores}}
 

### 2015-10-22 Assignment II/Assignment2-Ditz_Schroeder-WS15-16.tex
mooooooooooooooooore pictureeeeeeeeeeeeeeeeeees
Finished for this evening ... task one still needs text

@@
 \usepackage{graphicx}
+\usepackage{grffile} %allows to use pngs
 \usepackage{eurosym}
@@
  \section*{Exercise 1 - \textsl{Hirschberg algorithm for alignment in linear space}}
+  With two given Sequences (Xand Y), the scoring of s(a,a) = 4, s(a,b)=-3 and a gap penalty g=-3, the Hirschberg algorithm was started.
 
+ First, the Sequence X was split into two parts and 
+  \begin{figure}[h]
+  	\includegraphics[scale=0.25]{img/Hirschberg_Step1.png}
+  	\label{Step1}
+  	\caption{In the first step the sequence X was split into two parts and for both a NW global alignment was calculated.
+It's important to state, that the NW of the suffix of the sequence splitting was calculated reverse.
+The Maximum which was found after the substraction of both maxima was used to identify two letters, whrch are to be aligned.}
+  \end{figure}
+
+  \begin{figure}[h]
+   	\includegraphics[scale=0.25]{img/Hirschberg_Step2.png}
+   	\label{Step2}
+   	\caption{In the}
+  \end{figure}
+  \begin{figure}[h]
+    \includegraphics[scale=0.25]{img/Hirschberg_Step3.png}
+	\label{Step3}
+	\caption{BLAAAAAAAAAAA}
+  \end{figure}
+
+  \begin{figure}[h]
+   \includegraphics[scale=0.25]{img/Hirschberg_Step4.png}
+   \label{Step4}
+   \caption{BLAAAAAAAAAAA}
+   \end{figure}
  \section*{Exercise 2 - \textsl{Do scoring matrices have expected score smaller than zero?}}

### 2015-10-23 Assignment II/Assignment2-Ditz_Schroeder-WS15-16.tex
Excercsie 1
Hey, gerade etwas zeitdruck, bitte schau auch mal die aufgabe eins an ;)
hab sie eig. fertig, aber text ist so semi...

@@
  \section*{Exercise 1 - \textsl{Hirschberg algorithm for alignment in linear space}}
-  With two given Sequences (Xand Y), the scoring of s(a,a) = 4, s(a,b)=-3 and a gap penalty g=-3, the Hirschberg algorithm was started.
+  With two given Sequences (X= TGGA and Y=TTGAGA), the scoring of s(a,a) = 4, s(a,b)=-3 and a gap penalty g=-3, the Hirschberg algorithm was started.
+First the sequence X was split into two substrings, one was the prefix (\ref{Step1}-green): TG and one the subfix sequence GGA (\ref{Step1} - yellow).
+The prefix was used in a NW alignment and the suffix was also used in a NW laigment, but this time reversed.
+Both NW Matrices were calculated with the space reduced algorithm technique.
+The result is an array with the maxima the matrix saved in an array (\ref{Step1}-red columns).
+Both arrays are cellwise added up and the maximum is used to determine the two positions of both sequences (\ref{Step1}-red cell), which should be aligned.
+In step 1 this was the G(X2) to the G(Y3).
+These position were finally saved in a final array.
 
@@
   \end{figure}
+  The second steps starts with cutting the  matrix in the Sequence Y Dimension.
+Definition of how to start the cutting is not very clearly described, and therefore we cutted at position y+1(\ref{Step2} - yellow and gold area) and y-1 (\ref{Step2} - green area) of the last maximum.
+The yellow and gold part was processed like in the first step.
+The green one was interpreted as the trivial case, were one sequence has the length one.
+which mean,s we simply took the maximum of the table as the to aligning position and saved it in the result array.
 
@@
    	\label{Step2}
-   	\caption{In the}
+   	\caption{Step 2 - calculating the needleman wunsch alignments for the sub sequences.}
   \end{figure}
+
+  In step 3 the trivial case was now in the yellow area (\ref{Step3} -yellow arrea). And the last position for aligning was filled into the result matrix.
+
   \begin{figure}[h]
@@
 	\label{Step3}
-	\caption{BLAAAAAAAAAAA}
+	\caption{step 3 - final trivial case}
   \end{figure}
+
+    In step 4 the interpretation of the result array was processed.
+This means, that if a position was in the result array, both letters were aligned according to the postions.
+If there was no position in the array, a gap was filled in (\ref{Step4}).
 
@@
    \label{Step4}
-   \caption{BLAAAAAAAAAAA}
+   \caption{Interpretation of the Result array.}
    \end{figure}
+
  \section*{Exercise 2 - \textsl{Do scoring matrices have expected score smaller than zero?}}

### 2015-10-23 Assignment II/Assignment2-Ditz_Schroeder-WS15-16.tex
ein paar rechtschreibfehler korrigiert und zu aufgabe 3 schon etwas geschrieben

@@
   With two given Sequences (X= TGGA and Y=TTGAGA), the scoring of s(a,a) = 4, s(a,b)=-3 and a gap penalty g=-3, the Hirschberg algorithm was started.
-First the sequence X was split into two substrings, one was the prefix (\ref{Step1}-green): TG and one the subfix sequence GGA (\ref{Step1} - yellow).
-The prefix was used in a NW alignment and the suffix was also used in a NW laigment, but this time reversed.
+First the sequence X was split into two substrings, one was the prefix (\ref{Step1}-green): TG and one the suffix sequence GGA (\ref{Step1} - yellow).
+The prefix was used in a NW alignment and the suffix was also used in a NW alignment, but this time reversed.
 Both NW Matrices were calculated with the space reduced algorithm technique.
@@
 The green one was interpreted as the trivial case, were one sequence has the length one.
-which mean,s we simply took the maximum of the table as the to aligning position and saved it in the result array.
+Which means we simply took the maximum of the table as the two aligning position and saved it in the result array.
 
@@
 
-  In step 3 the trivial case was now in the yellow area (\ref{Step3} -yellow arrea). And the last position for aligning was filled into the result matrix.
+  In step 3 the trivial case was now in the yellow area (\ref{Step3} -yellow area). And the last position for aligning was filled into the result matrix.
 
@@
     In step 4 the interpretation of the result array was processed.
-This means, that if a position was in the result array, both letters were aligned according to the postions.
+This means, that if a position was in the result array, both letters were aligned according to the positions.
 If there was no position in the array, a gap was filled in (\ref{Step4}).
@@
 
+ We extended our GapPenalty class from the previous assignment. Now it is possible to get the
+ initialization cost. One just has to call the function getInitCost() with an integer, which defines
+ the current cell index i or j, respectively. This leads us to a very convenient way to initialize 
+ our matrix.
+
 \end{document}

### 2015-10-26 Assignment III/Assignment3-Ditz_Schroeder-WS15-16.tex
Start Assignment III

--- 2015-10-22 Assignment II/Assignment2-Ditz_Schroeder-WS15-16.tex
@@
 \begin{center}
-{\Large\textbf{ Blatt #1}} % Blatt
+{\Large\textbf{ Assignment #1}} % Blatt
 
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{7}{Alexander Seitz}{26. October 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
+\header{3}{Alexander Seitz}{2. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
 
- \section*{Exercise 1 - \textsl{Hirschberg algorithm for alignment in linear space}}
-  With two given Sequences (Xand Y), the scoring of s(a,a) = 4, s(a,b)=-3 and a gap penalty g=-3, the Hirschberg algorithm was started.
+\section*{Exercise 1 - \textsl{Equivalence of distance and similarity alignments}}
 
- First, the Sequence X was split into two parts and 
-  \begin{figure}[h]
-  	\includegraphics[scale=0.25]{img/Hirschberg_Step1.png}
-  	\label{Step1}
-  	\caption{In the first step the sequence X was split into two parts and for both a NW global alignment was calculated.
-It's important to state, that the NW of the suffix of the sequence splitting was calculated reverse.
-The Maximum which was found after the substraction of both maxima was used to identify two letters, whrch are to be aligned.}
-  \end{figure}
+\section*{Exercise 1 - \textsl{Using BLAT to align 454 reads to the Helicobacter pylori genome}}
 
-  \begin{figure}[h]
-   	\includegraphics[scale=0.25]{img/Hirschberg_Step2.png}
-   	\label{Step2}
-   	\caption{In the}
-  \end{figure}
-  \begin{figure}[h]
-    \includegraphics[scale=0.25]{img/Hirschberg_Step3.png}
-	\label{Step3}
-	\caption{BLAAAAAAAAAAA}
-  \end{figure}
-
-  \begin{figure}[h]
-   \includegraphics[scale=0.25]{img/Hirschberg_Step4.png}
-   \label{Step4}
-   \caption{BLAAAAAAAAAAA}
-   \end{figure}
- \section*{Exercise 2 - \textsl{Do scoring matrices have expected score smaller than zero?}}
-
- The substitution matrices were evaluated according to the expectancy value formula given in the lecture, the substitution matrices were evaluated with the assumption of uniform distributed amino acids in two sequences.
- \begin{equation*}
- \sum_{a,b \in \Sigma}p_a p_b s(a,b)
- <=>  (\sum_{a,b \in \Sigma} s(a,b))  p_a p_b
- \label{expectance}
- \end{equation*}
-
- For the determination of one expectance value, $p_a$ and $p_b$ were each substituted with $1/20$, for the probabilistic occurrence in sequences with uniform distributed amino acids.
-The sum was calculated via R and the total summation of the substitution matrix \ref{expectance}.The result for each matrix can be seen in table \ref{Results-Expectance}.
-
- \begin{table}[h]
- \begin{tabular}{|c|c|}
- 	\hline \rule[-2ex]{0pt}{5.5ex} Substitution Matrix & Expectance Value \\ 
- 	\hline \rule[-2ex]{0pt}{5.5ex} BLSOUM50 & -1.155 \\ 
- 	\hline \rule[-2ex]{0pt}{5.5ex} BLOSUM52 & -1.065 \\ 
- 	\hline \rule[-2ex]{0pt}{5.5ex} BLOSUM80 & -2.3275 \\ 
- 	\hline \rule[-2ex]{0pt}{5.5ex} PAM250 & -1.14 \\ 
- 	\hline \rule[-2ex]{0pt}{5.5ex} PAMN & 0.155 \\ 
- 	\hline 
- \end{tabular}
-
-   	\label{Results-Expectance}
-   	\caption{Result of the calculation with each given substitution matrix according to equation}
- \end{table}
-
- As a conclusion we want to state, that all substitution matrices are possible feasible matrices.
-Except of the PAMN matrix, which has a positive expectancy value, which could lead to wrong conclusion.
-One Aspect we also want to state, is that we did not calculate the values for the matrices with the unknown sign x or X.
-and the B or Z sign,  which stands for two amino acids.
-Although it would be possbile to use the unknown sign, if they are also uniform distributed in a sequence.
-But as a result of the wanted comparison, between matrices which didn't contain these signs, we did not use these columns and rows in our calculations.
-
- \section*{Exercise 3 - \textsl{Needleman-Wunsch algorithm for affine gap scores}}
+\section*{Exercise 1 - \textsl{Bonus: Use SSAHA2 to align 535 reads to the Helicobacter pylori genome}}
 

### 2015-10-26 Assignment III/Assignment3-Ditz_Schroeder-WS15-16.tex
hier ist schonmal ein erster Entwurf für den Beweis in Aufgabe 1. Vielleicht kannst du mal drübergucken.

@@
 \usepackage{ifthen}
-\usepackage{TikZ} %phylogenetischer Baum
-\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
-\usetikzlibrary{automata,arrows}
+%\usepackage{TikZ} %phylogenetischer Baum
+%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
+%\usetikzlibrary{automata,arrows}
 \usepackage{subfigure}
@@
 
-\section*{Exercise 1 - \textsl{Equivalence of distance and similarity alignments}}
+\section*{Theoretical Assignment - \textsl{Equivalence of distance and similarity alignments}}
+Assume there are two sequences of length n and m, respectively. The length of an alignment between
+this two sequences is of length n+m. As it is written on the assignment following equation is 
+valid:
 
-\section*{Exercise 1 - \textsl{Using BLAT to align 454 reads to the Helicobacter pylori genome}}
+\begin{equation}
+ n + m = 2*M + \sum_k kg_k ,
+\end{equation}
 
-\section*{Exercise 1 - \textsl{Bonus: Use SSAHA2 to align 535 reads to the Helicobacter pylori genome}}
+where M is the number of aligned characters. Since later one of our sequences is called a, we 
+changed the latter a, which is used on the assignment sheet, to M. \\
+Using this equation, we can write the distance of our two sequences (let us call them a and b) as
+
+\begin{align}
+ D(a,b) &= min\{\sum_M d(a,b) + \sum_k k g_k\} \nonumber\\
+        &= min\{\sum_M c + \sum_k k g_k c/2 - \sum_M s(a,b) + \sum_k \hat{\gamma}(k) g_k\} \nonumber\\
+        &= min\{c(n+m)/2 - \sum_M s(a,b) + \sum_k \hat{\gamma}(k) g_k\} \nonumber\\
+        &= c(n+m)/2 - max\{\sum_M s(a,b) - \sum_k \hat{\gamma}(k) g_k\} \nonumber\\
+        &= c(n+m)/2 - S(a,b)
+\end{align}
+
+Solving for S(a,b), we get:
+
+\begin{equation}
+ S(a,b) = c(n+m)/2 - D(a,b)
+\end{equation}
+
+So one can see that the Score is optimal if and only if the Distance is optimal.
+
+\section*{Practical Assignment - \textsl{Using BLAT to align 454 reads to the Helicobacter pylori genome}}
+
+\section*{Practical Assignment - \textsl{Bonus: Use SSAHA2 to align 535 reads to the Helicobacter pylori genome}}
 

### 2015-10-27 project/proposal/Project_proposal.tex
Project proposal
Hey, there should be more under the point ideas.... but i have no idea
;)
and please read the rest any ideas? corrections?

% !TeX spellcheck = en_US
\documentclass[]{article}

\usepackage[utf8]{inputenc} % Font Encoding, benoetigt fuer Umlaute
\usepackage[english]{babel}   % \textsl{}Spracheinstellung

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{grffile} %allows to use pngs
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
\usepackage{TikZ} %phylogenetischer Baum
\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

%opening
\title{Project Proposal: The Core Of The Poodle}
\author{Jonas Ditz  \& Benjamin Schroeder}

\begin{document}

\maketitle
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{img/logo_poodle.png}
\end{figure}

\begin{abstract}
Our project is to design and implement a tool for real world. The general idea of Poodle is to create a tool which allows lifescience laboratories to organize their own primer- , plasmid- or even culture-libraries. Therefore they need a database structure, a graphical user interface (GUI) and some additional functions for their daily duties. These additional functions could be a efficient sequence aligning tool (Hirschberg's algorithm). Also an integrated BLAST or DIAMOND search, which can adress the internal or external databases like PDB or Genbank. Although we know this is a though time consuming idea, we are ready to take our chance and to create something, which could be used in real world. We already have somebody in mind, we could concretely ask, if they want to develop this idea with us. 
\end{abstract}

\section{ The Idea}
Most lifescience labs manage their data for primers and plasmids via excel spreedsheats or other uncomfortable software solutions. Especially when these sheets grow over time the disadvantages of those spreedsheats become clear in aspects of time consuming searches or unorganized entries. 
\\
Our idea is to create an open source tool, which tries to optimize the organization and speed of getting to the desired data.

\section{ The Structure}
General we splitted the project in several modules. First we want to list the basic ones. These are the data base (DB) module, which we want to realise with SQL lite and .csv-files. These should be automatically loaded into the database and also should be automatically exported.
The next most important module is the GUI which should give the user the possibility of intuitive usage of the DB. Also we want to restrict the user to a minimum of needed rules, when for example making new entries, to verify a clear structured DB.\\
Following now the applications, which should run on the server and provide some useful functions.\\
The integration of the BLAST or DIAMOND search algorithm. This is useful for designing new Arrays or modifying plasmids, because it's is wanted to do the changes in the least amount of steps, which is of only possible if the most similar sequence is known.\\
Also a alignment tool can be very useful to visualize the found results. For the alignments the Hirschberg algorithm should be used.\\
The last module idea was to integrate information to the data from other DBs. If for example a certain protein or domain is incorporated into a plasmid it is useful to have the PDB reference or even integrated informations of the proteins.
	\begin{figure}[h]
		\includegraphics[scale=0.5]{img/Structure.png}
	\end{figure}

\section{ The Time-Plan}
Of course time is a important factor. Therefore we started to organize a time plan for all of our ideas. This is of course the final plan. The set up of the DB should be finished in the first two weeks. It should be easy to set the DB up from the data we might get from our eventually partner lab. At the same time and through the whole project time, we want to work on the GUI. Because of adding of new functional modules also needs to happen in the GUI. But before starting blindly the GUI we want to design a general concept, allowing a reasonable integration. After the basics are finished we start to implement or integrate additional functions, like the search or the alignment algortihms. Time is definetly limiting the time of our project. Therefore we want to add the modules one after another and we cannot add all modules in time, this might be the case after the project.

	\begin{figure}[h]
		\includegraphics[scale=0.5]{img/Time.png}
	\end{figure}

\end{document}

### 2015-11-01 Assignment III/Assignment3-Ditz_Schroeder-WS15-16.tex
tex file für assignment 3 weiterbearbeitet

@@
 
+As described on the assignment sheet, we downloaded the binaries of SSAHA2 from \\
+https://www.sanger.ac.uk/resources/software/ssaha2/\#t\_2. After unpacking the zip archive SSAHA2 was
+working, instantly. We ran SSAHA2 with the following command: \\
+\\
+\textit{~/bin/ssaha2\_v2.5.5\_x86\_64/ssaha2 -454 -output psl  ../data/Hpylori.fasta ../data/reads.fasta > hpylori\_reads\_ssaha2\_output.psl} \\
+\\
+The parameter \textit{-output psl} convert SSAHA2 output into psl format, which is the same format 
+as used by BLAT.
+One can look over the results by opening hpylori\_reads\_ssaha2\_output.psl, which we provide together 
+with this pdf. Since it is a huge file, we used a short python script (analysis.py, also send as a 
+attachment) to get a short overview of our results. \\
+\\
+Output of analysis.py:\\
+\indent number of all mapped reads:\\ 
+    \indent\indent absolute number:  321954\\
+    \indent\indent percentage:  100\\
+\indent number of unique mapped reads:\\ 
+    \indent\indent absolute number: 72897\\
+    \indent\indent percentage:  22.642054455\\
+\\
+With that short overview one can see that SSAHA2 mapped all provided reads to our database. In 
+this case our database was Helicobacter pylori. That is interesting and might indicate a problem with
+the default parameters of SSAHA2. It looks like SSAHA2 tries to get a sensitivity of 100\%, which 
+was successful in our case. One has to decide from case to case, if that is really what their needs.
+We run SSAHA2 on a linux machine with 1 Gb RAM and a single core processor with 1.66 GHz. The runtime
+was about one hour on that computer.
+
 \end{document}

### 2015-11-01 project/proposal/Project_proposal.tex
mein shit

@@
 \section{ The Idea}
-Most lifescience labs manage their data for primers and plasmids via excel spreedsheats or other uncomfortable software solutions.
-Especially when these sheets grow over time the disadvantages of those spreedsheats become clear in aspects of time consuming searches or unorganized entries.
+Most lifescience labs manage their data for primers and plasmids via excel spreadsheets or other uncomfortable software solutions.
+Especially when these sheets grow over time the disadvantages of those spreadsheets become clear in aspects of time consuming searches or unorganized entries.
 \\
@@
 	\begin{figure}[h]
-		\includegraphics[scale=0.5]{img/Structure.png}
+		\centering
+		\includegraphics[width=0.5\textwidth]{img/Structure.png}
 	\end{figure}
@@
 	\begin{figure}[h]
-		\includegraphics[scale=0.5]{img/Time.png}
+		\includegraphics[width=\textwidth]{img/Time.png}
 	\end{figure}

### 2015-11-01 Assignment III/code/Main.java

@@ -1,0 +1,13 @@
+package Ex1;
+
+import java.io.*;
+import java.util.InputMismatchException;
+import java.util.Scanner;
+
+public class Main {
+	public static void main(String[] args) {
+		parse= new Parser("C:\Users\Benjamin\Documents\GitHub\BioinformaticsI-Assigments\Assignment III\Material\output.psl");
+		
+		}
+	}
+}

### 2015-11-01 Assignment III/code/Parser.java

@@ -1,0 +1,80 @@
+package Ex1;
+
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.io.PrintWriter;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.regex.Pattern;
+
+public class Parser {
+	private String filePath;
+	private List<String[]> Sequences  = new LinkedList<String[]>();
+
+	public Parser(String path){
+		this.filePath=path;
+		readFile(path);
+	}
+	/**
+		Used parts of the code from exercise!
+	 */
+	public void readFile(String file){
+		try {
+			BufferedReader br = new BufferedReader(new FileReader(file));
+			String currLine = "";
+			int x= 1;
+			String[] e = new String [3];
+
+			while((currLine =br.readLine()) != null){
+				if(Pattern.matches(">.*", currLine)){
+					e= new String[3];
+					e[0]= ""+x;
+					x++;
+					e[1] = currLine;
+					e[2]="";
+					Sequences.add(e);
+				}
+				else if(Pattern.matches(".+",currLine) ){
+					e[2]= e[2]+currLine;
+				}
+			}
+		}
+		catch (IOException e) {
+			e.printStackTrace();
+		}
+
+	}
+
+	public void readOut(){
+		String[] e;
+		int i =0;
+		while(i < Sequences.size() && (e = Sequences.get(i)) != null ){
+			System.out.println("Sequence-Number: "+e[0]);
+			System.out.println("Header: "+e[1]);
+			System.out.println("Sequence: "+e[2]);
+			System.out.println();
+			i++;
+		}
+	}
+
+	public List<String[]> getSequences(){
+		return Sequences;
+	}
+	
+	public void createFastaFile(String file){
+		try {
+			String[] e;
+			PrintWriter out = new PrintWriter(new BufferedWriter(new FileWriter(file, false)));
+			for(int i=0; i<Sequences.size() && (e=Sequences.get(i))!=null; i++){
+				out.println(e[1]);
+				out.println(e[2]);
+			}
+			out.flush();
+		} catch (IOException e) {
+			e.printStackTrace();
+		}
+	}
+}

### 2015-11-01 Assignment III/script_R.R

@@ -1,0 +1,1 @@
+output <-  read.table("C:/Users/Benjamin/Documents/GitHub/BioinformaticsI-Assigments/Assignment III/Material/output.psl", header=TRUE, sep="\t")

### 2015-11-03 Assignment III/code/Main.java
Revert "mein shit"
This reverts commit 66f6f227e1510e7b82c0f94e5d921cc11bb2e9f4.

@@ -1,13 +1,0 @@
-package Ex1;
-
-import java.io.*;
-import java.util.InputMismatchException;
-import java.util.Scanner;
-
-public class Main {
-	public static void main(String[] args) {
-		parse= new Parser("C:\Users\Benjamin\Documents\GitHub\BioinformaticsI-Assigments\Assignment III\Material\output.psl");
-		
-		}
-	}
-}

### 2015-11-03 Assignment III/code/Parser.java

@@ -1,80 +1,0 @@
-package Ex1;
-
-import java.io.BufferedReader;
-import java.io.BufferedWriter;
-import java.io.FileReader;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.io.PrintWriter;
-import java.util.LinkedList;
-import java.util.List;
-import java.util.regex.Pattern;
-
-public class Parser {
-	private String filePath;
-	private List<String[]> Sequences  = new LinkedList<String[]>();
-
-	public Parser(String path){
-		this.filePath=path;
-		readFile(path);
-	}
-	/**
-		Used parts of the code from exercise!
-	 */
-	public void readFile(String file){
-		try {
-			BufferedReader br = new BufferedReader(new FileReader(file));
-			String currLine = "";
-			int x= 1;
-			String[] e = new String [3];
-
-			while((currLine =br.readLine()) != null){
-				if(Pattern.matches(">.*", currLine)){
-					e= new String[3];
-					e[0]= ""+x;
-					x++;
-					e[1] = currLine;
-					e[2]="";
-					Sequences.add(e);
-				}
-				else if(Pattern.matches(".+",currLine) ){
-					e[2]= e[2]+currLine;
-				}
-			}
-		}
-		catch (IOException e) {
-			e.printStackTrace();
-		}
-
-	}
-
-	public void readOut(){
-		String[] e;
-		int i =0;
-		while(i < Sequences.size() && (e = Sequences.get(i)) != null ){
-			System.out.println("Sequence-Number: "+e[0]);
-			System.out.println("Header: "+e[1]);
-			System.out.println("Sequence: "+e[2]);
-			System.out.println();
-			i++;
-		}
-	}
-
-	public List<String[]> getSequences(){
-		return Sequences;
-	}
-	
-	public void createFastaFile(String file){
-		try {
-			String[] e;
-			PrintWriter out = new PrintWriter(new BufferedWriter(new FileWriter(file, false)));
-			for(int i=0; i<Sequences.size() && (e=Sequences.get(i))!=null; i++){
-				out.println(e[1]);
-				out.println(e[2]);
-			}
-			out.flush();
-		} catch (IOException e) {
-			e.printStackTrace();
-		}
-	}
-}

### 2015-11-03 Assignment III/script_R.R

@@ -1,1 +1,0 @@
-output <-  read.table("C:/Users/Benjamin/Documents/GitHub/BioinformaticsI-Assigments/Assignment III/Material/output.psl", header=TRUE, sep="\t")

### 2015-11-03 project/proposal/Project_proposal.tex
Revert "mein shit"
This reverts commit 66f6f227e1510e7b82c0f94e5d921cc11bb2e9f4.

@@
 First we want to list the basic ones.
-These are the data base (DB) module, which we want to realise with SQL lite and .csv-files.
+These are the database (DB) module, which we want to realise with SQL lite and .csv-files.
 These should be automatically loaded into the database and also should be automatically exported.
@@
 	\begin{figure}[h]
-		\centering
-		\includegraphics[width=0.5\textwidth]{img/Structure.png}
+		\includegraphics[width=\textwidth]{img/Structure.png}
 	\end{figure}
@@
 But before starting blindly the GUI we want to design a general concept, allowing a reasonable integration.
-After the basics are finished we start to implement or integrate additional functions, like the search or the alignment algortihms.
-Time is definetly limiting the time of our project.
-Therefore we want to add the modules one after another and we cannot add all modules in time, this might be the case after the project.
+After the basics are finished we start to implement or integrate additional functions, like the search or the alignment algorithms.
+Time is the limiting factor of our project.
+Therefore we want to add the modules one after another and if we cannot add all modules in time, this might be the case after the project.
 

### 2015-11-03 Assignment III/Abgabe/Assignment3-Ditz_Schroeder-WS15-16.tex
added Abgabe to Assignment III

--- 2015-11-01 Assignment III/Assignment3-Ditz_Schroeder-WS15-16.tex
@@
 \section*{Practical Assignment - \textsl{Using BLAT to align 454 reads to the Helicobacter pylori genome}}
+The blat algorithm was compiled in a virtual box using bio-linux.
+The output generated by the blat algorithm was saved as .plt and is attached.
+The maximal Intron size was set to 50, to limit the ammount of hits.
+Generally this is a good idea, because introns which are getting to large make no sense in a biological context.
+The analysis was accomplished by a java program, which is also attached.
+The program was executed via eclipse and not via the command line.
+If you want to use it, you might change the path directions in the main class and it should work than.
+Sadly is the runtime very high and was around 45 mins for the given data set.
+\\
+
+The complete Data set had 524427 entries. The absolute number of reads, which was be aligned is  437586 or 83 \%. Of these reads 314896 were unique, which are 60\%.
+A second part of the task was to figure out how many positions of the H. pylori were left unaligned. From the total number of positions 1691694, 1071574 which is a coverage of 63%.\\
+The repeating of sequences can happen very often in different contexts. For example in with noncoding sequence regions or with viral DNA which is stabil incorporated into the genome.
 

### 2015-11-03 Assignment III/Abgabe/uncompiled_javaCode/Analysis/Analysis.java

@@ -1,0 +1,78 @@
+package Analysis;
+
+import java.util.Arrays;
+import java.util.LinkedList;
+import java.util.ListIterator;
+
+import javax.xml.soap.Node;
+
+
+
+public class Analysis {
+	String[][] content;
+	String[][] reads;
+	
+	public Analysis(String[][] content, String[][] reads){
+		this.content=content;
+		this.reads=reads;
+	}
+	
+	//for exercise 1 &2
+	public int[] checkAmmountOfHits(){
+		int reads=0;
+		int unique=0;
+		LinkedList<String> save = new LinkedList<String>();	// a temporary list to compare if a read was already reckognized
+		next:
+		for(int x=0; x < content.length; x++){	// go through whole output of blat
+			ListIterator<String> iterator = save.listIterator();
+			String a;
+			while(iterator.hasNext() && (a= iterator.next())!= null){	// check if a sequence name was already recognized
+				if(a!=null && a.equals(content[x][9])){
+					unique--;
+					continue next;
+				}
+			}
+			reads++; // If there is a new read.
+			unique++;
+			save.add(content[x][9]);
+//			System.out.println("line:"+x);
+		}
+		int[] result = new int[2];
+		result[0]=reads;
+		result[1]=unique;
+		return result;
+	}
+	
+	
+	//for exercise 3
+	public int mapped(){
+		boolean[] mapped = new boolean[1691694]; // found externally out, there are 1691694 positions in the H. pylori genome (wordcount and then took letters) 
+		Arrays.fill(mapped, Boolean.FALSE);
+		int result=10;
+		for(int x=0; x<content.length; x++){// generate array of Hpylori genome and the positions which are mapped.
+			int start;
+			int end;
+			if(content[x][15]!=null){
+				start= Integer.parseInt(content[x][15]);
+				if(content[x][16]!=null){
+					end= Integer.parseInt(content[x][16]);
+					for(;start<=end;start++){
+						if(mapped[start]==true){ // the position was already mapped!
+							continue;
+						}
+						else{	//found new position, which was not mapped.
+							mapped[start]=true;
+						}
+					}
+				}
+			}
+		}
+		
+		for(int x=0; x<mapped.length; x++){ // count the not mapped positions
+			if(mapped[x]==false){
+				result++;
+			}
+		}
+		return result;
+	}
+}

### 2015-11-03 Assignment III/Abgabe/uncompiled_javaCode/Parser/PaserBasic.java

@@ -1,0 +1,5 @@
+package Parser;
+
+public class PaserBasic {
+
+}

### 2015-11-03 Assignment III/Abgabe/uncompiled_javaCode/Parser/parserFasta.java

@@ -1,0 +1,88 @@
+package Parser;
+
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.io.PrintWriter;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.regex.Pattern;
+
+public class parserFasta {
+	private String filePath;
+	private LinkedList<String[]> sequences  = new LinkedList<String[]>();
+	private String[][] sequencesArray;
+	
+	public parserFasta(String path){
+		this.filePath=path;
+		readFile(path);
+	}
+	/**
+		Used parts of the code from exercise!
+	 */
+	public void readFile(String file){
+		try {
+			BufferedReader br = new BufferedReader(new FileReader(file));
+			String currLine = "";
+			int x= 1;
+			String[] e = new String [3];
+
+			while((currLine =br.readLine()) != null){
+				if(Pattern.matches(">.*", currLine)){
+					e= new String[3];
+					e[0]= ""+x;
+					x++;
+					e[1] = currLine;
+					e[2]="";
+					sequences.add(e);
+				}
+				else if(Pattern.matches(".+",currLine) ){
+					e[2]= e[2]+currLine;
+				}
+			}
+		}
+		catch (IOException e) {
+			e.printStackTrace();
+		}
+		
+		sequencesArray= new String[sequences.size()][3];
+		for(int x=0; x<sequences.size(); x++){
+			String[] temp = sequences.pop();
+			for(int y=0; y<3; y++){
+				sequencesArray[x][y]= temp[y];
+			}
+		}
+	}
+
+	public void readOut(){
+		String[] e;
+		int i =0;
+		while(i < sequences.size() && (e = sequences.get(i)) != null ){
+			System.out.println("Sequence-Number: "+e[0]);
+			System.out.println("Header: "+e[1]);
+			System.out.println("Sequence: "+e[2]);
+			System.out.println();
+			i++;
+		}
+	}
+
+	public String[][] getsequences(){
+		return sequencesArray;
+	}
+	
+	public void createFastaFile(String file){
+		try {
+			String[] e;
+			PrintWriter out = new PrintWriter(new BufferedWriter(new FileWriter(file, false)));
+			for(int i=0; i<sequences.size() && (e=sequences.get(i))!=null; i++){
+				out.println(e[1]);
+				out.println(e[2]);
+			}
[…]

### 2015-11-03 Assignment III/Abgabe/uncompiled_javaCode/Parser/parserInterface.java

@@ -1,0 +1,5 @@
+package Parser;
+
+public interface parserInterface {
+
+}

### 2015-11-03 Assignment III/Abgabe/uncompiled_javaCode/Parser/parserPSL.java

@@ -1,0 +1,96 @@
+package Parser;
+
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.io.PrintWriter;
+import java.util.LinkedList;
+import java.util.List;
+import java.util.regex.Pattern;
+
+public class parserPSL {
+	private String filePath;
+	private String[][] content;
+
+	public parserPSL(String path){
+		this.filePath=path;
+		readFile(path);
+	}
+
+	
+	public void readFile(String file){
+		try {
+			BufferedReader br = new BufferedReader(new FileReader(file));
+			LinkedList<String> entries = extractLines(br);
+			System.out.println("finished step 1");
+			this.content = splitStringListToColumnArray(entries, 21, '\t');
+			System.out.println("finished step 2");
+		}
+		catch (IOException e) {
+			e.printStackTrace();
+		}
+	}
+	
+	
+	protected LinkedList<String> extractLines(BufferedReader br){
+		LinkedList<String> entries = new LinkedList<String>();
+		String currLine = "";	
+		try {
+			while((currLine =br.readLine()) != null){
+				entries.add(currLine);
+			}
+		} catch (IOException e) {
+			System.out.println("There was a problem in extractLines Methode");
+			e.printStackTrace();
+		}
+		return entries; 
+	}
+	
+	protected String[][] splitStringListToColumnArray(LinkedList<String> entries, int columns, char seperator){
+		String[][] result= new String[entries.size()][columns];
+		String temp="";	//builds up a string for to fill into the column.
+		int headerLines=0;
+		
+		//Delete HEader.
+		while(headerLines<5){
+			String a=entries.pop();
+			headerLines++;
+		}
+		
+		//Split each line into the Columns
+		int row =0;
+			for(int x =0; x< entries.size(); x++){		//go through entry list
+				char[] entry= entries.pop().toCharArray();
+				int column=0;
+				for(int y=0; y<entry.length; y++){		//go through entry and seperate each column
+					if(seperator == entry[y]){		// jumpt to next column..
+						if(temp==""){
+							temp = "n.A.";
+						}
+						result[row][column]=temp;
+						temp="";
+						column++;
+					}
+					else if(' '==entry[y]){
+						continue;
+					}
+					else{
+						temp=temp+entry[y];	// concatenate the new char with already collected String.
+					}
+				}
[…]

### 2015-11-03 Assignment III/Abgabe/uncompiled_javaCode/Run/Main.java

@@ -1,0 +1,40 @@
+package Run;
+
+import java.io.*;
+import java.util.InputMismatchException;
+import java.util.Scanner;
+
+import Analysis.Analysis;
+import Parser.parserFasta;
+import Parser.parserPSL;
+
+public class Main {
+	public static void main(String[] args) {
+		String pathPsl = "C:/Users/Benjamin/Documents/GitHub/BioinformaticsI-Assigments/Assignment III/Material/output.psl";
+		String pathFasta = "C:/Users/Benjamin/Documents/GitHub/BioinformaticsI-Assigments/Assignment III/Material/reads.fasta";
+		
+		System.out.println("read in the .psl-File");
+		parserPSL blatOutput= new parserPSL(pathPsl); // read in the output file.
+		System.out.println("read in the .psl-File - Finished");
+		System.out.println("read in the .fasta-File");
+		parserFasta fastaReads = new parserFasta(pathFasta);
+		System.out.println("read in the .fasta-File - Finished");
+		
+		String[][] pslFile=blatOutput.getSequences();
+		String[][] fastaFile=fastaReads.getsequences();
+		
+		
+		System.out.println("Start Analysis:\n Here is the length:"+fastaFile.length);
+		Analysis analysis = new Analysis(pslFile, fastaFile);
+//		System.out.println(" How many Hits did blat find?:");
+//		int[] hits= analysis.checkAmmountOfHits();
+//		float percentageHits= hits[0]/fastaFile.length;
+//		float percentageuniqueHits= hits[1]/fastaFile.length;
+//		System.out.println("The absolute number: "+hits[0]+" Which is a percentage over the total: "+percentageHits);
+//		System.out.println("The unique number: "+hits[1]+" Which is a percentage over the total: "+percentageuniqueHits);
+		int mapped = analysis.mapped();
+		System.out.println("Were not mapped: "+mapped+" Which is a percentage ove: ");
+
+	}
+}
+

### 2015-11-04 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
added first steps of Excercise 2

--- 2015-10-26 Assignment III/Assignment3-Ditz_Schroeder-WS15-16.tex
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{3}{Alexander Seitz}{2. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
+\header{4}{Alexander Seitz}{9. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
 
-\section*{Theoretical Assignment - \textsl{Equivalence of distance and similarity alignments}}
-Assume there are two sequences of length n and m, respectively. The length of an alignment between
-this two sequences is of length n+m. As it is written on the assignment following equation is 
-valid:
+\section*{Theoretical Assignment - \textsl{Optimal multiple alignment}}
+
+To calculate our MSA we use the recursion written down on page 50 in the script.
 
 \begin{equation}
- n + m = 2*M + \sum_k kg_k ,
+ F(i_1, i_2, i_3) = max \begin{cases}
+                         F(i_1 -1, i_2 -1, i_3 -1) + s_{SP}(a_{1i_1},a_{2i_2},a_{3i_3}) \\
+                         \\
+                         F(i_1 -1, i_2 -1, i_3) + s_{SP}(a_{1i_1},a_{2i_2},-) \\
+                         F(i_1 -1, i_2, i_3 -1) + s_{SP}(a_{1i_1},-,a_{3i_3}) \\
+                         F(i_1, i_2 -1, i_3 -1) + s_{SP}(-,a_{2i_2},a_{3i_3}) \\
+                         \\
+                         F(i_1 -1, i_2, i_3) + s_{SP}(a_{1i_1},-,-) \\
+                         F(i_1, i_2 -1, i_3) + s_{SP}(-,a_{2i_2},-) \\
+                         F(i_1, i_2, i_3 -1) + s_{SP}(-,-,a_{3i_3}) \\
+                        \end{cases} \nonumber
 \end{equation}
 
-where M is the number of aligned characters. Since later one of our sequences is called a, we 
-changed the latter a, which is used on the assignment sheet, to M. \\
-Using this equation, we can write the distance of our two sequences (let us call them a and b) as
-
-\begin{align}
- D(a,b) &= min\{\sum_M d(a,b) + \sum_k k g_k\} \nonumber\\
-        &= min\{\sum_M c + \sum_k k g_k c/2 - \sum_M s(a,b) + \sum_k \hat{\gamma}(k) g_k\} \nonumber\\
-        &= min\{c(n+m)/2 - \sum_M s(a,b) + \sum_k \hat{\gamma}(k) g_k\} \nonumber\\
-        &= c(n+m)/2 - max\{\sum_M s(a,b) - \sum_k \hat{\gamma}(k) g_k\} \nonumber\\
-        &= c(n+m)/2 - S(a,b)
-\end{align}
-
-Solving for S(a,b), we get:
+\noindent If we fill the DP matrix using this recursion, we get the following MSA:
 
 \begin{equation}
- S(a,b) = c(n+m)/2 - D(a,b)
+ \begin{pmatrix}
+  C & T & T \\
+  - & T & C \\
+  C & C & T
+ \end{pmatrix}
 \end{equation}
 
-So one can see that the Score is optimal if and only if the Distance is optimal.
+\noindent with score $\alpha_{SP}(A^*) = S(A,B) + S(A,C) + S(B,C) = -2 + 2 + (-6) = -6$.
 
-\section*{Practical Assignment - \textsl{Using BLAT to align 454 reads to the Helicobacter pylori genome}}
+\section*{Theoretical Assignment - \textsl{Progressive alignment}}
+Progressive alignment methodes are one way to create multiple sequence alignments (MSA), in this task we had to accomplish manualy a progressive alignment.
+The first step for the progressive alignment was to generate the pairwise global distance matrices.
+Afterwards the global optima were entered into a new table, which was used to generate the guide tree in the second step.(figure \ref{DP2}).
+\begin{figure}[h]
+	\includegraphics[width=\textwidth]{Img/Exercise2-DP-Matrix.png}
+	\caption{ Global alignments lead to the basis table used to generate the guide tree}
+	\label{DP2}
+\end{figure}
 
-\section*{Practical Assignment - \textsl{Bonus: Use SSAHA2 to align 535 reads to the Helicobacter pylori genome}}
+In step 2 the guide tree was created by the UPGMA methode in 3 substeps.
+After every step, which added a new cluster, the distance table was updated.
+The result from this step was the guide tree, which was used to apply the 'complete alignment' methode in the last step, the progressive alignment step.(figure \ref{guidetree2})
+
+\begin{figure}[h]
+	\includegraphics[width=\textwidth]{Img/Exercise2-Guidetree.png}
+	\caption{ The guide tree is made from the final table from step 1}
+	\label{guidetree2}
+\end{figure}
+
+The last step was creating the actual MSA. The 'complete alignment' methode 
+\begin{figure}[h]
+	\includegraphics[width=\textwidth]{Img/Exercise2-CompleteAlignment.png}
+	\caption{ Complete alignment methode is used to get an MSA from the guidetree from step 2	}
+	\label{completealign}
+\end{figure}
+\section*{Practical Assignment - \textsl{Comparing multiple alignment}}
 

### 2015-11-05 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
Exercise final.
aufgabe 1 überarbeitet; jetzt mit DP matrix

@@
 \usepackage{dsfont}
+\usepackage{color}
 %\usepackage{wasysym}
@@
 
-\noindent If we fill the DP matrix using this recursion, we get the following MSA:
+\noindent Such a recursion results in a three-dimensional matrix. Since such a matrix is really difficult to 
+sketch, we split it into three two-dimensional matrices.
+
+\begin{figure}[ht]
+\centering
+\subfigure{
+\begin{tabular}{c|cccc}
+ 0 & 0 & C & C & T \\
+ \hline
+ 0 & \textcolor{red}{\textbf{0}} & -2 & -4 & -6 \\
+ C & -2 & \textcolor{red}{\textbf{-2}} & -4 & -10 \\
+ T & -4 & -8 & -8 & -6 \\
+ T & -6 & -10 & -12 & -10 \\
+\end{tabular}}
+\subfigure{
+\begin{tabular}{c|cccc}
+ T & 0 & C & C & T \\
+ \hline
+ 0 & -2 & -4 & -6 & -8 \\
+ C & -4 & -4 & -6 & -10 \\
+ T & -6 & -8 & \textcolor{red}{\textbf{-4}} & 2 \\
+ T & -8 & -10 & -8 & 2 \\
+\end{tabular}}
+\subfigure{
+\begin{tabular}{c|cccc}
+ C & 0 & C & C & T \\
+ \hline
+ 0 & -4 & -6 & -8 & -10 \\
+ C & -6 & 2 & 2 & -8 \\
+ T & -8 & -6 & -2 & 0 \\
+ T & -10 & -8 & -6 & \textcolor{red}{\textbf{-6}} \\
+\end{tabular}}
+\caption[DP matrix of MSA]{DP matrix of MSA, traceback is shown in red}
+\end{figure}
+
+\noindent If we fill the DP matrix using this recursion, we get several optimal alignments. One of 
+them is the following:
 
@@
 
-The last step was creating the actual MSA. The 'complete alignment' methode 
+The last step was creating the actual MSA.
+The 'complete alignment' methode was used.
+This means after every step, the distance of the new sequences was determined to each other sequence in the cluster.
+The optimal resulting score was used to get the best alignment for the new Sequence.
+after 3 steps the MSA was completed.
+(figure \ref{completealign})
 \begin{figure}[h]

### 2015-11-06 project/proposal/Project_proposal.tex
added alignments
but still working on comparisons

@@
 Our project is to design and implement a tool for real world.
-The general idea of Poodle is to create a tool which allows lifescience laboratories to organize their own primer- , plasmid- or even culture-libraries.
-Therefore they need a database structure, a graphical user interface (GUI) and some additional functions for their daily duties.
-These additional functions could be a efficient sequence aligning tool (Hirschberg's algorithm).
-Also an integrated BLAST or DIAMOND search, which can adress the internal or external databases like PDB or Genbank.
-Although we know this is a though time consuming idea, we are ready to take our chance and to create something, which could be used in real world.
+The general idea of Poodle is to create a tool which allows life science laboratories to organize their own primer-, plasmid- or even culture-libraries.
+Therefore, they need a database structure, a graphical user interface (GUI) and some additional functions for their daily duties.
+These additional functions could be an efficient sequence aligning tool (Hirschberg's algorithm).
+Also an integrated BLAST or DIAMOND search, which can address the internal or external databases like PDB or Genbank.
+Although we know this is a tough time consuming idea, we are ready to take our chance and to create something, which could be used in real world.
 We already have somebody in mind, we could concretely ask, if they want to develop this idea with us.
@@
 \section{ The Idea}
-Most lifescience labs manage their data for primers and plasmids via excel spreadsheets or other uncomfortable software solutions.
+Most life science labs manage their data for primers and plasmids via excel spreadsheets or other uncomfortable software solutions.
 Especially when these sheets grow over time the disadvantages of those spreadsheets become clear in aspects of time consuming searches or unorganized entries.
@@
 \section{ The Structure}
-General we splitted the project in several modules.
+General we split the project in several modules.
 First we want to list the basic ones.
-These are the database (DB) module, which we want to realise with SQL lite and .csv-files.
+These are the database (DB) module, which we want to realise with SQL-lite and .csv-files.
 These should be automatically loaded into the database and also should be automatically exported.
@@
 This is useful for designing new Arrays or modifying plasmids, because it's is wanted to do the changes in the least amount of steps, which is of only possible if the most similar sequence is known.\\
-Also a alignment tool can be very useful to visualize the found results. For the alignments the Hirschberg algorithm should be used.\\
+Also an alignment tool can be very useful to visualize the found results. For the alignments the Hirschberg algorithm should be used.\\
 The last module idea was to integrate information to the data from other DBs.
-If for example a certain protein or domain is incorporated into a plasmid it is useful to have the PDB reference or even integrated informations of the proteins.
+If for example a certain protein or domain is incorporated into a plasmid it is useful to have the PDB reference or even integrated information’s of the proteins.
+
 	\begin{figure}[h]
@@
 \section{ The Time-Plan}
-Of course time is a important factor.
-Therefore we started to organize a time plan for all of our ideas.
+Of course time is an important factor.
+Therefore, we started to organize a time plan for all of our ideas.
 This is of course the final plan.
-The set up of the DB should be finished in the first two weeks.
+The setup of the DB should be finished in the first two weeks.
 It should be easy to set the DB up from the data we might get from our eventually partner lab.
@@
 Time is the limiting factor of our project.
-Therefore we want to add the modules one after another and if we cannot add all modules in time, this might be the case after the project.
+Therefore, we want to add the modules one after another and if we cannot add all modules in time, this might be the case after the project.
 

### 2015-11-07 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
add die bib datei für unsere referenzen und neueste version vom tex file

@@
 \usepackage{ifthen}
+\usepackage{cite}
 %\usepackage{TikZ} %phylogenetischer Baum
@@
 Afterwards the global optima were entered into a new table, which was used to generate the guide tree in the second step.(figure \ref{DP2}).
-\begin{figure}[h]
-	\includegraphics[width=\textwidth]{Img/Exercise2-DP-Matrix.png}
+\begin{figure}[ht]
+        \centering
+	\includegraphics[width=0.7\textwidth]{Img/Exercise2-DP-Matrix.png}
 	\caption{ Global alignments lead to the basis table used to generate the guide tree}
@@
 
-\begin{figure}[h]
-	\includegraphics[width=\textwidth]{Img/Exercise2-Guidetree.png}
+\begin{figure}[ht]
+        \centering
+	\includegraphics[width=0.7\textwidth]{Img/Exercise2-Guidetree.png}
 	\caption{ The guide tree is made from the final table from step 1}
@@
 (figure \ref{completealign})
-\begin{figure}[h]
-	\includegraphics[width=\textwidth]{Img/Exercise2-CompleteAlignment.png}
+\begin{figure}[ht]
+        \centering
+	\includegraphics[width=0.7\textwidth]{Img/Exercise2-CompleteAlignment.png}
 	\caption{ Complete alignment methode is used to get an MSA from the guidetree from step 2	}
@@
 \end{figure}
+
 \section*{Practical Assignment - \textsl{Comparing multiple alignment}}
+Multiple sequence alignments (MSA) are very important to detect similarities between several 
+sequences and e.g. determine whether a sequence belongs to a certain family or not. Hence, many 
+different programs, such as ClustalW, were developed to calculate a MSA. We calculated a multiple 
+sequence alignment for three files (BB11007, BB20002 and Prolyl-tRNA), each file contained several 
+sequences, with different programs 
+to compare the results. The used programs are MAFFT\cite{Katoh1}, MUSCLE\cite{Edgar1, Edgar2} and 
+Clustal$\Omega$\cite{Sievers539}. The resulting MSAs were compared with a gold standard provided by 
+BaliBase\cite{Bahr1}. This database provide a large number of reference MSAs as well as a program 
+\grqq BaliScore\grqq , which can be used to calculate different scores to evaluate your MSA. For 
+this assignment we are interested in the total column score, which is the percentage of accurately 
+reconstructed columns of the reference MSA, and the sum-of-pair score, which is for BaliScore the 
+percentage of pairs of aligned residues that are similar in the reference and the reconstructed 
+MSA. Furthermore, a important information is the runtime of different programs. We used the bash 
+command \textit{time} to collect this information.\\
+\\
+\noindent The resulting total column scores can be found in figure \ref{totCol}. All calculated sum-
+of-pairs scores are written down in figure \ref{SPscore} and the runtime of all programs can be found 
+in figure \ref{runtime}.
+
+\begin{figure}[ht]
+ \centering
+ \subfigure{
+ \begin{tabular}{c|ccc}
+  \textit{total column score} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
+  \hline
+  \textbf{BB11007} & $c_{1,1}$ & $c_{2,1}$ & $c_{3,1}$ \\
+  \textbf{BB20002} & $c_{1,2}$ & $c_{2,2}$ & $c_{3,2}$ \\
+  \textbf{Prolyl-tRNA} & $c_{1,3}$ & $c_{2,3}$ & $c_{3,3}$ \\
+ \end{tabular}}
+ \caption{total column score of all used programs for example files}
+ \label{totCol}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \subfigure{
+ \begin{tabular}{c|ccc}
+   \textit{SP-score}& \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
+  \hline
+  \textbf{BB11007} & $s_{1,1}$ & $s_{2,1}$ & $s_{3,1}$ \\
+  \textbf{BB20002} & $s_{1,2}$ & $s_{2,2}$ & $s_{3,2}$ \\
+  \textbf{Prolyl-tRNA} & $s_{1,3}$ & $s_{2,3}$ & $s_{3,3}$ \\
+ \end{tabular}}
+ \caption{sum-of-pairs score of all used programs for example files}
+ \label{SPscore}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \subfigure{
+ \begin{tabular}{c|ccc}
+  \textit{runtime} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
+  \hline
+  \textbf{BB11007} & $t_{1,1}$ & $t_{2,1}$ & $t_{3,1}$ \\
+  \textbf{BB20002} & $t_{1,2}$ & $t_{2,2}$ & $t_{3,2}$ \\
+  \textbf{Prolyl-tRNA} & $t_{1,3}$ & $t_{2,3}$ & $t_{3,3}$ \\
+ \end{tabular}}
+ \caption{runtime of all used programs for example files}
+ \label{runtime}
+\end{figure}
+
+\newpage
+\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
+\bibliographystyle{ieeetr}
 

### 2015-11-07 poodle_project/src/com/example/poodle_project_code/Poodle_project_codeUI.java
Sequences and project structure

@@ -1,0 +1,39 @@
+package com.example.poodle_project_code;
+
+import javax.servlet.annotation.WebServlet;
+
+import com.vaadin.annotations.Theme;
+import com.vaadin.annotations.VaadinServletConfiguration;
+import com.vaadin.server.VaadinRequest;
+import com.vaadin.server.VaadinServlet;
+import com.vaadin.ui.Button;
+import com.vaadin.ui.Button.ClickEvent;
+import com.vaadin.ui.Label;
+import com.vaadin.ui.UI;
+import com.vaadin.ui.VerticalLayout;
+
+@SuppressWarnings("serial")
+@Theme("poodle_project_code")
+public class Poodle_project_codeUI extends UI {
+
+	@WebServlet(value = "/*", asyncSupported = true)
+	@VaadinServletConfiguration(productionMode = false, ui = Poodle_project_codeUI.class)
+	public static class Servlet extends VaadinServlet {
+	}
+
+	@Override
+	protected void init(VaadinRequest request) {
+		final VerticalLayout layout = new VerticalLayout();
+		layout.setMargin(true);
+		setContent(layout);
+
+		Button button = new Button("Click Me");
+		button.addClickListener(new Button.ClickListener() {
+			public void buttonClick(ClickEvent event) {
+				layout.addComponent(new Label("Thank you for clicking"));
+			}
+		});
+		layout.addComponent(button);
+	}
+
+}

### 2015-11-07 poodle_project/test/com/example/poodle_project_code/Poodle_project_codeTest.java

@@ -1,0 +1,87 @@
+package com.example.poodle_project_code;
+
+import com.vaadin.testbench.ScreenshotOnFailureRule;
+import com.vaadin.testbench.TestBenchTestCase;
+import com.vaadin.testbench.elements.ButtonElement;
+import com.vaadin.testbench.elements.LabelElement;
+
+import org.junit.Before;
+import org.junit.Rule;
+import org.junit.Test;
+import org.openqa.selenium.firefox.FirefoxDriver;
+
+import java.util.List;
+
+import static org.junit.Assert.assertEquals;
+import static org.junit.Assert.assertFalse;
+
+/**
+ * This class contains JUnit tests, which are run using Vaadin TestBench 4.
+ *
+ * To run this, first get an evaluation license from
+ * https://vaadin.com/addon/vaadin-testbench and follow the instructions at
+ * https://vaadin.com/directory/help/installing-cval-license to install it.
+ *
+ * Once the license is installed, you can run this class as a JUnit test.
+ */
+public class Poodle_project_codeTest extends TestBenchTestCase {
+    @Rule
+    public ScreenshotOnFailureRule screenshotOnFailureRule =
+            new ScreenshotOnFailureRule(this, true);
+
+    @Before
+    public void setUp() throws Exception {
+        setDriver(new FirefoxDriver()); // Firefox
+
+        // To use Chrome, first install chromedriver.exe from
+        // http://chromedriver.storage.googleapis.com/index.html
+        // on your system path (e.g. C:\Windows\System32\)
+        //   setDriver(new ChromeDriver()); // Chrome
+
+        // To use Internet Explorer, first install iedriverserver.exe from
+        // http://selenium-release.storage.googleapis.com/index.html?path=2.43/
+        // on your system path (e.g. C:\Windows\System32\)
+        //   setDriver(new InternetExplorerDriver()); // IE
+
+        // To test headlessly (without a browser), first install phantomjs.exe
+        // from http://phantomjs.org/download.html on your system path
+        // (e.g. C:\Windows\System32\)
+        //   setDriver(new PhantomJSDriver()); // PhantomJS headless browser
+    }
+
+    /**
+     * Opens the URL where the application is deployed.
+     */
+    private void openTestUrl() {
+        getDriver().get("http://localhost:8080/poodle_project_code");
+    }
+
+    @Test
+    public void testClickButton() throws Exception {
+        openTestUrl();
+
+        // At first there should be no labels
+        assertFalse($(LabelElement.class).exists());
+
+        // Click the button
[…]

### 2015-11-07 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
neueste version der tex datei beschreibung der methoden hinzugefügt

@@
 sequences, with different programs 
-to compare the results. The used programs are MAFFT\cite{Katoh1}, MUSCLE\cite{Edgar1, Edgar2} and 
-Clustal$\Omega$\cite{Sievers539}. The resulting MSAs were compared with a gold standard provided by 
+to compare the results. The used programs are Clustal$\Omega$\cite{Sievers539}, MAFFT\cite{Katoh1} 
+and MUSCLE\cite{Edgar1, Edgar2}. The resulting MSAs were compared with a gold standard provided by 
 BaliBase\cite{Bahr1}. This database provide a large number of reference MSAs as well as a program 
@@
 command \textit{time} to collect this information.\\
+\\
+\noindent Clustal$\Omega$ is the newest extension for the Clustal family. One problem of ClustalW 
+was the scalability. With Clustal$\Omega$ a MSA can now calculated for hundreds of thousands of 
+sequences within a few hours. On the technical side the algorithm can use multiple processors. 
+According to the official site\footnote{http://www.clustal.org/omega/}, Clustal$\Omega$ produces 
+better alignments than previous versions. MAFFT offers several modes. The L-INS-i mode is 
+slower and only suitable for alignments with less than 200 sequences but results in a more accurate 
+alignment. Contrary to that mode the FFT-NS-2 mode can be used to align up to 300.000 sequences. It 
+is a lot faster by using the Fast Fourier Transformation but also less accurate. We used the 
+FFT-NS-2 mode for this assignment. The third program MUSCLE is a iterative approach to multiple 
+sequence alignments. It uses a very accurate distance measure two calculate relatedness of two 
+sequences and updates this distance measure for every iteration step.\\
 \\
@@
   \hline
-  \textbf{BB11007} & $c_{1,1}$ & $c_{2,1}$ & $c_{3,1}$ \\
-  \textbf{BB20002} & $c_{1,2}$ & $c_{2,2}$ & $c_{3,2}$ \\
+  \textbf{BB11007} & 0.33 & 0.39 & 0.24 \\
+  \textbf{BB20002} & 0.00 & 0.00 & 0.00 \\
   \textbf{Prolyl-tRNA} & $c_{1,3}$ & $c_{2,3}$ & $c_{3,3}$ \\
@@
   \hline
-  \textbf{BB11007} & $s_{1,1}$ & $s_{2,1}$ & $s_{3,1}$ \\
-  \textbf{BB20002} & $s_{1,2}$ & $s_{2,2}$ & $s_{3,2}$ \\
+  \textbf{BB11007} & 0.597 & 0.582 & 0.524 \\
+  \textbf{BB20002} & 0.314 & 0.197 & 0.246 \\
   \textbf{Prolyl-tRNA} & $s_{1,3}$ & $s_{2,3}$ & $s_{3,3}$ \\

### 2015-11-07 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
update of .tex file

@@
  \end{tabular}}
- \caption{total column score of all used programs for example files}
+ \caption{total column score of all alignments}
  \label{totCol}
@@
  \end{tabular}}
- \caption{sum-of-pairs score of all used programs for example files}
+ \caption{sum-of-pairs score of all alignments}
  \label{SPscore}
@@
   \hline
-  \textbf{BB11007} & $t_{1,1}$ & $t_{2,1}$ & $t_{3,1}$ \\
-  \textbf{BB20002} & $t_{1,2}$ & $t_{2,2}$ & $t_{3,2}$ \\
+  \textbf{BB11007} & 0.389 & 0.488 & 0.13 \\
+  \textbf{BB20002} & 6.62 & 19.928 & 0.38 \\
   \textbf{Prolyl-tRNA} & $t_{1,3}$ & $t_{2,3}$ & $t_{3,3}$ \\
  \end{tabular}}
- \caption{runtime of all used programs for example files}
+ \caption{runtime of all used programs for example files (in sec)}
  \label{runtime}

### 2015-11-07 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
updated of .tex file
pratical assignment sollte jetzt soweit fertig sein

@@
 of-pairs scores are written down in figure \ref{SPscore} and the runtime of all programs can be found 
-in figure \ref{runtime}.
+in figure \ref{runtime}. One can see that the total column score as well as the sum-of-pairs 
+score for Prolyl-tRNA is missing. Although we calculated the MSAs with all three programs for these 
+sequences, BaliScore was not able to calculate a score. We got a memory error, even with five Gb 
+accessible memory. Also interesting is the total column score for the second biggest file, BB20002. 
+BaliScore calculated a score of 0.00 for all of the three programms. If we assume that the 
+program calculated valid scores, one can see that the gold standard provided by BaliBase differs 
+a lot compared to the calculated MSAs. Even for the smallest file, BB11007, the total column score 
+barely reaches 0.4. That means only 40 percent of the columns in the reference MSA were identically 
+reproduced by our used algorithms. Since all three programs are heuristics, it is not surprising 
+that the calculated MSAs are not similar with the gold standard. One can explain such a big difference 
+with the occurrence of several optimal MSAs of the sequences. And the algorithms have calculated 
+another MSA than the gold standard. Another explanation for our results would be that the heuristics 
+worked worst than expected. By comparing runtimes of Clustal$\Omega$, MUSCLE and MAFFT one can see 
+that MUSCLE is by far the slowest program. This is logical, since MUSCLE is a iterative approach to 
+multiple sequence alignment. But our results for MUSCLE are not significant better than for the other 
+algorithms. So in that case we paid with a lot of computational time for no improvement.
 
@@
   \textbf{BB20002} & 0.00 & 0.00 & 0.00 \\
-  \textbf{Prolyl-tRNA} & $c_{1,3}$ & $c_{2,3}$ & $c_{3,3}$ \\
+  \textbf{Prolyl-tRNA} & - & - & - \\
  \end{tabular}}
@@
   \textbf{BB20002} & 0.314 & 0.197 & 0.246 \\
-  \textbf{Prolyl-tRNA} & $s_{1,3}$ & $s_{2,3}$ & $s_{3,3}$ \\
+  \textbf{Prolyl-tRNA} & - & - & - \\
  \end{tabular}}
@@
   \textbf{BB20002} & 6.62 & 19.928 & 0.38 \\
-  \textbf{Prolyl-tRNA} & $t_{1,3}$ & $t_{2,3}$ & $t_{3,3}$ \\
+  \textbf{Prolyl-tRNA} & 16.11 & 4116.97 & 7.72 \\
  \end{tabular}}

### 2015-11-08 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
cites for programms

@@
-%\textsl{}%!TEX TS-options = --shell-escape
+bb%\textsl{}%!TEX TS-options = --shell-escape
 %!TEX TS-program = pdflatex
@@
 \\
-\noindent Clustal$\Omega$ is the newest extension for the Clustal family. One problem of ClustalW 
+\noindent Clustal$\Omega$ \cite{Sievers539} is the newest extension for the Clustal family. One problem of ClustalW 
 was the scalability. With Clustal$\Omega$ a MSA can now calculated for hundreds of thousands of 
@@
 According to the official site\footnote{http://www.clustal.org/omega/}, Clustal$\Omega$ produces 
-better alignments than previous versions. MAFFT offers several modes. The L-INS-i mode is 
+better alignments than previous versions. MAFFT\cite{Katoh1} offers several modes. The L-INS-i mode is 
 slower and only suitable for alignments with less than 200 sequences but results in a more accurate 
@@
 is a lot faster by using the Fast Fourier Transformation but also less accurate. We used the 
-FFT-NS-2 mode for this assignment. The third program MUSCLE is a iterative approach to multiple 
+FFT-NS-2 mode for this assignment. The third program MUSCLE \cite{Edgar1} his a iterative approach to multiple 
 sequence alignments. It uses a very accurate distance measure two calculate relatedness of two 

### 2015-11-10 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
A neeeeeeeeeeeeeew Round Assignment 5

--- 2015-11-07 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
@@
 
-{(Abgabe am #3)} % Abgabedatum
+{(Handed in #3)} % Abgabedatum
 \end{center}
@@
   \begin{vartab}{\thecolmns}
-    \numbers{#1} & $\sum$\\\hline
+    \numbers{#1} & $\sum$ (7)\\\hline   %add here Complete number of points ---------------------------
     \emptyLine{\thecolmns}\\
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{4}{Alexander Seitz}{9. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
+\header{5}{Alexander Seitz}{16. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{4}
 
 \section*{Theoretical Assignment - \textsl{Optimal multiple alignment}}
-
-To calculate our MSA we use the recursion written down on page 50 in the script.
-
-\begin{equation}
- F(i_1, i_2, i_3) = max \begin{cases}
-                         F(i_1 -1, i_2 -1, i_3 -1) + s_{SP}(a_{1i_1},a_{2i_2},a_{3i_3}) \\
-                         \\
-                         F(i_1 -1, i_2 -1, i_3) + s_{SP}(a_{1i_1},a_{2i_2},-) \\
-                         F(i_1 -1, i_2, i_3 -1) + s_{SP}(a_{1i_1},-,a_{3i_3}) \\
-                         F(i_1, i_2 -1, i_3 -1) + s_{SP}(-,a_{2i_2},a_{3i_3}) \\
-                         \\
-                         F(i_1 -1, i_2, i_3) + s_{SP}(a_{1i_1},-,-) \\
-                         F(i_1, i_2 -1, i_3) + s_{SP}(-,a_{2i_2},-) \\
-                         F(i_1, i_2, i_3 -1) + s_{SP}(-,-,a_{3i_3}) \\
-                        \end{cases} \nonumber
-\end{equation}
-
-\noindent Such a recursion results in a three-dimensional matrix. Since such a matrix is really difficult to 
-sketch, we split it into three two-dimensional matrices.
-
-\begin{figure}[ht]
-\centering
-\subfigure{
-\begin{tabular}{c|cccc}
- 0 & 0 & C & C & T \\
- \hline
- 0 & \textcolor{red}{\textbf{0}} & -2 & -4 & -6 \\
- C & -2 & \textcolor{red}{\textbf{-2}} & -4 & -10 \\
- T & -4 & -8 & -8 & -6 \\
- T & -6 & -10 & -12 & -10 \\
-\end{tabular}}
-\subfigure{
-\begin{tabular}{c|cccc}
- T & 0 & C & C & T \\
- \hline
- 0 & -2 & -4 & -6 & -8 \\
- C & -4 & -4 & -6 & -10 \\
- T & -6 & -8 & \textcolor{red}{\textbf{-4}} & 2 \\
- T & -8 & -10 & -8 & 2 \\
-\end{tabular}}
-\subfigure{
-\begin{tabular}{c|cccc}
- C & 0 & C & C & T \\
- \hline
- 0 & -4 & -6 & -8 & -10 \\
- C & -6 & 2 & 2 & -8 \\
- T & -8 & -6 & -2 & 0 \\
- T & -10 & -8 & -6 & \textcolor{red}{\textbf{-6}} \\
-\end{tabular}}
-\caption[DP matrix of MSA]{DP matrix of MSA, traceback is shown in red}
-\end{figure}
-
-\noindent If we fill the DP matrix using this recursion, we get several optimal alignments. One of 
-them is the following:
-
-\begin{equation}
- \begin{pmatrix}
-  C & T & T \\
-  - & T & C \\
-  C & C & T
- \end{pmatrix}
-\end{equation}
-
-\noindent with score $\alpha_{SP}(A^*) = S(A,B) + S(A,C) + S(B,C) = -2 + 2 + (-6) = -6$.
-
-\section*{Theoretical Assignment - \textsl{Progressive alignment}}
-Progressive alignment methodes are one way to create multiple sequence alignments (MSA), in this task we had to accomplish manualy a progressive alignment.
-The first step for the progressive alignment was to generate the pairwise global distance matrices.
-Afterwards the global optima were entered into a new table, which was used to generate the guide tree in the second step.(figure \ref{DP2}).
-\begin{figure}[ht]
-        \centering
-	\includegraphics[width=0.7\textwidth]{Img/Exercise2-DP-Matrix.png}
-	\caption{ Global alignments lead to the basis table used to generate the guide tree}
-	\label{DP2}
-\end{figure}
-
-In step 2 the guide tree was created by the UPGMA methode in 3 substeps.
-After every step, which added a new cluster, the distance table was updated.
-The result from this step was the guide tree, which was used to apply the 'complete alignment' methode in the last step, the progressive alignment step.(figure \ref{guidetree2})
-
-\begin{figure}[ht]
-        \centering
-	\includegraphics[width=0.7\textwidth]{Img/Exercise2-Guidetree.png}
-	\caption{ The guide tree is made from the final table from step 1}
-	\label{guidetree2}
-\end{figure}
-
-The last step was creating the actual MSA.
-The 'complete alignment' methode was used.
-This means after every step, the distance of the new sequences was determined to each other sequence in the cluster.
-The optimal resulting score was used to get the best alignment for the new Sequence.
-after 3 steps the MSA was completed.
-(figure \ref{completealign})
-\begin{figure}[ht]
-        \centering
-	\includegraphics[width=0.7\textwidth]{Img/Exercise2-CompleteAlignment.png}
-	\caption{ Complete alignment methode is used to get an MSA from the guidetree from step 2	}
-	\label{completealign}
-\end{figure}
-
-\section*{Practical Assignment - \textsl{Comparing multiple alignment}}
-Multiple sequence alignments (MSA) are very important to detect similarities between several 
-sequences and e.g. determine whether a sequence belongs to a certain family or not. Hence, many 
-different programs, such as ClustalW, were developed to calculate a MSA. We calculated a multiple 
-sequence alignment for three files (BB11007, BB20002 and Prolyl-tRNA), each file contained several 
-sequences, with different programs 
-to compare the results. The used programs are Clustal$\Omega$\cite{Sievers539}, MAFFT\cite{Katoh1} 
-and MUSCLE\cite{Edgar1, Edgar2}. The resulting MSAs were compared with a gold standard provided by 
-BaliBase\cite{Bahr1}. This database provide a large number of reference MSAs as well as a program 
-\grqq BaliScore\grqq , which can be used to calculate different scores to evaluate your MSA. For 
-this assignment we are interested in the total column score, which is the percentage of accurately 
-reconstructed columns of the reference MSA, and the sum-of-pair score, which is for BaliScore the 
-percentage of pairs of aligned residues that are similar in the reference and the reconstructed 
-MSA. Furthermore, a important information is the runtime of different programs. We used the bash 
-command \textit{time} to collect this information.\\
-\\
-\noindent Clustal$\Omega$ is the newest extension for the Clustal family. One problem of ClustalW 
-was the scalability. With Clustal$\Omega$ a MSA can now calculated for hundreds of thousands of 
-sequences within a few hours. On the technical side the algorithm can use multiple processors. 
-According to the official site\footnote{http://www.clustal.org/omega/}, Clustal$\Omega$ produces 
-better alignments than previous versions. MAFFT offers several modes. The L-INS-i mode is 
-slower and only suitable for alignments with less than 200 sequences but results in a more accurate 
-alignment. Contrary to that mode the FFT-NS-2 mode can be used to align up to 300.000 sequences. It 
-is a lot faster by using the Fast Fourier Transformation but also less accurate. We used the 
-FFT-NS-2 mode for this assignment. The third program MUSCLE is a iterative approach to multiple 
-sequence alignments. It uses a very accurate distance measure two calculate relatedness of two 
-sequences and updates this distance measure for every iteration step.\\
-\\
-\noindent The resulting total column scores can be found in figure \ref{totCol}. All calculated sum-
-of-pairs scores are written down in figure \ref{SPscore} and the runtime of all programs can be found 
-in figure \ref{runtime}.
-
-\begin{figure}[ht]
- \centering
- \subfigure{
- \begin{tabular}{c|ccc}
-  \textit{total column score} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
-  \hline
-  \textbf{BB11007} & 0.33 & 0.39 & 0.24 \\
-  \textbf{BB20002} & 0.00 & 0.00 & 0.00 \\
-  \textbf{Prolyl-tRNA} & $c_{1,3}$ & $c_{2,3}$ & $c_{3,3}$ \\
- \end{tabular}}
- \caption{total column score of all alignments}
- \label{totCol}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \subfigure{
- \begin{tabular}{c|ccc}
-   \textit{SP-score}& \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
-  \hline
-  \textbf{BB11007} & 0.597 & 0.582 & 0.524 \\
-  \textbf{BB20002} & 0.314 & 0.197 & 0.246 \\
-  \textbf{Prolyl-tRNA} & $s_{1,3}$ & $s_{2,3}$ & $s_{3,3}$ \\
- \end{tabular}}
- \caption{sum-of-pairs score of all alignments}
- \label{SPscore}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \subfigure{
- \begin{tabular}{c|ccc}
-  \textit{runtime} & \textbf{Clustal$\Omega$} & \textbf{MUSCLE} & \textbf{MAFFT} \\
-  \hline
-  \textbf{BB11007} & 0.389 & 0.488 & 0.13 \\
-  \textbf{BB20002} & 6.62 & 19.928 & 0.38 \\
-  \textbf{Prolyl-tRNA} & $t_{1,3}$ & $t_{2,3}$ & $t_{3,3}$ \\
- \end{tabular}}
- \caption{runtime of all used programs for example files (in sec)}
- \label{runtime}
-\end{figure}
 

### 2015-11-10 poodle_project/src/Test/testing.java

@@ -1,0 +1,38 @@
+package Test;
+
+import com.vaadin.annotations.Theme;
+import com.vaadin.server.VaadinRequest;
+import com.vaadin.ui.*;
+import com.vaadin.*;
+@Theme("myProject")
+
+public class testing extends UI {
+	 @Override
+	    protected void init(VaadinRequest request) {
+	        // The root of the component hierarchy
+	        VerticalLayout content = new VerticalLayout();
+	        content.setSizeFull(); // Use entire window
+	        setContent(content);   // Attach to the UI
+	        
+	        // Add some component
+	        content.addComponent(new Label("Hello!"));
+	        
+	        // Layout inside layout
+	        HorizontalLayout hor = new HorizontalLayout();
+	        hor.setSizeFull(); // Use all available space
+
+	        // Couple of horizontally laid out components
+	        Tree tree = new Tree("My Tree",
+	                TreeExample.createTreeContent());
+	        hor.addComponent(tree);
+
+	        Table table = new Table("My Table",
+	                TableExample.generateContent());
+	        table.setSizeFull();
+	        hor.addComponent(table);
+	        hor.setExpandRatio(table, 1); // Expand to fill
+
+	        content.addComponent(hor);
+	        content.setExpandRatio(hor, 1); // Expand to fill
+	    }
+}

### 2015-11-11 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
nicht viel passiert nur die überschriften hinzugefügt
erster lösungsvorschlag für aufgabe 1

@@
 
-\section*{Theoretical Assignment - \textsl{Optimal multiple alignment}}
+\section*{Theoretical Assignment - \textsl{Comparison with at most $l$ mismatches}}
 
-\newpage
-\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
-\bibliographystyle{ieeetr}
+Assume two sequences of length t with l mismatches. In the worst case, all mismatches are 
+distributed uniformly. Than both sequences will share $l+1$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$.\\
+\\
+\noindent So both sequences share $l+1$ k-tuples of length $k = \lfloor\frac{t}{l+1}\rfloor$ and for each 
+$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $l+1 * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
+k-tuples.
+
+\section*{Theoretical Assignment - \textsl{Linear programming by hand}}
+
+\section*{Theoretical Assignment - \textsl{Bonus: Carillo-Lipman bound}}
+
+%\newpage
+%\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
+%\bibliographystyle{ieeetr}
 

### 2015-11-11 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
viele viele bunte smarties

@@
 \noindent So both sequences share $l+1$ k-tuples of length $k = \lfloor\frac{t}{l+1}\rfloor$ and for each 
-$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $l+1 * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
+$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
 k-tuples.
@@
 \section*{Theoretical Assignment - \textsl{Linear programming by hand}}
+
+The feasible region of this linear program is shown in figure \ref{feasibleRegion}, where the red line 
+is constraint 1, green line is constraint 2, constraint 3 is drawn as a blue line and the yellow line 
+is constraint 4.
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.7\textwidth]{img/figure_1.png}
+ \caption{feasible region of linear program}
+ \label{feasibleRegion}
+\end{figure}
 

### 2015-11-11 AssignmentV/drawLPArea.py

@@ -1,0 +1,14 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+x = np.arange(0.,8.)
+
+y1 = 12-2*x
+y2 = 7-x
+y3 = (16-2*x)/3
+y4 = (6+x)/2
+
+plt.ylim(0,14)
+plt.plot(x,y1,'r', x,y2,'g', x,y3,'b', x,y4,'y')
+plt.fill_between(x,y3,y1, color='grey', alpha='0.5')
+plt.show()

### 2015-11-11 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
Final_Benni_EX1
Hab das nohcmal durchgelesen und meiner meinung nahc angepasst an unser
besprochenes

@@
 
-Assume two sequences of length t with l mismatches. In the worst case, all mismatches are 
-distributed uniformly. Than both sequences will share $l+1$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$.\\
+General we are now only looking at the worst case scenario, which means uniform distributed mistmatches in an alignment.
+Also we only look at $k>=1$, as $k=0$ is in our application not a useful result.
+Assume two sequences of length t with l mismatches.\\
+ Than both sequences contain $l$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ .
+Where $k = \lfloor\frac{t}{l+1}\rfloor$ is the maximal tuple length, possible in both sequences.\\
 \\
-\noindent So both sequences share $l+1$ k-tuples of length $k = \lfloor\frac{t}{l+1}\rfloor$ and for each 
+\noindent So both sequences share $l+1$ k-tuples and for each 
 $k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$

### 2015-11-11 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
soulution if t=1=s

@@
  Than both sequences contain $l$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ .
-Where $k = \lfloor\frac{t}{l+1}\rfloor$ is the maximal tuple length, possible in both sequences.\\
+Where $k = \lfloor\frac{t}{l+1}\rfloor$ is the maximal tuple length, possible in sequences.\\
 \\
@@
  \includegraphics[width=0.7\textwidth]{img/figure_1.png}
- \caption{feasible region of linear program}
+ \caption{feasible region of linear program (grey area)}
  \label{feasibleRegion}
 \end{figure}
+
+\subsection*{solution if t=s=1}
+Generally we only used integers in this task. The constraint for the algortihm are as following if t and s value is 1 now:
+
+\begin{eqnarray}
+max: 1*x_1+1*x_2 \label{con1}\\ 
+2*x_1+x_2 \le 12 \label{con2}\\ 
+2*x_1+3*x_2 \le 7 \label{con3}\\ 
+-1*x_1+2*x_2 \le 16 \label{con4}\\ 
+x_1,x_2 \ge 0 \label{con5}
+\end{eqnarray}
+
+In the next step we started to compute each line of the tuple.
+Starting with constraint \ref{con3} under the aspect of constraint \ref{con5}.
+All possible tuples respectivly to both constraints from the assignment are:\\
+$temp1=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);(6,1);(7,0)\}$\\
+
+Next the constraint \ref{con2} was applied to temp1:\\
+$temp2=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);\}$\\
+
+Again the next constraint (contraint \ref{con4}) was applied:\\
+$temp3=\{(5,2)\}$\\
+
+Last but not least the last constraint (4) is checked and the remaining tuple from the last step is valid:\\
+$r=\{(5,2)\}$\\
+
+So the final result for the Algorithm with s=t=1 is the Dupel: (5,2).\\
+
+\subsection*{How to make unsolveable?}
+To get a not solveable algorithm for example the following constraint could be added:
+	\begin{equation}\\
+		x_1+x_2\ge 7
+	\end{equation}
+
+\subsection*{How to get infinite solutions with t and s?}
+
+\subsection*{how to get the points? ?}
+
+P1=(0,3)
+P2=(2,4)
+P3=(1,3)
+P4=(6,0)
 

### 2015-11-12 AssignmentV/drawLPArea.py
I was playing around with drawLPArea.py

@@ -10,5 +10,8 @@ y4 = (6+x)/2
 
 plt.ylim(0,14)
 plt.plot(x,y1,'r', x,y2,'g', x,y3,'b', x,y4,'y')
-plt.fill_between(x,y3,y1, color='grey', alpha='0.5')
+plt.fill_between(x,y1, color='r', alpha='0.5')
+plt.fill_between(x,y2, color='g', alpha='0.5')
+plt.fill_between(x,y3, color='b', alpha='0.5')
+plt.fill_between(x,y4, color='y', alpha='0.5')
 plt.show()

### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
Unsolveable solution

@@
 
+Generally a new constraint just needs to be a contradiction to another constraint.
+
 \subsection*{How to get infinite solutions with t and s?}
+The equation influence by t and s is:
+
+\begin{equation*}
+max: s*x_1+t*x_2
+\end{equation*}
+
+One way to get an infinite solution could be to generate a endless loop with values for s and t like:
+\begin{eqnarray*}
+s=s*x_1\label{inf1}\\ 
+t=t*x_2 \label{inf2}\\ 
+or\\
+s=t*x_2\label{inf3}\\ 
+t=s*x_1 \label{inf4}\\ 
+\end{eqnarray*}
+
+Best idea of the evening:
+Do not assume to only use integers!
+Another variant is to define:
+\begin{eqnarray*}
+	s=\frac{1}{x_1}\\
+	t=\frac{1}{x_2}\\ 
+\end{eqnarray*}
+the result for Z now is 2 and there are infinite many possibilities to get to 2.
 

### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
ein paar layout und typo verbesserungen

@@
 \subsection*{solution if t=s=1}
-Generally we only used integers in this task. The constraint for the algortihm are as following if t and s value is 1 now:
+Generally we only used integers in this task. The constraint for the algorithm are as following if t and s value is 1 now:
 
@@
 
-In the next step we started to compute each line of the tuple.
+\noindent the next step we started to compute each line of the tuple.
 Starting with constraint \ref{con3} under the aspect of constraint \ref{con5}.
-All possible tuples respectivly to both constraints from the assignment are:\\
+All possible tuples respectively to both constraints from the assignment are:\\
 $temp1=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);(6,1);(7,0)\}$\\
 
-Next the constraint \ref{con2} was applied to temp1:\\
+\noindent the constraint \ref{con2} was applied to temp1:\\
 $temp2=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);\}$\\
 
-Again the next constraint (contraint \ref{con4}) was applied:\\
+\noindent the next constraint (constraint \ref{con4}) was applied:\\
 $temp3=\{(5,2)\}$\\
 
-Last but not least the last constraint (4) is checked and the remaining tuple from the last step is valid:\\
+\noindent but not least the last constraint (4) is checked and the remaining tuple from the last step is valid:\\
 $r=\{(5,2)\}$\\
 
-So the final result for the Algorithm with s=t=1 is the Dupel: (5,2).\\
+\noindent the final result for the Algorithm with s=t=1 is the tuple: (5,2). Solving the formula with this numbers 
+leads us to the following maximal value: $1*x_1 + 1*x_2 = 5+2 = 7$\\
 
-\subsection*{How to make unsolveable?}
-To get a not solveable algorithm for example the following constraint could be added:
+\subsection*{How to make unsolvable?}
+To get a not solvable algorithm for example the following constraint could be added:
 	\begin{equation}\\
@@
 
-Generally a new constraint just needs to be a contradiction to another constraint.
+\noindent a new constraint just needs to be a contradiction to another constraint.
 
@@
 
-One way to get an infinite solution could be to generate a endless loop with values for s and t like:
+\noindent way to get an infinite solution could be to generate a endless loop with values for s and t like:
 \begin{eqnarray*}
@@
 
-Best idea of the evening:
+\noindent idea of the evening:
 Do not assume to only use integers!
@@
 
-\subsection*{how to get the points? ?}
+\subsection*{how to get the points?}
 
-P1=(0,3)
-P2=(2,4)
-P3=(1,3)
+P1=(0,3)\\
+P2=(2,4)\\
+P3=(1,3)\\
 P4=(6,0)

### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
ein paar weitere "verbesserungen" für die erste aufgabe

@@
 Assume two sequences of length t with l mismatches.\\
- Than both sequences contain $l$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ .
-Where $k = \lfloor\frac{t}{l+1}\rfloor$ is the maximal tuple length, possible in sequences.\\
+ Than both sequences contain $l$ tuples of length $L = \lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ . \\
 \\
-\noindent So both sequences share $l+1$ k-tuples and for each 
-$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
+\noindent So both sequences share $l$ or $l+1$ k-tuples, if $k = \lfloor\frac{t}{l+1}\rfloor$, and for each 
+$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{L}{k}\rfloor$
 k-tuples.

### 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
aufgabe 2 weiter bearbeitet

@@
 \begin{eqnarray}
-max: 1*x_1+1*x_2 \label{con1}\\ 
-2*x_1+x_2 \le 12 \label{con2}\\ 
+max. 1*x_1+1*x_2 \label{con1}\\ 
+s.t. 2*x_1+x_2 \le 12 \label{con2}\\ 
 2*x_1+3*x_2 \le 7 \label{con3}\\ 
@@
 
-\noindent idea of the evening:
-Do not assume to only use integers!
-Another variant is to define:
-\begin{eqnarray*}
-	s=\frac{1}{x_1}\\
-	t=\frac{1}{x_2}\\ 
-\end{eqnarray*}
-the result for Z now is 2 and there are infinite many possibilities to get to 2.
-
 \subsection*{how to get the points?}
 
-P1=(0,3)\\
+For the first point $P_1=(0,3)$ we have to set $s = -1$ and $t = 1$. That result in a maximal value 
+for (0,3) because we cannot set $x_2$ arbitrary big due to constraint 4. And if we assign a bigger 
+value to $x_1$, would decrease the result. Also we would violate constraint 2, if $x_1$ is to big.\\
+\\
 P2=(2,4)\\
 P3=(1,3)\\
-P4=(6,0)
+\\
+\noindent To make $P_4=(6,0)$ the maximum we set $s = 1$ and $t = -1$. We cannot set $x_1$ to a bigger value 
+than 6 without violating constraint 1.
 

### 2015-11-13 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
Another point (P=2/4) and infinity

@@
 \subsection*{How to get infinite solutions with t and s?}
+
+Getting infinite solutions,  requires to describe with the max function of a linear algorithm a line in the feasible region and not just one point.
+Therefore we decided to use constraint 3 and wanted to generate a max function along constraint (3).
+For the modelling of the max function we used two points from constraint (3) ($P_1(2,4); P_2(5,2)$) to determine $s=\frac{2}{3}$ and $t=1$ in the following equations.
+
+\begin{eqnarray*}
+	s * x_{1_{P_1}} + t*x_{2_{P_1}} = s * x_{1_{P_2}} + t*x_{2_{P_2}}\\
+\Leftrightarrow	s*2+t*4 = s*5+ t*2\\
+\Leftrightarrow	2t = 3s\\
+\Leftrightarrow	s = \frac{2}{3}t\\
+\rightarrow t=1\\	
+\end{eqnarray*}
+
+Now we controlled the resuld by inserting the extreme data points $P_1$ and $P_2$.
+
+\begin{eqnarray*}
+t=1\\
+\frac{2}{3}*t*x_1+t*x_2\\
+\Leftrightarrow\frac{2}{3}*x_1+x_2\\
+\\
+\frac{2}{3}*2+4 =\frac{2}{3}*5+2  = 5+\frac{1}{3}\\
+\end{eqnarray*}
+
+Not serious ;)
 The equation influence by t and s is:
@@
 P2=(2,4)\\
+
+\begin{figure}[h]
+	\includegraphics[width=\textwidth]{img/figure-P24.png}
+	\label{P24}
+\end{figure}
+
+To achive that P(2,4) is the only maximal value, we need to use the borders used in figure \ref{P24}.
+The lower one is described by the maximal constraint (4) (equation \ref{lowerbound})and the higher one is described by the horizontal line at $x2=4$.
+Next we can define relations, for the variables $m_2$ and $c_2$ of the searched linear equation.
+These are shown in equation \ref{rel1} and \ref{rel2}.
+
+\begin{eqnarray}
+-1x_1+2x_2=6\\
+\Leftrightarrow  x_2 = \frac{1}{2} x_1 +3 \label{lowerbound}\\
+=	x_2= m_1 x_1 + c_1\\
+	\\
+	m_1 > m_2 > 0 \label{rel1}\\
+	c_1<c_2<4 \label{rel2}\\
+\end{eqnarray}
+
+ So any linear equation, which lies in the green area of figure \ref{P24} , is a possible solution.
+We will now just choose one and define $c_2 = 3.5 = \frac{7}{2}$ according to relation \label{rel2}.
+From this now we can deduce $m_2=\frac{1}{4}$ as shown in Equation \ref{m} so that P(2,4) is the only intersection with the feasible region.
+
+\begin{eqnarray}
+4=m_2 * 2+3.5\\
+m_2 = \frac{4-3.5}{2}  = \frac{1}{4} \label{m}\\
+\end{eqnarray}
+
+The last step is now to get s and t, this is achieved by forming the found linear equation back to the desired form (Equation \ref{result24}).
+The complete result is for $s=\frac{-1}{14}$ and for $t= \frac{2}{7}$.
+
+\begin{eqnarray}
+x_2=\frac{1}{4} * x_1 + \frac{7}{2}\\
+ 	\Leftrightarrow 	- \frac{1}{4} x_1 + x_2=\frac{7}{2}\\
+ 	\Leftrightarrow 	- \frac{1}{14} x_1 + \frac{2}{7} x_2 = 1 \label{result24}\\
+\Rightarrow s= - \frac{1}{14} ; t=\frac{2}{7}\\
+\end{eqnarray}
+
 P3=(1,3)\\

### 2015-11-13 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
aufgabe 2 fast fertig und aufgabe 3 fertig

--- 2015-11-12 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
@@
 \usepackage{amsmath}
+\usepackage{mathtools}
 \usepackage{hyperref}
@@
 \subsection*{How to get infinite solutions with t and s?}
-The equation influence by t and s is:
+The linear program has infinite solutions, if we assign the following values to s and t:
 
-\begin{equation*}
-max: s*x_1+t*x_2
-\end{equation*}
+\begin{align}
+ s &= x_2 \nonumber \\
+ t &= -x_1 \nonumber \\
+\end{align}
 
-\noindent way to get an infinite solution could be to generate a endless loop with values for s and t like:
-\begin{eqnarray*}
-s=s*x_1\label{inf1}\\ 
-t=t*x_2 \label{inf2}\\ 
-or\\
-s=t*x_2\label{inf3}\\ 
-t=s*x_1 \label{inf4}\\ 
-\end{eqnarray*}
+\noindent These values would lead to the equation $x_2*x_1 + (-x_1)*x_2$, which is always zero. So 
+the maximal result is zero and you can fill in arbitrary numbers to get this result, i.e. infinite 
+solutions.
 
-\subsection*{how to get the points?}
+\subsection*{how to make the points a optimal solution?}
 
@@
 
+The Carrillo-Lipman bound is defined by $B_{pq} \coloneqq B(A) - (\sum_{i<j} s(\hat{A}_i, \hat{A}_j)-s(\hat{A}_p,\hat{A}_q))$, 
+where $B(A)$ is a score for the alignment computed by a heuristic and $s(\hat{A}_i,\hat{A}_j)$ is 
+the score of a optimal alignment of sequences $i$ and $j$. If we have just two sequences $p$ and $q$, 
+this equation would be simplified as 
+\[
+B_{pq} = B(A) - (s(\hat{A}_p,\hat{A}_q)-s(\hat{A}_p,\hat{A}_q)) = B(A).
+\]
+
+\noindent So the Carrillo-Lipman bound for two sequences is just the computed score by a heuristic.
 %\newpage

### 2015-11-13 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex

@@
 
+%Getting infinite solutions,  requires to describe with the max function of a linear algorithm a line in the feasible region and not just one point.
+%Therefore we decided to use constraint 3 and wanted to generate a max function along constraint (3).
+For the modelling of the max function we used two points from constraint (3) ($P_1(2,4); P_2(5,2)$) to determine $s=\frac{2}{3}$ and $t=1$ in the following equations.
+
+%\begin{eqnarray*}
+%	s * x_{1_{P_1}} + t*x_{2_{P_1}} = s * x_{1_{P_2}} + t*x_{2_{P_2}}\\
+%\Leftrightarrow	s*2+t*4 = s*5+ t*2\\
+%\Leftrightarrow	2t = 3s\\
+%\Leftrightarrow	s = \frac{2}{3}t\\
+%\rightarrow t=1\\	
+%\end{eqnarray*}
+
+%Now we controlled the resuld by inserting the extreme data points $P_1$ and $P_2$.
+
+%\begin{eqnarray*}
+%t=1\\
+%\frac{2}{3}*t*x_1+t*x_2\\
+%\Leftrightarrow\frac{2}{3}*x_1+x_2\\
+%\\
+%\frac{2}{3}*2+4 =\frac{2}{3}*5+2  = 5+\frac{1}{3}\\
+%\end{eqnarray*}
+
+%Not serious ;)
+%The equation influence by t and s is:
+
 \begin{align}

### 2015-11-18 AssignmentVI/Assignment5-Ditz_Schroeder-WS15-16.tex
assignment 6 aufgabe 1a fertig

--- 2015-11-13 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{5}{Alexander Seitz}{16. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{4}
+\header{6}{Alexander Seitz}{23. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
 
-\section*{Theoretical Assignment - \textsl{Comparison with at most $l$ mismatches}}
+\section*{Theoretical Assignment - \textsl{Sequence-profile alignment and expected patterns in sequences}}
 
-General we are now only looking at the worst case scenario, which means uniform distributed mistmatches in an alignment.
-Also we only look at $k>=1$, as $k=0$ is in our application not a useful result.
-Assume two sequences of length t with l mismatches.\\
- Than both sequences contain $l$ tuples of length $L = \lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ . \\
-\\
-\noindent So both sequences share $l$ or $l+1$ k-tuples, if $k = \lfloor\frac{t}{l+1}\rfloor$, and for each 
-$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{L}{k}\rfloor$
-k-tuples.
+\subsection*{}
+The profile as a PSWM for the given MSA would look like table \ref{tab:pswm}.
 
-\section*{Theoretical Assignment - \textsl{Linear programming by hand}}
+\begin{table}[h]
+\centering
+\caption{PSWM of the given MSA}
+\begin{tabular}{c|ccccc}
+   & $p_1$ & $p_2$ & $p_3$ & $p_4$ & $p_5$ \\
+ \hline  
+ \textbf{A} & $0.\overline{3}$ & 0 & $0.\overline{3}$ & 0 & 0 \\
+ \textbf{C} & 0 & 0 & 0 & 1 & 0 \\
+ \textbf{G} & 0 & 0 & 0 & 0 & 1 \\
+ \textbf{T} & 0 & 1 & $0.\overline{6}$ & 0 & 0 \\
+ \textbf{-} & $0.\overline{6}$ & 0 & 0 & 0 & 0 
+ \label{tab:pswm}
+\end{tabular}
+\label{tab:pswm}
+\end{table}
 
-The feasible region of this linear program is shown in figure \ref{feasibleRegion}, where the red line 
-is constraint 1, green line is constraint 2, constraint 3 is drawn as a blue line and the yellow line 
-is constraint 4.
+\noindent Using this PSWM we can now compute an optimal semiglobal alignment of our profile with the 
+sequence $A = CATTCCGTTC$. First we calculate the scoring matrix using as a scoring function 
+$s(a,b) = -1$, $s(a,a) = 3$ and $d = 2$:
 
-\begin{figure}[ht]
+\bigskip
+
+\begin{table}[h]
 \centering
- \includegraphics[width=0.7\textwidth]{img/figure_1.png}
- \caption{feasible region of linear program (grey area)}
- \label{feasibleRegion}
-\end{figure}
+\begin{tabular}{c|cccccccccc}
+   & $b_1$ & $b_2$ & $b_3$ & $b_4$ & $b_5$ & $b_6$ & $b_7$ & $b_8$ & $b_9$ & $b_{10}$ \\
+   & C & A & T & T & C & C & G & T & T & C \\
+ \hline
+ $p_1$ & $-1.\overline{6}$ & $-0.\overline{3}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ \\
+ $p_2$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ \\
+ $p_3$ & $-1$ & $0.\overline{3}$ & $1.\overline{6}$ & $1.\overline{6}$ & $-1$ & $-1$ & $-1$ & $1.\overline{6}$ & $1.\overline{6}$ & $-1$ \\
+ $p_4$ & $3$ & $-1$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-1$ & $-1$ & $3$ \\
+ $p_5$ & $-1$ & $-1$ & $-1$ & $-1$ & $-1$ & $-1$ & $3$ & $-1$ & $-1$ & $-1$ 
+\end{tabular}
+\end{table}
+\newpage
+\noindent Now we fill the DP matrix using that scoring matrix:
+\bigskip
+\begin{table}[h!]
+ \centering
+ \begin{tabular}{c|ccccccccccc}
+    & 0 & C & A & T & T & C & C & G & T & T & C \\
+  \hline
+  0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
+  $p_1$ & -2 & $-1.\overline{6}$ & \textcolor{red}{$-0.\overline{3}$} & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ \\
+  $p_2$ & -4 & $-3$ & $-2.\overline{6}$ & \textcolor{red}{$2.\overline{6}$} & $1.\overline{3}$ & $-0.\overline{6}$ & $-2.\overline{6}$ & $-2.\overline{6}$ & $1.\overline{3}$ & $1.\overline{3}$ & $-0.\overline{6}$ \\
+  $p_3$ & -6 & $-5$ & $-2.\overline{6}$ & $0.\overline{6}$ & \textcolor{red}{$4.\overline{3}$} & $2.\overline{3}$ & $0.\overline{3}$ & $-1.\overline{6}$ & $-0.\overline{6}$ & $3$ & $1$ \\
+  $p_4$ & -8 & $-3$ & $-4.\overline{6}$ & $-1.\overline{3}$ & $2.\overline{3}$ & \textcolor{red}{$7.\overline{3}$} & \textcolor{red}{$5.\overline{3}$} & $3.\overline{3}$ & $1.\overline{3}$ & $1$ & $6$ \\
+  $p_5$ & -10 & $-9$ & $-4$ & $-3.\overline{3}$ & $0.\overline{3}$ & $5.\overline{3}$ & $6.\overline{3}$ & \textcolor{red}{$8.\overline{3}$} & $6.\overline{3}$ & $4.\overline{3}$ &  $4$ \\
+ \end{tabular} 
+\end{table}
 
-\subsection*{solution if t=s=1}
-Generally we only used integers in this task. The constraint for the algorithm are as following if t and s value is 1 now:
+\noindent One can see that the optimal alignment (colored in red) is:
 
-\begin{eqnarray}
-max. 1*x_1+1*x_2 \label{con1}\\ 
-s.t. 2*x_1+x_2 \le 12 \label{con2}\\ 
-2*x_1+3*x_2 \le 7 \label{con3}\\ 
--1*x_1+2*x_2 \le 16 \label{con4}\\ 
-x_1,x_2 \ge 0 \label{con5}
-\end{eqnarray}
+\begin{table}[h]
+\centering
+\begin{tabular}{cccccccccc}
+ C&A&T&T&C&C&G&T&T&C\\
+  &$p_1$&$p_2$&$p_3$&$p_4$&-&$p_5$& & & 
+\end{tabular}
+\end{table}
 
-\noindent the next step we started to compute each line of the tuple.
-Starting with constraint \ref{con3} under the aspect of constraint \ref{con5}.
-All possible tuples respectively to both constraints from the assignment are:\\
-$temp1=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);(6,1);(7,0)\}$\\
+\section*{Theoretical Assignment - \textsl{Practice writing an introduction / background for a paper}}
 
-\noindent the constraint \ref{con2} was applied to temp1:\\
-$temp2=\{(0,7);(1,6);(2,5);(3,4);(4,3);(5,2);\}$\\
-
-\noindent the next constraint (constraint \ref{con4}) was applied:\\
-$temp3=\{(5,2)\}$\\
-
-\noindent but not least the last constraint (4) is checked and the remaining tuple from the last step is valid:\\
-$r=\{(5,2)\}$\\
-
-\noindent the final result for the Algorithm with s=t=1 is the tuple: (5,2). Solving the formula with this numbers 
-leads us to the following maximal value: $1*x_1 + 1*x_2 = 5+2 = 7$\\
-
-\subsection*{How to make unsolvable?}
-To get a not solvable algorithm for example the following constraint could be added:
-	\begin{equation}\\
-		x_1+x_2\ge 7
-	\end{equation}
-
-\noindent a new constraint just needs to be a contradiction to another constraint.
-
-\subsection*{How to get infinite solutions with t and s?}
-The linear program has infinite solutions, if we assign the following values to s and t:
-
-\begin{align}
- s &= x_2 \nonumber \\
- t &= -x_1 \nonumber \\
-\end{align}
-
-\noindent These values would lead to the equation $x_2*x_1 + (-x_1)*x_2$, which is always zero. So 
-the maximal result is zero and you can fill in arbitrary numbers to get this result, i.e. infinite 
-solutions.
-
-\subsection*{how to make the points a optimal solution?}
-
-For the first point $P_1=(0,3)$ we have to set $s = -1$ and $t = 1$. That result in a maximal value 
-for (0,3) because we cannot set $x_2$ arbitrary big due to constraint 4. And if we assign a bigger 
-value to $x_1$, would decrease the result. Also we would violate constraint 2, if $x_1$ is to big.\\
-\\
-P2=(2,4)\\
-P3=(1,3)\\
-\\
-\noindent To make $P_4=(6,0)$ the maximum we set $s = 1$ and $t = -1$. We cannot set $x_1$ to a bigger value 
-than 6 without violating constraint 1.
-
-\section*{Theoretical Assignment - \textsl{Bonus: Carillo-Lipman bound}}
-
-The Carrillo-Lipman bound is defined by $B_{pq} \coloneqq B(A) - (\sum_{i<j} s(\hat{A}_i, \hat{A}_j)-s(\hat{A}_p,\hat{A}_q))$, 
-where $B(A)$ is a score for the alignment computed by a heuristic and $s(\hat{A}_i,\hat{A}_j)$ is 
-the score of a optimal alignment of sequences $i$ and $j$. If we have just two sequences $p$ and $q$, 
-this equation would be simplified as 
-\[
-B_{pq} = B(A) - (s(\hat{A}_p,\hat{A}_q)-s(\hat{A}_p,\hat{A}_q)) = B(A).
-\]
-
-\noindent So the Carrillo-Lipman bound for two sequences is just the computed score by a heuristic.
 %\newpage

### 2015-11-19 AssignmentVI/Assignment5-Ditz_Schroeder-WS15-16.tex
aufgabe 1 ist fertig; vielleicht nochmal drüberschauen ob du da mit mir übereinstimmst

@@
   \begin{vartab}{\thecolmns}
-    \numbers{#1} & $\sum$ (7)\\\hline   %add here Complete number of points ---------------------------
+    \numbers{#1} & $\sum$ (6)\\\hline   %add here Complete number of points ---------------------------
     \emptyLine{\thecolmns}\\
@@
 
-\subsection*{}
+\subsection*{(a)}
 The profile as a PSWM for the given MSA would look like table \ref{tab:pswm}.
@@
 
+\subsection*{(b)}
+\subsubsection*{i. Compute the probability that S[1...4] contains P = GT without substitutions.}
+There are three different outcomes for this result.
+
+\begin{align}
+ p_1 &: S[1] = G\textrm{ and }S[2] =T \nonumber \\
+ p_2 &: S[2] = G\textrm{ and }S[3] =T \nonumber \\
+ p_3 &: S[3] = G\textrm{ and }S[4] =T \nonumber 
+\end{align}
+
+\noindent Since all $S[i]$s are independent of each other, we simple multiply all probabilities for 
+each $S[i]$.
+
+\begin{align}
+ P(p_1) &= \frac{1}{4} * \frac{1}{4} * 1 * 1 = \frac{1}{16} \nonumber \\
+ P(p_2) &= 1 * \frac{1}{4} * \frac{1}{4} * 1 = \frac{1}{16} \nonumber \\
+ P(p_3) &= 1 * 1 * \frac{1}{4} * \frac{1}{4} = \frac{1}{16} \nonumber 
+\end{align}
+
+\noindent Where $\frac{1}{4}$ is the probability to choose G or C, respectively, and $1$ is the 
+probability to choose any character from the alphabet. All three outcomes would fulfill the task, 
+so we simply sum up all probabilities:
+
+\begin{equation}
+ P(\textrm{S[1...4] contains GT}) = P(p_1) + P(p_2) + P(p_3) = \frac{3}{16} \nonumber
+\end{equation}
+
+\subsubsection*{ii. Compute the probability that S[1...6] contains P = AAA with at most one substitution.}
+There are three different possible outcomes for P to appear at position 1:
+
+\begin{align}
+ S[1...3] &= YAA \nonumber \\
+ S[1...3] &= AYA \nonumber \\
+ S[1...3] &= AAY \nonumber 
+\end{align}
+
+\noindent Each of this possibilities has the probability $\frac{1}{16}$. Since we have four different 
+start positions (1,2,3 and 4) and for each position three different outcomes, the final probability 
+is:
+
+\begin{equation}
+ P(\textrm{S[1...6] contains AAA}) = 4 * 3 * \frac{1}{16} = \frac{3}{4} \nonumber
+\end{equation}
+
 \section*{Theoretical Assignment - \textsl{Practice writing an introduction / background for a paper}}

### 2015-11-23 AssignmentVI/Assignment5-Ditz_Schroeder-WS15-16.tex
againaga

@@
  S[1...3] &= AYA \nonumber \\
- S[1...3] &= AAY \nonumber 
+ S[1...3] &= AAY \nonumber an
 \end{align}
@@
 
-%\newpage
-%\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
-%\bibliographystyle{ieeetr}
+Pattern recognition is a important topic for all life sciences areas and also a though challenge for the computational area.
+The main goal of finding repeating patterns in bio-sequences is the lead to propose functions which could be contained in new unknown sequences.
+Specially motifs which are involved in regulation can give a deep insight to regulatory networks and the involvement of proteins.
+The field of transcription factors is also highly interested in interaction motifs, which can lead to a regulation of gene expression.\\
+For example the standard example the nucleus located protein p53, which is in very often mutated in cancer cells.
+A very conserved region of p53 binding side which binds to following motif on the DNA (\cite{p53}):
+\begin{equation*}
+5'-R-R-R-C-(A/T)-(T/A)-G-Y-Y-Y-3'
+\end{equation*}
+
+Directly by p53 influenced proteins are for example p21, which inhibits the cell cyklus and Bcl2, an trigger protein for apoptosis.\cite{p53-Function}\\
+\\sperimental approach for showing the binding of a protein is the chromatin immunoprecipitation (ChIP).
+With the fixation of the nucleic-acid-protein-complex via formaldehyde.
+Afterwards the cells are lysated via sonification.
+The resulting DNA and DNA-Protein-complex fragments are seperated via an immunoprecipitiation with a protein specific antibody.
+After several washing steps, the fixation via the formaldehyde is destroyed via heating up the sample.
+After another seperation step, the result is the DNA from the DNA-protein-complex.
+The gained can be sequenced or otherwise analysed.
+A critical parameter for this methode is the specifity of the antibody.
+Because if the specifity is to low, no pure sample can be purified \cite{chip}.
+\\
+But of course there are also computational methods, which allow the discovery of new motifs like with the Gibbs sampling mehtod implemented in or the Projection Method.
+These methods all challenge the problem, what is background and therefore not important for a interaction?
+But also there are Database like Jaspar or TRANSFAC which already contain motifs, which can be compared to a querry.
+\\
+With this new algorithm we designed, we want to push the limits of space, time complexity and accuracy.
+The "best-motives"-Algorithm solves could therefore make motif finding much more easier and faster.
+\\
+\newpage
+\bibliography{Assignment6-Ditz_Schroeder-WS15-16.bib}
+\bibliographystyle{ieeetr}
 

### 2015-11-26 AssignmentVII/Assignment7-Ditz_Schroeder-WS15-16.tex
Latex File

--- 2015-11-18 AssignmentVI/Assignment5-Ditz_Schroeder-WS15-16.tex
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{6}{Alexander Seitz}{23. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
+\header{7}{Alexander Seitz}{30. November 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
 
-\section*{Theoretical Assignment - \textsl{Sequence-profile alignment and expected patterns in sequences}}
+\section*{Practical Assignment - \textsl{Planted Motif Problem Generator}}
 
-\subsection*{}
-The profile as a PSWM for the given MSA would look like table \ref{tab:pswm}.
-
-\begin{table}[h]
-\centering
-\caption{PSWM of the given MSA}
-\begin{tabular}{c|ccccc}
-   & $p_1$ & $p_2$ & $p_3$ & $p_4$ & $p_5$ \\
- \hline  
- \textbf{A} & $0.\overline{3}$ & 0 & $0.\overline{3}$ & 0 & 0 \\
- \textbf{C} & 0 & 0 & 0 & 1 & 0 \\
- \textbf{G} & 0 & 0 & 0 & 0 & 1 \\
- \textbf{T} & 0 & 1 & $0.\overline{6}$ & 0 & 0 \\
- \textbf{-} & $0.\overline{6}$ & 0 & 0 & 0 & 0 
- \label{tab:pswm}
-\end{tabular}
-\label{tab:pswm}
-\end{table}
-
-\noindent Using this PSWM we can now compute an optimal semiglobal alignment of our profile with the 
-sequence $A = CATTCCGTTC$. First we calculate the scoring matrix using as a scoring function 
-$s(a,b) = -1$, $s(a,a) = 3$ and $d = 2$:
-
-\bigskip
-
-\begin{table}[h]
-\centering
-\begin{tabular}{c|cccccccccc}
-   & $b_1$ & $b_2$ & $b_3$ & $b_4$ & $b_5$ & $b_6$ & $b_7$ & $b_8$ & $b_9$ & $b_{10}$ \\
-   & C & A & T & T & C & C & G & T & T & C \\
- \hline
- $p_1$ & $-1.\overline{6}$ & $-0.\overline{3}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ \\
- $p_2$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ \\
- $p_3$ & $-1$ & $0.\overline{3}$ & $1.\overline{6}$ & $1.\overline{6}$ & $-1$ & $-1$ & $-1$ & $1.\overline{6}$ & $1.\overline{6}$ & $-1$ \\
- $p_4$ & $3$ & $-1$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-1$ & $-1$ & $3$ \\
- $p_5$ & $-1$ & $-1$ & $-1$ & $-1$ & $-1$ & $-1$ & $3$ & $-1$ & $-1$ & $-1$ 
-\end{tabular}
-\end{table}
+\section{Practical Assignment - \textsl{MEME and Gibbs sampler}}
 \newpage
-\noindent Now we fill the DP matrix using that scoring matrix:
-\bigskip
-\begin{table}[h!]
- \centering
- \begin{tabular}{c|ccccccccccc}
-    & 0 & C & A & T & T & C & C & G & T & T & C \\
-  \hline
-  0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
-  $p_1$ & -2 & $-1.\overline{6}$ & \textcolor{red}{$-0.\overline{3}$} & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ & $-1.\overline{6}$ \\
-  $p_2$ & -4 & $-3$ & $-2.\overline{6}$ & \textcolor{red}{$2.\overline{6}$} & $1.\overline{3}$ & $-0.\overline{6}$ & $-2.\overline{6}$ & $-2.\overline{6}$ & $1.\overline{3}$ & $1.\overline{3}$ & $-0.\overline{6}$ \\
-  $p_3$ & -6 & $-5$ & $-2.\overline{6}$ & $0.\overline{6}$ & \textcolor{red}{$4.\overline{3}$} & $2.\overline{3}$ & $0.\overline{3}$ & $-1.\overline{6}$ & $-0.\overline{6}$ & $3$ & $1$ \\
-  $p_4$ & -8 & $-3$ & $-4.\overline{6}$ & $-1.\overline{3}$ & $2.\overline{3}$ & \textcolor{red}{$7.\overline{3}$} & \textcolor{red}{$5.\overline{3}$} & $3.\overline{3}$ & $1.\overline{3}$ & $1$ & $6$ \\
-  $p_5$ & -10 & $-9$ & $-4$ & $-3.\overline{3}$ & $0.\overline{3}$ & $5.\overline{3}$ & $6.\overline{3}$ & \textcolor{red}{$8.\overline{3}$} & $6.\overline{3}$ & $4.\overline{3}$ &  $4$ \\
- \end{tabular} 
-\end{table}
-
-\noindent One can see that the optimal alignment (colored in red) is:
-
-\begin{table}[h]
-\centering
-\begin{tabular}{cccccccccc}
- C&A&T&T&C&C&G&T&T&C\\
-  &$p_1$&$p_2$&$p_3$&$p_4$&-&$p_5$& & & 
-\end{tabular}
-\end{table}
-
-\section*{Theoretical Assignment - \textsl{Practice writing an introduction / background for a paper}}
-
-%\newpage
-%\bibliography{Assignment4-Ditz_Schroeder-WS15-16.bib}
-%\bibliographystyle{ieeetr}
+\bibliography{Assignment6-Ditz_Schroeder-WS15-16.bib}
+\bibliographystyle{ieeetr}
 

### 2015-11-30 poodle_project/webInterface/src/SearchForm/GeneralSearchParameter.java
a Crude start

@@ -35,6 +35,7 @@ public class GeneralSearchParameter extends VerticalLayout{
 	    public GeneralSearchParameter() {
 	    	setDefaultComponentAlignment(Alignment.TOP_CENTER);
 	    	
+	    	grid.setSpacing(true);
 	        addComponent(displays);
 	        
 	    	grid.addComponent(parameter1, 0, 0);
@@ -46,5 +47,12 @@ public class GeneralSearchParameter extends VerticalLayout{
 	        grid.addComponent(parameter7, 1, 2);
 	        addComponent(grid);
 
+	    }
+	    public void fill(String[][] entry){
+	    	
+	    }
+	    
+	    public void getParameters(){
+	    	
 	    }
 	}

### 2015-11-30 poodle_project/webInterface/src/SearchForm/SearchBar.java

@@ -11,56 +11,56 @@ import guis.SearchResultView;
 public class SearchBar extends HorizontalLayout {
 
 	GridLayout columns = new GridLayout(4,4);
-	
-//	SearchButton
+
+	//	SearchButton
 	Button searchButton;
-	
+
 	//Search Parameter:
 	//General
-	   TextField parameter1   = new TextField("ID");
-	   TextField parameter2   = new TextField("box");
-	   TextField parameter3   = new TextField("position");
-	   TextField parameter4   = new TextField("name");
-	   TextField parameter5   = new TextField("protein");
-	   TextField parameter6   = new TextField("domain");
-	   TextField parameter7   = new TextField("author");
-	   
+	TextField parameter1   = new TextField("ID");
+	TextField parameter2   = new TextField("box");
+	TextField parameter3   = new TextField("position");
+	TextField parameter4   = new TextField("name");
+	TextField parameter5   = new TextField("protein");
+	TextField parameter6   = new TextField("domain");
+	TextField parameter7   = new TextField("author");
+
 	//Vectors
-	   TextField parameter8   = new TextField("Tags");
-	   TextField parameter9   = new TextField("Ant-Biotics");
-	   
-	   
-	   public SearchBar(){
-		   this.setSpacing(true);
-		   columns.setSpacing(true);
-			// Search Button 
-			searchButton = new Button("Search");
-			searchButton.addStyleName("searchButton");
-			searchButton.addClickListener(new Button.ClickListener() {
-				public void buttonClick(ClickEvent event) {
-					Label na = new Label("Did it again!");
-					columns.addComponent(na);
-					}
-				});
-			
-   
-		   columns.addComponent(parameter1, 0, 0);
-		   columns.addComponent(parameter2, 0, 1);
-		   columns.addComponent(parameter3, 0, 2);
-		   
-		   columns.addComponent(parameter4, 1, 0);
-		   columns.addComponent(parameter5, 1, 1);
-		   columns.addComponent(parameter6, 1, 2);
-		   	
-		   columns.addComponent(parameter7, 2, 0);
-		   columns.addComponent(parameter8, 2, 1);
-		   columns.addComponent(parameter9, 2, 2);
-		   
-		   columns.addComponent(searchButton, 3,3);
-	   }
-	   
-	   public Layout getLayout(){
-		   return columns;
-	   }
-	
[…]

### 2015-11-30 poodle_project/webInterface/src/com/poodledb/PoodledbUI.java

@@ -34,6 +34,7 @@ public class PoodledbUI extends UI {
 	private final VerticalLayout layout = new VerticalLayout();
 	private MenuBar navigationMenu;
 	private static VerticalLayout content;
+	private static ServerTableSelection serverTableSelection;
 	
 	@WebServlet(value = "/*", asyncSupported = true)
 	@VaadinServletConfiguration(productionMode = false, ui = PoodledbUI.class)
@@ -56,7 +57,7 @@ public class PoodledbUI extends UI {
 		FileResource resource1 = new FileResource(new File(basepath+"/WEB-INF/img/logo_poodle.png"));
 		logo= new Image("",resource1);
 		logo.setWidth("256px");
-		layout.addComponent(logo);
+
 		
 		//setup search view
 		//initially start with search view
@@ -69,27 +70,38 @@ public class PoodledbUI extends UI {
 		navigationMenu = new NavigationBar(this);
 		navigationMenu.addStyleName("navigationMenu");
 
-
+		//Selection
+		serverTableSelection = new ServerTableSelection(this);
 		
 		//whole Layout
-
+		layout.addComponent(logo);
 		layout.addComponent(navigationMenu);
+		layout.addComponent(serverTableSelection);
 		layout.addComponent(content);
 	}
 	
 	public void modifyLayouttoResultView(){
 		layout.removeComponent(logo);
+		layout.removeComponent(serverTableSelection);
 		layout.setComponentAlignment(navigationMenu, Alignment.TOP_LEFT);
 	}
 	public void modifyLayouttoSearchView(){
 		layout.removeAllComponents();
 		layout.addComponent(logo);
 		layout.addComponent(navigationMenu);
+		layout.addComponent(serverTableSelection);
 		layout.addComponent(content);
+	}
+	
+	public Layout getContentBox(){
+		return content;
 	}
 	
 	public void SetContentBox(Component view){
 		content.removeAllComponents();
 		content.addComponent(view);
+	}
+	public ServerTableSelection getServerTable(){
+		return serverTableSelection;
 	}
 }

### 2015-11-30 poodle_project/webInterface/src/com/poodledb/ServerTableSelection.java

@@ -1,0 +1,74 @@
+package com.poodledb;
+
+import com.vaadin.ui.HorizontalLayout;
+import com.vaadin.ui.Layout;
+import com.vaadin.ui.NativeSelect;
+
+import SearchForm.GeneralSearchParameter;
+import SearchForm.PrimerParameter;
+import SearchForm.ProteinConstructParameter;
+import SearchForm.VectorParameter;
+import guis.SearchView;
+
+public class ServerTableSelection extends HorizontalLayout{
+	PoodledbUI poodledb;
+	NativeSelect tableSelect;
+	NativeSelect dbSelect;
+	
+	public ServerTableSelection(PoodledbUI poodledb){
+		this.poodledb = poodledb;
+
+		//Selection Buttons (for table
+		//Which server or Table??
+		this.setSpacing(true);
+		//Select which Database:
+		dbSelect = new NativeSelect("Select the Database");
+		dbSelect.addItems("all","Sprangers", "Wiesner");
+		dbSelect.setValue("Wiesner");
+		dbSelect.setNullSelectionAllowed(false);
+		//Select which table you want to search through
+		tableSelect = new NativeSelect("Pre-Select");
+		tableSelect.addItems("all", "Primer", "cloningVectors", "proteinConstructs");
+		tableSelect.setValue("all");
+		tableSelect.setNullSelectionAllowed(false);
+		// Handling of Selections:
+		//	dbSelect.addValueChangeListener(event -> dbSQL = (String) event.getProperty().getValue())));
+		tableSelect.addValueChangeListener(event -> this.tableValues((String) event.getProperty().getValue()));
+		
+		this.addComponent(tableSelect);
+		this.addComponent(dbSelect);
+	}
+	
+	public String getTable(){
+		return (String)tableSelect.getValue();
+	}
+
+	private void tableValues(String val){
+		Layout view = (Layout) poodledb.getContentBox();
+
+		if(view instanceof SearchView){
+			HorizontalLayout parameters= ((SearchView) view).getParameters();
+			switch(val){
+			case "All":
+				parameters.removeAllComponents();
+				parameters.addComponent(new GeneralSearchParameter());
+				break;
+			case "Primer":
+				parameters.removeAllComponents();
+				parameters.addComponent(new GeneralSearchParameter());
+				parameters.addComponent(new PrimerParameter());
+				break;
+			case "Vector":
+				parameters.removeAllComponents();
+				parameters.addComponent(new GeneralSearchParameter());
[…]

### 2015-11-30 poodle_project/webInterface/src/guis/BlastView.java

@@ -20,6 +20,7 @@ public class BlastView extends VerticalLayout {
 		//Layout
 		this.setDefaultComponentAlignment(Alignment.TOP_CENTER);
 		this.setSpacing(true);
+		this.setMargin(true);
 		//Selection Buttons (for table
 		//Which server or Table??
 		serverTableBar.setSpacing(true);

### 2015-11-30 poodle_project/webInterface/src/guis/SearchResultView.java

@@ -9,17 +9,39 @@ import sqlClasses.SQLCommunicator;
 
 @Push
 public class SearchResultView extends VerticalLayout{
-	GridLayout grid = new GridLayout(1,3);
+	GridLayout grid = new GridLayout(1,4);
 	SearchBar searchBar = new SearchBar();
 	Table primerTable = new Table("Primer");
-	
-	
+	Table vectorTable = new Table("Vector");
+	Table proteinTable = new Table("Protein");
+
 	public SearchResultView(SQLCommunicator sqlC){		
-		
-		primerTable.setContainerDataSource(sqlC.getContainer());
-		
+
+		switch(sqlC.getTable()){
+		case "Primer":
+			primerTable.setContainerDataSource(sqlC.getContainer());
+			grid.addComponent(primerTable, 0, 1);
+			break;
+		case "cloningVectors":
+			vectorTable.setContainerDataSource(sqlC.getContainer());
+			grid.addComponent(vectorTable, 0, 1);
+			break;
+		case "proteinConstructs":
+			proteinTable.setContainerDataSource(sqlC.getContainer());
+			grid.addComponent(proteinTable, 0, 1);
+			break;
+		case "all":
+			primerTable.setContainerDataSource(sqlC.getPrimerQuerry());
+			vectorTable.setContainerDataSource(sqlC.getVectorQuerry());
+			proteinTable.setContainerDataSource(sqlC.getProteinQuerry());
+
+			grid.addComponent(primerTable, 0, 1);
+			grid.addComponent(vectorTable, 0, 2);
+			grid.addComponent(proteinTable, 0, 3);
+			break;
+		}
+
 		grid.addComponent(searchBar.getLayout(), 0, 0);
-		grid.addComponent(primerTable, 0, 1);
 		addComponent(grid);
 	}
 }

### 2015-11-30 poodle_project/webInterface/src/guis/SearchView.java

@@ -29,15 +29,15 @@ import sqlClasses.SQLCommunicator;
 
 @Push
 public class SearchView extends VerticalLayout {
-	VerticalLayout root;
 	Button searchButton;
+	HorizontalLayout serverTableBar = new HorizontalLayout();
+	HorizontalLayout parameters = new HorizontalLayout();
+	
 	VerticalLayout generalSearchParameter = new GeneralSearchParameter();
 	VerticalLayout vectorParameter = new VectorParameter();
 	VerticalLayout primerParameter = new PrimerParameter();
 	VerticalLayout proteinConstructParameter = new ProteinConstructParameter();
 	
-	HorizontalLayout serverTableBar = new HorizontalLayout();
-	HorizontalLayout parameters = new HorizontalLayout();
 
 	//SQL - THINGS
 	String dbSQL="Wiesner"; 
@@ -49,10 +49,9 @@ public class SearchView extends VerticalLayout {
 		 sqlC = new SQLCommunicator(dbSQL);
 		
 		
-		//root Layout 
-		root = new VerticalLayout();
-		root.setDefaultComponentAlignment(Alignment.TOP_CENTER);
-		root.setSpacing(true);
+		//Layout 
+		this.setDefaultComponentAlignment(Alignment.TOP_CENTER);
+		this.setSpacing(true);
 		
 		//initialize
 		generalSearchParameter = new GeneralSearchParameter();
@@ -63,28 +62,7 @@ public class SearchView extends VerticalLayout {
 		generalSearchParameter.addStyleName("Parameters");
 		
 		//Components
-
-		
-
-		
-		//Selection Buttons (for table
-		//Which server or Table??
-		serverTableBar.setSpacing(true);
-		//Select which Database:
-		NativeSelect dbSelect = new NativeSelect("Select the Database");
-		dbSelect.addItems("All","Sprangers", "Wiesner");
-		dbSelect.setValue("Wiesner");
-		dbSelect.setNullSelectionAllowed(false);
-		//Select which table you want to search through
-		NativeSelect tableSelect = new NativeSelect("Pre-Select");
-		tableSelect.addItems("All", "Primer", "Vector", "Protein-Construct");
-		tableSelect.setValue("All");
-		tableSelect.setNullSelectionAllowed(false);
-		// Handling of Selections:
-//		dbSelect.addValueChangeListener(event -> dbSQL = (String) event.getProperty().getValue())));
[…]

### 2015-11-30 poodle_project/webInterface/src/sqlClasses/SQLCommunicator.java

@@ -12,10 +12,16 @@ public class SQLCommunicator {
 
 	JDBCConnectionPool pool;
 	String db;
+	String table;
 	TableQuery tq;
 	String [][] searchCriteria;
 	SQLContainer container;
+	SQLContainer primerContainer;
+	SQLContainer vectorContainer;
+	SQLContainer proteinContainer;
 	
+
+
 	public SQLCommunicator(String db){
 		this.db = db;	
 		try {
@@ -25,18 +31,66 @@ public class SQLCommunicator {
 			e.printStackTrace();
 		}
 
-	
+
 	}
 
 	public void setTableQuerry(String a){
-		tq= new TableQuery(a, pool);
-		tq.setVersionColumn("OPTLOCK");
-		try {
-			container = new SQLContainer(tq);
-		} catch (SQLException e) {
-			// TODO Auto-generated catch block
-			e.printStackTrace();
+		table = a;
+		switch(a){
+		case "all":
+			TableQuery tq1= new TableQuery("Primer", pool);
+			tq1.setVersionColumn("OPTLOCK");
+			try {
+				primerContainer = new SQLContainer(tq1);
+			} catch (SQLException e) {
+				// TODO Auto-generated catch block
+				e.printStackTrace();
+			}
+			
+			TableQuery tq2= new TableQuery("cloningVectors", pool);
+			tq2.setVersionColumn("OPTLOCK");
+			try {
+				vectorContainer = new SQLContainer(tq2);
+			} catch (SQLException e) {
+				// TODO Auto-generated catch block
+				e.printStackTrace();
+			}
+			
+			TableQuery tq3= new TableQuery("proteinConstructs", pool);
+			tq3.setVersionColumn("OPTLOCK");
+			try {
+				proteinContainer = new SQLContainer(tq3);
+			} catch (SQLException e) {
+				// TODO Auto-generated catch block
+				e.printStackTrace();
+			}
+			break;
+
+		default:
+			tq= new TableQuery(a, pool);
+			tq.setVersionColumn("OPTLOCK");
+			try {
+				container = new SQLContainer(tq);
+			} catch (SQLException e) {
+				// TODO Auto-generated catch block
+				e.printStackTrace();
+			}
+			break;
+
 		}
+	}
+
+	public String getTable(){
+		return table;
+	}
+	public SQLContainer getProteinQuerry(){
+		return proteinContainer;
+	}
+	public SQLContainer getPrimerQuerry(){
[…]

### 2015-11-30 AssignmentVII/Assignment7-Ditz_Schroeder-WS15-16.tex
Assignment is ready

@@
 \usepackage{grffile} %allows to use pngs
+%\usepackage{epstopdf} % allows to use eps
 \usepackage{eurosym}
@@
 \section*{Practical Assignment - \textsl{Planted Motif Problem Generator}}
+A executable .jar-File of the written program for this task is attached to the our hand-in.
+The .jar can be executed via a commandline with the command "java -jar SeqGen.jar".
+The help for usage can be called with the option "-h", "-help", "--help" or "-?".
+Generally we tried to be as user-friendly as possible, via using options as input markers and generating detailed and clear error messages, if a input is invalid or missing.
+General needed input values are the options "-k <int>" ammount of sequences in the final set, "-n <int>" the sequence length, "-d <int>" the amount of deviation positions and "-l <int>" the length of the motif  or "-M <String>" a motif itself.
+If "-l <int>" is entered, a random motif is generated.
+With "-M <String>" the String is used as motif and "-l" is of course not needed, and vice versa.
+The "-o <String>" option is optional and stand for the output name.
+If no option is added the test run is started with the default values from the assignment sheet.\\
+ The motifs are generated with d deviation positions, which are not independent from each other.
+So if d is 2, there are two variable positions in the motif.
+These can not fall onto the same position.
+But each position can deviate as one of all four basic nucleotides, so also as the one which was already contained.\\
+ Another feature of our program is, that it also generates sequences with based on an amino acid alphabet.
+Switching to the amino acids the option "-E p" is needed.
+For the basicDNA bases no option is needed, although there is the "-E n" option.
+Also a matter of user-friendliness is the fact of never overwriting the output, but instead counting up an number.
+This causes the comfort of never overwriting accidently a file.
 
-\section{Practical Assignment - \textsl{MEME and Gibbs sampler}}
+\section*{Practical Assignment - \textsl{MEME and Gibbs sampler}}
+
+\subsection*{Method}
+We used two different software solution of Motif finder to perform a Motif search on our test sets. 
+The first tool was MEME-suite \cite{meme} a set of Motif-based sequence analysis tools. For this task 
+we used the online implementation of MEME\footnote{http://meme-suite.org/tools/meme} with the site 
+distribution parameter set to ``One occurrence per sequence'' and the number of Motifs set to one. 
+On the other hand we used the Gibbs Motif Sampler \cite{gibbs}. All parameters were set to their 
+default values except we set the -n flag to use nucleic acid alphabet.
+
+All test sets of sequences used for this task were generated by SeqGen. This is a self-programmed 
+Java tool, which uses four parameters to build a set of sequences. A overview of important parameters 
+of SeqGen can be found in table \ref{tab:params}. We generated five different test sets (see table 
+\ref{tab:sets}), which we used for comparison of MEME and Gibbs sampler.
+
+\begin{table}[ht]
+ \centering
+ \caption{Parameters of SeqGen}
+ \begin{tabular}{|l|l|}
+  \hline
+  Parameter & Description \\
+  \hline
+  k & number of sequences \\
+  n & length of each sequence \\
+  l & length of Motif \\
+  d & number of deviating positions \\
+  M & specify a Motif (optional) \\
+  \hline
+ \end{tabular}
+ \label{tab:params}
+\end{table}
+
+\begin{table}[ht]
+ \centering
+ \caption{parameter, which was used to generated test sets}
+ \begin{tabular}{|c|c|c|c|c|c|}
+  \hline
+    & k & n & l & d & M \\
+  \hline
+  test set 1 & 20 & 100 & 10 & 2 & AGTGGAACAG \\
+  test set 2 & 15 & 150 & 15 & 3 & CTTTGAGCAAATAAT \\
+  test set 3 & 20 & 100 & 5 & 1 & ATATC \\
+  test set 4 & 25 & 50 & 5 & 2 & CTGCA \\
+  test set 5 & 25 & 100 & 10 & 1 & ACAGGGGTGC \\
+  \hline
+ \end{tabular}
+ \label{tab:sets}
+\end{table}
+
+\subsection*{Result}
+
+MEME was able to find a Motif for all of the five test sets (see Figure \ref{fig:memeLogo}). However, 
+one can see easily that it overestimated the length for short Motifs.
+
+\begin{figure}[ht]
+ \centering
+ \subfigure[test set 1]{
+  \includegraphics[width=0.45\textwidth]{results_MEME/logo_testSetVorgabe}
+ }
+ \subfigure[test set 2]{
+  \includegraphics[width=0.45\textwidth]{results_MEME/logo_testSet1}
+ }
+ \subfigure[test set 3]{
+  \includegraphics[width=0.45\textwidth]{results_MEME/logo_testSet2}
+ }
+ \subfigure[test set 4]{
+  \includegraphics[width=0.45\textwidth]{results_MEME/logo_testSet3}
+ }
+ \subfigure[test set 5]{
+  \includegraphics[width=0.45\textwidth]{results_MEME/logo_testSet4}
+ }
+ \caption{Sequence logo of calculated Motifs by MEME}
+ \label{fig:memeLogo}
+\end{figure}
+
+Even worst was the result of Gibbs sampler. This program was only able to find the Motif in test set 
+two and five. For all of the three other sets, Gibbs sample could not find any Motif in the sequences
+(see table \ref{tab:gibbsResult}).
+
+\begin{table}[ht]
+ \centering
+ \caption{Detected Motifs by Gibbs sampler. The letter N means that Gibbs sampler did not give a suggestion for this position.}
+ \begin{tabular}{|l|l|}
+  \hline
+    & Motif \\
+  \hline
+  test set 1 & \textit{No Motifs detected} \\
+  test set 2 & ANTNTTNGCTNANAG \\
+  test set 3 & \textit{No Motifs detected} \\
+  test set 4 & \textit{No Motifs detected} \\
+  test set 5 & TACAGGGGTNC \\
+  \hline
+ \end{tabular}
+ \label{tab:gibbsResult} 
+\end{table}
+
+If we compare the runtime of both programs (see table \ref{tab:runtime}) one can see that MEME is in 
+general a little bit faster. But since we used the webservice of MEME and run Gibbs sampler on a local 
+machine with a single core CPU and just one Gb of RAM, the comparability of theses runtimes may not 
+be given.
+
+\begin{table}
+ \centering
+ \caption{Runtime of used programs in Seconds}
+ \begin{tabular}{|c|c|c|}
+  \hline
+    & MEME & Gibbs sampler \\
+  \hline
+  test set 1 & 1.66 & 1.04 \\
+  test set 2 & 3.33 & 1.13 \\
+  test set 3 & 1.66 & 1.05 \\
+  test set 4 & 1.66 & 0.78 \\
+  test set 5 & 3.33 & 1.19 \\
+  \hline
+ \end{tabular}
+ \label{tab:runtime}
+\end{table}
+
+\subsection*{Discussion}
+
+With the results given above one can see that both, MEME and Gibbs sampler, have a problem with 
+Motifs of too small size. Since the Motif finding problem is not statistically solvable for small 
+Motifs\cite{bioinf1}, this observation makes sense. Also MEME seems to have a higher sensitivity, 
+since it still find a Motif for test set three and four but a wrong one. Obviously for these wrong 
+Motifs the position found by MEME were also wrong but for all other Motifs MEME found the exact 
+positions. On the other hand Gibbs sampler has a lower sensitivity than MEME and it also did not 
+output the positions of the founded Motifs. So it is difficult to proof that Gibbs sampler found 
+the right Motifs.
+
+Under the circumstances discussed above and with respect to the much more user-friendly interface of 
+MEME-Suite we would recommend to use that website.
+
 \newpage
-\bibliography{Assignment6-Ditz_Schroeder-WS15-16.bib}
+\bibliography{Assignment7-Ditz_Schroeder-WS15-16.bib}
 \bibliographystyle{ieeetr}

### 2015-11-30 AssignmentVII/src/SeqGenerators/MotifDeviator.java

@@ -34,12 +34,7 @@ public class MotifDeviator {
 		// Now modify every position now
 		for(int j=0; j<deviationPositions.length; j++){
 			String dev =E.getSymbolByIndex((int) (Math.random()*100)%E.getAlphabetLength());
-			if(tmpMotif.get((deviationPositions[j]-1)).equals(dev)){
-				j--;
-			}
-			else{
 				tmpMotif.set((deviationPositions[j]-1), dev );
-			}
 		}		
 		return tmpMotif;
 	}

### 2015-12-09 AssignmentVIII/Assignment8-Ditz_Schroeder-WS15-16.tex
anfänge des achten übungsblattes

--- 2015-10-19 Assignment II/Assignment1-Ditz_Schroeder-WS15-16.tex
@@
   \begin{vartab}{\thecolmns}
-    \numbers{#1} & $\sum$\\\hline
+    \numbers{#1} & $\sum$ (6+2)\\\hline
     \emptyLine{\thecolmns}\\
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{7}{Alexander Seitz}{26. October 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
+\header{8}{Alexander Seitz}{14. December 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
 
-  \section*{Exercise 1 - \textsl{}}
+\section*{Theoretical Assignment - \textit{Suffix tree construction and application}}
+
+\subsection*{a - \textit{Suffix tree construction}}
+\subsubsection*{i}
+If one uses the naive approach to construct the suffix tree of ``CTAGTAGCAG'', the result would look 
+like Figure \ref{fig:naiveImpl}.
+
+\begin{figure}[ht]
+ \centering
+ \subfigure[step 1]{
+  \includegraphics[width=0.15\textwidth]{tast1ai/tree_step01.png}
+ }
+ \subfigure[step 2]{
+  \includegraphics[width=0.25\textwidth]{tast1ai/tree_step02.png}
+ }
+ \subfigure[step 3]{
+  \includegraphics[width=0.35\textwidth]{tast1ai/tree_step03.png}
+ }
+ \subfigure[step 4]{
+  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step04.png}
+ }
+ \subfigure[step 5]{
+  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step05.png}
+ }
+ \subfigure[step 6]{
+  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step06.png}
+ }
+ \subfigure[step 7]{
+  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step07.png}
+ }
+ \subfigure[step 8]{
+  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step08.png}
+ }
+ \subfigure[step 9]{
+  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step09.png}
+ }
+ \subfigure[step 10]{
+  \includegraphics[width=0.7\textwidth]{tast1ai/tree_step10.png}
+ }
+ \subfigure[step 11]{
+  \includegraphics[width=0.7\textwidth]{tast1ai/tree_step11.png}
+ }
+ \caption{All steps of the naive implementation of suffix tree construction for the string ``CTAGTAGCAG''.}
+ \label{fig:naiveImpl}
+\end{figure}
+
+\subsubsection*{ii}
+
+\subsection*{b - \textit{Main data table of WOTD}}
+
+\subsection*{c - \textit{Suffix tree application}}
+
+\section*{Theoretical Assignment - \textit{Runtime and space complexity of suffix trees}}
+
+\subsection*{a}
+
+\subsection*{b}
+
+\subsection*{c}
 

### 2015-12-09 AssignmentVIII/tast1ai/drawTrees.py

@@ -1,0 +1,85 @@
+#!/bin/python
+
+from graphviz import Digraph
+
+
+def drawTree(nodes, edges, fname):
+  tree = Digraph(comment='suffix tree', format='png')
+  for node in nodes:
+    tree.node(node[0], node[1])
+  for edge in edges:
+    tree.edge(edge[0], edge[1], label=edge[2])
+  tree.render(filename=fname)
+
+
+if __name__ == '__main__':
+  # draw all steps for naive suffix tree constuction of text=CTAGTAGCAG
+
+  # step 1 'C'
+  drawTree([['A',''],['B','']], [['A','B','CTAGTAGCAG$']], 'tree_step01')
+
+  # step 2 'T'
+  drawTree([['A',''],['B',''],['C','']], [['A','B','CTAGTAGCAG$'],['A','C','TAGTAGCAG$']], 'tree_step02')
+
+  # step 3 'A'
+  drawTree([['A',''],['B',''],['C',''],['D','']], 
+           [['A','B','CTAGTAGCAG$'],['A','C','TAGTAGCAG$'], ['A','D','AGTAGCAG$']], 'tree_step03')
+
+  # step 4 'G'
+  drawTree([['A',''],['B',''],['C',''],['D',''],['E','']], 
+           [['A','B','CTAGTAGCAG$'],['A','C','TAGTAGCAG$'], ['A','D','AGTAGCAG$'],['A','E','GTAGCAG$']], 'tree_step04')
+
+  # step 5 'T'
+  drawTree([['A',''],['B',''],['C',''],['D',''],['E',''],['F',''],['G','']],
+           [['A','B','CTAGTAGCAG$'],['A','C','TAG'], ['A','D','AGTAGCAG$'],['A','E','GTAGCAG$'],
+            ['C','F','TAGCAG$'],['C','G','CAG$']], 
+           'tree_step05')
+
+  # step 6 'A'
+  drawTree([['A',''],['B',''],['C',''],['D',''],['E',''],['F',''],['G',''],['H',''],['I','']],
+           [['A','B','CTAGTAGCAG$'],['A','C','TAG'], ['A','D','AG'],['A','E','GTAGCAG$'],
+            ['C','F','TAGCAG$'],['C','G','CAG$'],['D','H','TAGCAG$'],['D','I','CAG$']],
+           'tree_step06')
+
+  # step 7 'G'
[…]

### 2015-12-09 AssignmentVIII/Assignment8-Ditz_Schroeder-WS15-16.tex
Aufgabe 2a ist fertig

@@
 \subsection*{a}
+Assume a text $T$ of length $n$ with $n$ times the letter ``a''. If one build a suffix tree for $T$ 
+using WOTD, each node will have just one c-group with all remaining suffixes in it. So evaluating the 
+root node, one has to compute the longest common prefix of $n$ suffixes, of $n-1$ suffixes for the 
+second node and so on. In each c-group the shortest suffix is of length $1$, so for each node $\bar{u}$ 
+there are just $|R_a{\bar{u}}|$ numbers of comparisons.
+
+Since $T$ is of length $n$ this will lead to an overall runtime of $\sum_{i=1}^{n}i = \frac{1}{2}n(n+1)$, 
+which is in $O(n^2)$. $\square$
 

### 2015-12-09 AssignmentVIII/Assignment8-Ditz_Schroeder-WS15-16.tex
aufgabe 2 b ist fertig

@@
 root node, one has to compute the longest common prefix of $n$ suffixes, of $n-1$ suffixes for the 
-second node and so on. In each c-group the shortest suffix is of length $1$, so for each node $\bar{u}$ 
-there are just $|R_a{\bar{u}}|$ numbers of comparisons.
+second node and so on. In each c-group the shortest suffix is of length $1$, so for each node $\overline{u}$ 
+there are just $|R_a\{\overline{u}\}|$ numbers of comparisons.
 
@@
 \subsection*{b}
+Suffix links are defined as an auxiliary edge that point from branching node $\overline{bw}$ to the branching 
+node $\overline{w}$, if it exists and to the root otherwise. If we now defined a suffix link, such that it 
+points into the other direction (i.e. from branching node $\overline{w}$ to branching node $\overline{bw}$) gives 
+us an efficient method to find maximal unique matches. If we now find a branching node that indicates 
+a unique match (for definition see script) and there is a suffix link that point to another branching node, we know that the current 
+branching node is not a maximal unique match (because it is not left maximal). So we just have to 
+follow the suffix links until we reach a branching node without an outgoing suffix link and we have 
+found a maximal unique match.
 

### 2016-01-09 poodle_project/paper/main.tex
der anfang zum paper, das wir abgeben muessen

\documentclass{bioinfo}
\copyrightyear{2016} \pubyear{2016}

\access{}%Advance Access Publication Date: Day Month Year}
\appnotes{}%Manuscript Category}

\begin{document}
\firstpage{1}

\subtitle{}%Database applications}

\title[POODLE]{POODLE - To the core of your data}
\author[Ditz \textit{et~al}.]{Jonas Ditz\,$^{\text{\sfb 1,}*}$ and Benjamin Schroeder\,$^{\text{\sfb 1,}*}$} 
\address{$^{\text{\sf 1}}$Department of Informatics, Eberhard Karls University, T\"ubingen, 72076, Germany.}

\corresp{$^\ast$To whom correspondence should be addressed.}

\history{}%Received on XXXXX; revised on XXXXX; accepted on XXXXX}

\editor{}%Associate Editor: XXXXXXX}

\abstract{\textbf{Motivation:} Many life science laboratories are still using Excel files do organize their data. 
	This leads to a huge workload for maintenance as well as a inconvenient access and update routine. 
	POODLE provides an easy-to-use and powerful interface to improve the work of your lab.\\
\textbf{Results:} POODLE is a Java-based web interface, which allows you to intuitively access, update and 
manipulate your data.\\
\textbf{Contact:} \href{}{forename.surname@student.uni-tuebingen.de}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{https://github.com/derjedi/BioinformaticsI\-Assigments/tree/master/poodle\_project}
online.}

\maketitle

\section{Introduction}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text. Figure~\ref{fig:01}
shows that the above method  Text Text Text Text  Text Text Text
Text Text Text  Text Text.  \citep{Bag01} wants to know about
{\ldots}{\ldots} text follows.
\begin{equation}
\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
\end{equation}

%\enlargethispage{12pt}

\section{Approach}

Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
Text Text Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
.....

\begin{methods}
\section{Methods}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text
text\vspace*{1pt}

\begin{itemize}
\item for bulleted list, use itemize
\item for bulleted list, use itemize
\item for bulleted list, use itemize\vspace*{1pt}
\end{itemize}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text\vadjust{\newpage}.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text Text Text Text Text Text Text Text Text Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsection{This is subheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
text. Text Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\subsubsection{This is subsubheading}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text\break
text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text
textText Text Text Text Text Text  Text Text Text Text Text Text
Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

\enlargethispage{6pt}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{table}[!t]
\processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
head2 & head3 & head4\\\midrule
row1 & row1 & row1 & row1\\
row2 & row2 & row2 & row2\\
row3 & row3 & row3 & row3\\
row4 & row4 & row4 & row4\\\botrule
\end{tabular}}{This is a footnote}
\end{table}

\end{methods}

\begin{figure}[!tpb]%figure1
\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
\end{minipage}}
%\centerline{\includegraphics{fig01.eps}}
\caption{Caption, caption.}\label{fig:01}
\end{figure}

%\begin{figure}[!tpb]%figure2
%%\centerline{\includegraphics{fig02.eps}}
%\caption{Caption, caption.}\label{fig:02}
%\end{figure}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\subsection{Test1}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\section{Discussion}

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text.

Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
the above method Text Text. Text Text Text  Text Text Text Text
Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
method Text Text. Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
Text.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
%     as it may ignore the figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
Text Text Text Text Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text
Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text  Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about  text text text text

\begin{enumerate}
\item this is item, use enumerate
\item this is item, use enumerate
\item this is item, use enumerate
\end{enumerate}

Text Text Text Text Text Text Text Text Text Text Text Text Text
Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
above method  Text Text Text Text Text Text Text Text Text Text
Text Text.  \citealp{Boffelli03} might want to know about text
text text text Text Text Text Text Text Text  Text Text Text Text
Text Text Text Text Text Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text Text Text Text Text Text Text  Text Text.
\citealp{Boffelli03} might want to know about text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text Text Text Text Text Text\break Text.

Text Text Text Text Text Text  Text Text Text Text Text Text Text
Text Text  Text Text Text Text Text Text.
Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
Text Text Text\vspace*{-10pt}

\section*{Acknowledgements}

Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text
text text text\vspace*{-12pt}

\section*{Funding}

This work has been supported by the... Text Text  Text Text.\vspace*{-12pt}

%\bibliographystyle{natbib}
%\bibliographystyle{achemnat}
%\bibliographystyle{plainnat}
%\bibliographystyle{abbrv}
%\bibliographystyle{bioinformatics}
%
%\bibliographystyle{plain}
%
%\bibliography{Document}

\begin{thebibliography}{}

\bibitem[Bofelli {\it et~al}., 2000]{Boffelli03}
Bofelli,F., Name2, Name3 (2003) Article title, {\it Journal Name}, {\bf 199}, 133-154.

\bibitem[Bag {\it et~al}., 2001]{Bag01}
Bag,M., Name2, Name3 (2001) Article title, {\it Journal Name}, {\bf 99}, 33-54.

\bibitem[Yoo \textit{et~al}., 2003]{Yoo03}
Yoo,M.S. \textit{et~al}. (2003) Oxidative stress regulated genes
in nigral dopaminergic neurnol cell: correlation with the known
pathology in Parkinson's disease. \textit{Brain Res. Mol. Brain
Res.}, \textbf{110}(Suppl. 1), 76--84.

\bibitem[Lehmann, 1986]{Leh86}
Lehmann,E.L. (1986) Chapter title. \textit{Book Title}. Vol.~1, 2nd edn. Springer-Verlag, New York.

\bibitem[Crenshaw and Jones, 2003]{Cre03}
Crenshaw, B.,III, and Jones, W.B.,Jr (2003) The future of clinical
cancer management: one tumor, one chip. \textit{Bioinformatics},
doi:10.1093/bioinformatics/btn000.

\bibitem[Auhtor \textit{et~al}. (2000)]{Aut00}
Auhtor,A.B. \textit{et~al}. (2000) Chapter title. In Smith, A.C.
(ed.), \textit{Book Title}, 2nd edn. Publisher, Location, Vol. 1, pp.
???--???.

\bibitem[Bardet, 1920]{Bar20}
Bardet, G. (1920) Sur un syndrome d'obesite infantile avec
polydactylie et retinite pigmentaire (contribution a l'etude des
formes cliniques de l'obesite hypophysaire). PhD Thesis, name of
institution, Paris, France.

\end{thebibliography}
\end{document}

### 2016-01-10 poodle_project/webInterface/src/SearchForm/GeneralSearchParameter.java
Current state of interface

@@ -67,7 +67,6 @@ public class GeneralSearchParameter extends BasicParameters{
 		GridLayout grid = new GridLayout(4,4);
 		grid.setSpacing(true);
 
-//		((TextField) entryParameters[3]).
 		Label label1 = new Label("General");
 		Label label2 = new Label("Location");
 

### 2016-01-10 poodle_project/paper/main.tex

@@
 \title[POODLE]{POODLE - To the core of your data}
-\author[Ditz \textit{et~al}.]{Jonas Ditz\,$^{\text{\sfb 1,}*}$ and Benjamin Schroeder\,$^{\text{\sfb 1,}*}$} 
+\author[Ditz, Schroeder]{Jonas Ditz\,$^{\text{\sfb 1,}*}$ and Benjamin Schroeder\,$^{\text{\sfb 1,}*}$} 
 \address{$^{\text{\sf 1}}$Department of Informatics, Eberhard Karls University, T\"ubingen, 72076, Germany.}
@@
 
-Equation~(\ref{eq:01}) Text Text Text Text Text Text  Text Text
-Text Text Text Text Text Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-.....
+There are a few obvious drawbacks with Excel files.
 

### 2016-01-10 poodle_project/BlastSearch/BlastParser.java
Blast View and Blast integration started

@@ -1,62 +1,0 @@
-import java.io.*;
-import java.util.*;
-
-import org.biojava.bio.program.sax.*;
-import org.biojava.bio.program.ssbind.*;
-import org.biojava.bio.search.*;
-import org.biojava.bio.seq.db.*;
-import org.xml.sax.*;
-import org.biojava.bio.*;
-
-
-/**
- * Wrapper class to parse BLAST output
- */
-public class BlastParser {
-  
-  public static ArrayList parseResults(String fileName) {
-    try {
-      //get the Blast input as a Stream
-      InputStream is = new FileInputStream(fileName);
- 
-      //make a BlastLikeSAXParser
-      BlastLikeSAXParser parser = new BlastLikeSAXParser();
- 
- 
-      // try to parse, even if the blast version is not recognized.
-      parser.setModeLazy();
- 
- 
-      //make the SAX event adapter that will pass events to a Handler.
-      SeqSimilarityAdapter adapter = new SeqSimilarityAdapter();
- 
-      //set the parsers SAX event adapter
-      parser.setContentHandler(adapter);
- 
-      //The list to hold the SeqSimilaritySearchResults
-      List results = new ArrayList();
- 
-      //create the SearchContentHandler that will build SeqSimilaritySearchResults
-      //in the results List
-      SearchContentHandler builder = new BlastLikeSearchBuilder(results,
-          new DummySequenceDB("queries"), new DummySequenceDBInstallation());
- 
-      //register builder with adapter
-      adapter.setSearchContentHandler(builder);
- 
-      //parse the file, after this the result List will be populated with
-      //SeqSimilaritySearchResults
-      parser.parse(new InputSource(is));
- 
-      //return results
-      return results;
-    }
-    catch (SAXException ex) {
-      //XML problem
-      ex.printStackTrace();
-    }catch (IOException ex) {
-      //IO problem, possibly file not found
-      ex.printStackTrace();
-    }
-  }
-}

### 2016-01-10 poodle_project/BlastSearch/BlastSearch.java

@@ -1,134 +1,0 @@
-import java.io.*;
-import java.util.*;
-
-/**
- * Wrapper class to perform a BLAST search locally
- */
-public class BlastSearch {
-
-  // MEMBER VARIABLES
-  private String blastDB = null;
-  private String blastProgram = null;
-  private String task = null;
-  private String query = null;
-  private long timestemp = 0;
-  private String blastResult = "";
-
-  // CONSTRUCTOR
-  public BlastSearch(String query, String database, String program) {
-    this.blastDB = database;
-    this.blastProgram = program;
-    this.query = query;
-
-    java.util.Date date = new java.util.Date();
-    this.timestemp = date.getTime();
-
-    String[] auxTask = program.split("/");
-    try {
-      this.task = auxTask[auxTask.length -1];
-    } catch (Exception e) {
-      /* ignore */
-    }
-  }
-
-  // MEMBER FUNCTIONS
-
-  // Setter functions
-  public void setBlastDB(String database) {
-    this.blastDB = database;
-  }
-
-  public void setBlastProgram(String program) {
-    this.blastProgram = program;
-  }
-
-  public void setQuery(String query) {
-    this.query = query;
-  }
-
-  // Getter functions
-  public String getBlastDB() {
-    return this.blastDB;
-  }
-
-  public String getBlastProgram() {
-    return this.blastProgram;
-  }
-
-  public String getQuery() {
-    return this.query;
-  }
-
-  public String getResult() {
-    return this.blastResult;
-  }
-
-  // other functions
-  private void createQueryFile(String queryFile) {
-    Writer writer = null;
-
-    try {
-      writer = new BufferedWriter(new OutputStreamWriter(new FileOutputStream(queryFile), "utf-8"));
-      writer.write(">query1" + System.getProperty("line.separator"));
-      writer.write(this.query + System.getProperty("line.separator"));
-      System.out.println(queryFile + " was successfully created");
-    }catch (IOException ex) {
-      System.out.println(ex.toString());
-      ex.printStackTrace();
-    }finally {
-     try {writer.close();} catch (Exception ex) {/*ignore*/}
-    }
-  }
-
-  private void deleteQueryFile(String queryFile) {
-    try {
-      File file = new File(queryFile);
-  
-      if(file.delete()) {
-        System.out.println(queryFile + " was successfully deleted");
-      }else {
-        System.out.println("Was not able to delete " + queryFile);
-      }
-    }catch(Exception e) {
[…]

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/BlastOutput.java

@@ -1,325 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "blastOutputProgram",
-    "blastOutputVersion",
-    "blastOutputReference",
-    "blastOutputDb",
-    "blastOutputQueryID",
-    "blastOutputQueryDef",
-    "blastOutputQueryLen",
-    "blastOutputQuerySeq",
-    "blastOutputParam",
-    "blastOutputIterations",
-    "blastOutputMbstat"
-})
-@XmlRootElement(name = "BlastOutput")
-public class BlastOutput {
-
-    @XmlElement(name = "BlastOutput_program", required = true)
-    protected String blastOutputProgram;
-    @XmlElement(name = "BlastOutput_version", required = true)
-    protected String blastOutputVersion;
-    @XmlElement(name = "BlastOutput_reference", required = true)
-    protected String blastOutputReference;
-    @XmlElement(name = "BlastOutput_db", required = true)
-    protected String blastOutputDb;
-    @XmlElement(name = "BlastOutput_query-ID", required = true)
-    protected String blastOutputQueryID;
-    @XmlElement(name = "BlastOutput_query-def", required = true)
-    protected String blastOutputQueryDef;
-    @XmlElement(name = "BlastOutput_query-len", required = true)
-    protected String blastOutputQueryLen;
-    @XmlElement(name = "BlastOutput_query-seq")
-    protected String blastOutputQuerySeq;
-    @XmlElement(name = "BlastOutput_param", required = true)
-    protected BlastOutputParam blastOutputParam;
[…]

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/BlastOutputIterations.java

@@ -1,62 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import java.util.ArrayList;
-import java.util.List;
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "iteration"
-})
-@XmlRootElement(name = "BlastOutput_iterations")
-public class BlastOutputIterations {
-
-    @XmlElement(name = "Iteration")
-    protected List<Iteration> iteration;
-
-    /**
-     * Gets the value of the iteration property.
-     * 
-     * <p>
-     * This accessor method returns a reference to the live list,
-     * not a snapshot. Therefore any modification you make to the
-     * returned list will be present inside the JAXB object.
-     * This is why there is not a <CODE>set</CODE> method for the iteration property.
-     * 
-     * <p>
-     * For example, to add a new item, do as follows:
-     * <pre>
-     *    getIteration().add(newItem);
-     * </pre>
-     * 
-     * 
-     * <p>
-     * Objects of the following type(s) are allowed in the list
-     * {@link Iteration }
-     * 
-     * 
-     */
-    public List<Iteration> getIteration() {
-        if (iteration == null) {
-            iteration = new ArrayList<Iteration>();
-        }
-        return this.iteration;
-    }
-
-}

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/BlastOutputMbstat.java

@@ -1,55 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "statistics"
-})
-@XmlRootElement(name = "BlastOutput_mbstat")
-public class BlastOutputMbstat {
-
-    @XmlElement(name = "Statistics", required = true)
-    protected Statistics statistics;
-
-    /**
-     * Ruft den Wert der statistics-Eigenschaft ab.
-     * 
-     * @return
-     *     possible object is
-     *     {@link Statistics }
-     *     
-     */
-    public Statistics getStatistics() {
-        return statistics;
-    }
-
-    /**
-     * Legt den Wert der statistics-Eigenschaft fest.
-     * 
-     * @param value
-     *     allowed object is
-     *     {@link Statistics }
-     *     
-     */
-    public void setStatistics(Statistics value) {
-        this.statistics = value;
-    }
-
-}

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/BlastOutputParam.java

@@ -1,55 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "parameters"
-})
-@XmlRootElement(name = "BlastOutput_param")
-public class BlastOutputParam {
-
-    @XmlElement(name = "Parameters", required = true)
-    protected Parameters parameters;
-
-    /**
-     * Ruft den Wert der parameters-Eigenschaft ab.
-     * 
-     * @return
-     *     possible object is
-     *     {@link Parameters }
-     *     
-     */
-    public Parameters getParameters() {
-        return parameters;
-    }
-
-    /**
-     * Legt den Wert der parameters-Eigenschaft fest.
-     * 
-     * @param value
-     *     allowed object is
-     *     {@link Parameters }
-     *     
-     */
-    public void setParameters(Parameters value) {
-        this.parameters = value;
-    }
-
-}

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/Hit.java

@@ -1,190 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "hitNum",
-    "hitId",
-    "hitDef",
-    "hitAccession",
-    "hitLen",
-    "hitHsps"
-})
-@XmlRootElement(name = "Hit")
-public class Hit {
-
-    @XmlElement(name = "Hit_num", required = true)
-    protected String hitNum;
-    @XmlElement(name = "Hit_id", required = true)
-    protected String hitId;
-    @XmlElement(name = "Hit_def", required = true)
-    protected String hitDef;
-    @XmlElement(name = "Hit_accession", required = true)
-    protected String hitAccession;
-    @XmlElement(name = "Hit_len", required = true)
-    protected String hitLen;
-    @XmlElement(name = "Hit_hsps")
-    protected HitHsps hitHsps;
-
-    /**
-     * Ruft den Wert der hitNum-Eigenschaft ab.
-     * 
-     * @return
-     *     possible object is
-     *     {@link String }
-     *     
-     */
-    public String getHitNum() {
-        return hitNum;
-    }
-
-    /**
-     * Legt den Wert der hitNum-Eigenschaft fest.
-     * 
-     * @param value
-     *     allowed object is
-     *     {@link String }
-     *     
-     */
-    public void setHitNum(String value) {
-        this.hitNum = value;
-    }
-
-    /**
-     * Ruft den Wert der hitId-Eigenschaft ab.
-     * 
-     * @return
-     *     possible object is
-     *     {@link String }
-     *     
-     */
[…]

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/HitHsps.java

@@ -1,62 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import java.util.ArrayList;
-import java.util.List;
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "hsp"
-})
-@XmlRootElement(name = "Hit_hsps")
-public class HitHsps {
-
-    @XmlElement(name = "Hsp")
-    protected List<Hsp> hsp;
-
-    /**
-     * Gets the value of the hsp property.
-     * 
-     * <p>
-     * This accessor method returns a reference to the live list,
-     * not a snapshot. Therefore any modification you make to the
-     * returned list will be present inside the JAXB object.
-     * This is why there is not a <CODE>set</CODE> method for the hsp property.
-     * 
-     * <p>
-     * For example, to add a new item, do as follows:
-     * <pre>
-     *    getHsp().add(newItem);
-     * </pre>
-     * 
-     * 
-     * <p>
-     * Objects of the following type(s) are allowed in the list
-     * {@link Hsp }
-     * 
-     * 
-     */
-    public List<Hsp> getHsp() {
-        if (hsp == null) {
-            hsp = new ArrayList<Hsp>();
-        }
-        return this.hsp;
-    }
-
-}

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/Hsp.java

@@ -1,568 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "hspNum",
-    "hspBitScore",
-    "hspScore",
-    "hspEvalue",
-    "hspQueryFrom",
-    "hspQueryTo",
-    "hspHitFrom",
-    "hspHitTo",
-    "hspPatternFrom",
-    "hspPatternTo",
-    "hspQueryFrame",
-    "hspHitFrame",
-    "hspIdentity",
-    "hspPositive",
-    "hspGaps",
-    "hspAlignLen",
-    "hspDensity",
-    "hspQseq",
-    "hspHseq",
-    "hspMidline"
-})
-@XmlRootElement(name = "Hsp")
-public class Hsp {
-
-    @XmlElement(name = "Hsp_num", required = true)
-    protected String hspNum;
-    @XmlElement(name = "Hsp_bit-score", required = true)
-    protected String hspBitScore;
-    @XmlElement(name = "Hsp_score", required = true)
-    protected String hspScore;
-    @XmlElement(name = "Hsp_evalue", required = true)
-    protected String hspEvalue;
-    @XmlElement(name = "Hsp_query-from", required = true)
-    protected String hspQueryFrom;
-    @XmlElement(name = "Hsp_query-to", required = true)
-    protected String hspQueryTo;
-    @XmlElement(name = "Hsp_hit-from", required = true)
-    protected String hspHitFrom;
-    @XmlElement(name = "Hsp_hit-to", required = true)
-    protected String hspHitTo;
[…]

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/Iteration.java

@@ -1,217 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "iterationIterNum",
-    "iterationQueryID",
-    "iterationQueryDef",
-    "iterationQueryLen",
-    "iterationHits",
-    "iterationStat",
-    "iterationMessage"
-})
-@XmlRootElement(name = "Iteration")
-public class Iteration {
-
-    @XmlElement(name = "Iteration_iter-num", required = true)
-    protected String iterationIterNum;
-    @XmlElement(name = "Iteration_query-ID")
-    protected String iterationQueryID;
-    @XmlElement(name = "Iteration_query-def")
-    protected String iterationQueryDef;
-    @XmlElement(name = "Iteration_query-len")
-    protected String iterationQueryLen;
-    @XmlElement(name = "Iteration_hits")
-    protected IterationHits iterationHits;
-    @XmlElement(name = "Iteration_stat")
-    protected IterationStat iterationStat;
-    @XmlElement(name = "Iteration_message")
-    protected String iterationMessage;
-
-    /**
-     * Ruft den Wert der iterationIterNum-Eigenschaft ab.
-     * 
-     * @return
-     *     possible object is
-     *     {@link String }
-     *     
-     */
-    public String getIterationIterNum() {
-        return iterationIterNum;
-    }
-
-    /**
-     * Legt den Wert der iterationIterNum-Eigenschaft fest.
-     * 
-     * @param value
-     *     allowed object is
-     *     {@link String }
-     *     
-     */
[…]

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/IterationHits.java

@@ -1,62 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import java.util.ArrayList;
-import java.util.List;
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "hit"
-})
-@XmlRootElement(name = "Iteration_hits")
-public class IterationHits {
-
-    @XmlElement(name = "Hit")
-    protected List<Hit> hit;
-
-    /**
-     * Gets the value of the hit property.
-     * 
-     * <p>
-     * This accessor method returns a reference to the live list,
-     * not a snapshot. Therefore any modification you make to the
-     * returned list will be present inside the JAXB object.
-     * This is why there is not a <CODE>set</CODE> method for the hit property.
-     * 
-     * <p>
-     * For example, to add a new item, do as follows:
-     * <pre>
-     *    getHit().add(newItem);
-     * </pre>
-     * 
-     * 
-     * <p>
-     * Objects of the following type(s) are allowed in the list
-     * {@link Hit }
-     * 
-     * 
-     */
-    public List<Hit> getHit() {
-        if (hit == null) {
-            hit = new ArrayList<Hit>();
-        }
-        return this.hit;
-    }
-
-}

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/IterationStat.java

@@ -1,55 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "statistics"
-})
-@XmlRootElement(name = "Iteration_stat")
-public class IterationStat {
-
-    @XmlElement(name = "Statistics", required = true)
-    protected Statistics statistics;
-
-    /**
-     * Ruft den Wert der statistics-Eigenschaft ab.
-     * 
-     * @return
-     *     possible object is
-     *     {@link Statistics }
-     *     
-     */
-    public Statistics getStatistics() {
-        return statistics;
-    }
-
-    /**
-     * Legt den Wert der statistics-Eigenschaft fest.
-     * 
-     * @param value
-     *     allowed object is
-     *     {@link Statistics }
-     *     
-     */
-    public void setStatistics(Statistics value) {
-        this.statistics = value;
-    }
-
-}

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/ObjectFactory.java

@@ -1,135 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlRegistry;
-
-
-/**
- * This object contains factory methods for each 
- * Java content interface and Java element interface 
- * generated in the BlastXMLParser package. 
- * <p>An ObjectFactory allows you to programatically 
- * construct new instances of the Java representation 
- * for XML content. The Java representation of XML 
- * content can consist of schema derived interfaces 
- * and classes representing the binding of schema 
- * type definitions, element declarations and model 
- * groups.  Factory methods for each of these are 
- * provided in this class.
- * 
- */
-@XmlRegistry
-public class ObjectFactory {
-
-
-    /**
-     * Create a new ObjectFactory that can be used to create new instances of schema derived classes for package: BlastXMLParser
-     * 
-     */
-    public ObjectFactory() {
-    }
-
-    /**
-     * Create an instance of {@link IterationStat }
-     * 
-     */
-    public IterationStat createIterationStat() {
-        return new IterationStat();
-    }
-
-    /**
-     * Create an instance of {@link Statistics }
-     * 
-     */
-    public Statistics createStatistics() {
-        return new Statistics();
-    }
-
-    /**
-     * Create an instance of {@link Parameters }
-     * 
-     */
-    public Parameters createParameters() {
-        return new Parameters();
-    }
-
-    /**
-     * Create an instance of {@link Hsp }
-     * 
-     */
-    public Hsp createHsp() {
-        return new Hsp();
-    }
-
-    /**
-     * Create an instance of {@link IterationHits }
-     * 
-     */
-    public IterationHits createIterationHits() {
-        return new IterationHits();
-    }
-
-    /**
-     * Create an instance of {@link Hit }
-     * 
-     */
-    public Hit createHit() {
-        return new Hit();
-    }
-
-    /**
-     * Create an instance of {@link BlastOutput }
-     * 
-     */
[…]

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/Parameters.java

@@ -1,298 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "parametersMatrix",
-    "parametersExpect",
-    "parametersInclude",
-    "parametersScMatch",
-    "parametersScMismatch",
-    "parametersGapOpen",
-    "parametersGapExtend",
-    "parametersFilter",
-    "parametersPattern",
-    "parametersEntrezQuery"
-})
-@XmlRootElement(name = "Parameters")
-public class Parameters {
-
-    @XmlElement(name = "Parameters_matrix")
-    protected String parametersMatrix;
-    @XmlElement(name = "Parameters_expect", required = true)
-    protected String parametersExpect;
-    @XmlElement(name = "Parameters_include")
-    protected String parametersInclude;
-    @XmlElement(name = "Parameters_sc-match")
-    protected String parametersScMatch;
-    @XmlElement(name = "Parameters_sc-mismatch")
-    protected String parametersScMismatch;
-    @XmlElement(name = "Parameters_gap-open", required = true)
-    protected String parametersGapOpen;
-    @XmlElement(name = "Parameters_gap-extend", required = true)
-    protected String parametersGapExtend;
-    @XmlElement(name = "Parameters_filter")
-    protected String parametersFilter;
-    @XmlElement(name = "Parameters_pattern")
-    protected String parametersPattern;
-    @XmlElement(name = "Parameters_entrez-query")
-    protected String parametersEntrezQuery;
-
-    /**
-     * Ruft den Wert der parametersMatrix-Eigenschaft ab.
-     * 
-     * @return
[…]

### 2016-01-10 poodle_project/BlastSearch/BlastXMLParser/sources/BlastXMLParser/Statistics.java

@@ -1,217 +1,0 @@
-//
-// Diese Datei wurde mit der JavaTM Architecture for XML Binding(JAXB) Reference Implementation, v2.2.8-b130911.1802 generiert 
-// Siehe <a href="http://java.sun.com/xml/jaxb">http://java.sun.com/xml/jaxb</a> 
-// Änderungen an dieser Datei gehen bei einer Neukompilierung des Quellschemas verloren. 
-// Generiert: 2015.12.22 um 01:09:47 PM CET 
-//
-
-
-package BlastXMLParser;
-
-import javax.xml.bind.annotation.XmlAccessType;
-import javax.xml.bind.annotation.XmlAccessorType;
-import javax.xml.bind.annotation.XmlElement;
-import javax.xml.bind.annotation.XmlRootElement;
-import javax.xml.bind.annotation.XmlType;
-
-
-/**
- * 
- */
-@XmlAccessorType(XmlAccessType.FIELD)
-@XmlType(name = "", propOrder = {
-    "statisticsDbNum",
-    "statisticsDbLen",
-    "statisticsHspLen",
-    "statisticsEffSpace",
-    "statisticsKappa",
-    "statisticsLambda",
-    "statisticsEntropy"
-})
-@XmlRootElement(name = "Statistics")
-public class Statistics {
-
-    @XmlElement(name = "Statistics_db-num", required = true)
-    protected String statisticsDbNum;
-    @XmlElement(name = "Statistics_db-len", required = true)
-    protected String statisticsDbLen;
-    @XmlElement(name = "Statistics_hsp-len", required = true)
-    protected String statisticsHspLen;
-    @XmlElement(name = "Statistics_eff-space", required = true)
-    protected String statisticsEffSpace;
-    @XmlElement(name = "Statistics_kappa", required = true)
-    protected String statisticsKappa;
-    @XmlElement(name = "Statistics_lambda", required = true)
-    protected String statisticsLambda;
-    @XmlElement(name = "Statistics_entropy", required = true)
-    protected String statisticsEntropy;
-
-    /**
-     * Ruft den Wert der statisticsDbNum-Eigenschaft ab.
-     * 
-     * @return
-     *     possible object is
-     *     {@link String }
-     *     
-     */
-    public String getStatisticsDbNum() {
-        return statisticsDbNum;
-    }
-
-    /**
-     * Legt den Wert der statisticsDbNum-Eigenschaft fest.
-     * 
-     * @param value
-     *     allowed object is
[…]

### 2016-01-10 poodle_project/BlastSearch/RunBlastSearch.java

@@ -1,28 +1,0 @@
-import java.io.*;
-import java.util.*;
-
-public class RunBlastSearch {
-
-  static public void main(String[] args) throws Exception {
-    String mode = args[0];
-    String program = args[1];
-    String sequence = args[2];
-    String database = args[3];
-    String query = args[4];
-    String blastResult = null;
-
-    if (mode.equals("local")) {
-      BlastSearch localBlast = new BlastSearch(sequence, database, program);
-      localBlast.runBlastSearch();
-      blastResult = localBlast.getResult();
-    }else if(mode.equals("NCBI")) {
-      // perform NCBI search
-      NCBIQBlastClass ncbiBlast = new NCBIQBlastClass();
-      //ncbiBlast.runBLASTRequest(program, sequence, database, query);
-      ncbiBlast.runBLASTRequest("blastp", "MKWVTFISLLFLFSSAYSRGVFRRDAHKSEVAHRFKDLGEENFKALVLIAFAQYLQQCP", "swissprot", "\"serum albumin\"[Protein name] AND mammals[Organism]");
-      blastResult = ncbiBlast.getResult();
-    }
-    
-    System.out.println(blastResult);
-  }
-}

### 2016-01-10 poodle_project/webInterface/src/SearchForm/BasicParameters.java

@@ -1,84 +1,0 @@
-package SearchForm;
-
-import com.vaadin.ui.Component;
-import com.vaadin.ui.GridLayout;
-import com.vaadin.ui.Label;
-import com.vaadin.ui.TextField;
-import com.vaadin.ui.VerticalLayout;
-
-public abstract class BasicParameters extends VerticalLayout {
-	//Grid Layout:
-	protected GridLayout grid;
-	//Search Parameter:
-	protected TextField[] parameters;
-	protected Component[] entryParameters;
-	protected Label title = new Label("unknown");
-	//Rest Navigation
-	Label displays = new Label("General Parameters.");
-	public void fill(String[][] strings){
-		for(int j=0; j< strings.length; j++){
-			for(int i=0; i< parameters.length; i++){
-				if(parameters[i].getDescription().equals(strings[j][0])){
-					parameters[i].setValue(strings[j][1]);
-				}
-			}
-		}
-	}
-	public void changeViewSmall(){
-		this.removeAllComponents();
-		grid= new GridLayout(3,(parameters.length/3)+2);
-
-		int j=-1;
-		for(int i=0; i<parameters.length; i++){
-			if(i%3==0){
-				j++;
-			}
-			parameters[i].setWidth("175px");
-//			parameters[i].setHeight("25px");
-			grid.addComponent(parameters[i], j, i%3);
-		}
-		this.addComponent(grid);
-	}
-
-	public void changeViewLarge(){
-		this.removeAllComponents();
-
-		grid = new GridLayout(2,4);
-		
-		int j=-1;
-		for(int i=0; i<parameters.length; i++){
-			if(i%4==0){
-				j++;
-			}
-			grid.addComponent(parameters[i], j, i%4);
-		}
-		grid.setSpacing(true);
-		
-		this.addComponent(title);
-		this.addComponent(grid);
-	}
-	
-	public void changeToEntryForm(){
-		this.removeAllComponents();
-	}
-	
-	public String getParameter(int x){
-		return  parameters[x].getValue();
-	}
-	public String[][] getParamteters(){
-		String[][] entry = new String[parameters.length][2];
-		for (int i=0; i< entry.length; i++){
-			entry[i][0] = parameters[i].getCaption();
-			entry[i][1] = parameters[i].getValue();
-		}
-		return entry;
-	}
-	public void refreshTextfields(){
-		for(int i=0; i<parameters.length; i++){
-			parameters[i].setValue("");
-		}
-	}
[…]

### 2016-01-10 poodle_project/webInterface/src/SearchForm/GeneralSearchParameter.java

@@ -1,110 +1,0 @@
-package SearchForm;
-
-import com.vaadin.ui.*;
-
-import java.util.Date;
-
-import javax.servlet.annotation.WebServlet;
-
-import com.vaadin.annotations.DesignRoot;
-import com.vaadin.annotations.Theme;
-import com.vaadin.annotations.VaadinServletConfiguration;
-import com.vaadin.data.Property;
-import com.vaadin.server.UserError;
-import com.vaadin.server.VaadinRequest;
-import com.vaadin.server.VaadinServlet;
-import com.vaadin.ui.Button.ClickEvent;
-import com.vaadin.ui.Field.ValueChangeEvent;
-import com.vaadin.ui.declarative.Design;
-
-import sqlClasses.SQLCommunicator;
-
-
-public class GeneralSearchParameter extends BasicParameters{
-	private DateField date;
-
-	public GeneralSearchParameter() {
-		parameters = new TextField[7];
-		entryParameters = new TextField[5];
-
-		title = new Label("General Parameters");
-
-		//Parameters for a Search request!
-		parameters[0] = new TextField("Id");
-		parameters[1] = new TextField("box");
-		parameters[2] = new TextField("position");
-		parameters[3] = new TextField("name");
-		parameters[4] = new TextField("date");
-		parameters[5] = new TextField("author");
-		parameters[6] = new TextField("protein");
-
-		//Parameters for a New Entry
-		entryParameters[0] = new TextField("Id");
-		entryParameters[1] = new TextField("box");
-		entryParameters[2] = new TextField("position");
-		entryParameters[3] = new TextField("name");
-		entryParameters[4] = new TextField("author");
-		date = new DateField("date");
-
-
-		
-		// some adjustification for parameter fields:
-		this.fillID();
-		entryParameters[0].setEnabled(false);
-		
-		((TextField) entryParameters[1]).setNullSettingAllowed(false);
-		
-		date.setValue(new java.util.Date());
-		date.setImmediate(true);
-		date.setValidationVisible(true);
-
-		
-		this.changeViewLarge();         
-	}
-
-	public void changeToEntryForm(SQLCommunicator sqlC){
-		this.removeAllComponents();
-		GridLayout grid = new GridLayout(4,4);
-		grid.setSpacing(true);
-
-		Label label1 = new Label("General");
-		Label label2 = new Label("Location");
-
-		grid.addComponent(label1, 0, 0);
[…]

### 2016-01-10 poodle_project/webInterface/src/SearchForm/PrimerParameter.java

@@ -1,81 +1,0 @@
-package SearchForm;
-
-import com.vaadin.ui.Component;
-import com.vaadin.ui.GridLayout;
-import com.vaadin.ui.Label;
-import com.vaadin.ui.OptionGroup;
-import com.vaadin.ui.TextField;
-import com.vaadin.ui.VerticalLayout;
-
-public class PrimerParameter extends BasicParameters{
-
-	//Rest Navigation
-	Label     displays = new Label("Primer Parameters.");
-
-	public PrimerParameter() {
-		title = new Label("Primer Parameters");
-		parameters = new TextField[5];
-		entryParameters = new Component[13];
-		
-		//Search Parameter:
-		parameters[0] = new TextField("project");
-		parameters[1] = new TextField("organism");
-		parameters[2] = new TextField("protein");
-		parameters[3] = new TextField("domain");
-		parameters[4] = new TextField("restrictionSite");
-		
-		entryParameters[0] = new OptionGroup("cloning types");
-		entryParameters[1] = new TextField("restriction sites");
-		entryParameters[2] = new TextField("direction");
-		
-		entryParameters[3] = new TextField("melting temperatur");
-		entryParameters[4] = new TextField("concentration");
-		
-		entryParameters[5] = new TextField("primer Sequence");
-		entryParameters[6] = new TextField("protein sequence");
-		
-		entryParameters[7] = new TextField("notes");
-
-		((OptionGroup) entryParameters[0]).addItems("classic", "QC", "RF");
-		
-		addComponent(displays);
-		this.changeViewLarge();
-	}
-	public void changeToEntryForm(){
-		this.removeAllComponents();
-		GridLayout grid = new GridLayout(4,12);
-		Label label1 = new Label("organisatory");
-		Label label2 = new Label("biology");
-		Label label3 = new Label("cloning");
-		Label label4 = new Label("specifications");
-		Label label5 = new Label("sequences");
-		Label label6 = new Label("rest");
-		
-		grid.addComponent(label1, 0, 0);
-		grid.addComponent(parameters[0], 1, 1);
-		grid.addComponent(parameters[1], 2, 1);
-		grid.addComponent(parameters[2], 3, 1);
-		
-		grid.addComponent(label2, 0, 2);
-		grid.addComponent(parameters[3], 1, 3);
-		grid.addComponent(parameters[4], 2, 3);
[…]

### 2016-01-10 poodle_project/webInterface/src/SearchForm/ProteinConstructParameter.java

@@ -1,91 +1,0 @@
-package SearchForm;
-
-import com.vaadin.ui.Component;
-import com.vaadin.ui.GridLayout;
-import com.vaadin.ui.Label;
-import com.vaadin.ui.OptionGroup;
-import com.vaadin.ui.TextField;
-import com.vaadin.ui.VerticalLayout;
-
-public class ProteinConstructParameter extends BasicParameters{
-
-	    public ProteinConstructParameter() {
-			title= new Label("Protein Construct Parameter");
-			
-			parameters = new TextField[5];
-			//Search Parameter:
-			parameters[0]   = new TextField("C-Tags");
-			parameters[1]   = new TextField("N-Tags");
-			parameters[2]   = new TextField("Mutation");
-			parameters[3]   = new TextField("protein-family");
-			parameters[4]   = new TextField("vector");			
-			
-			//entry Parameter:
-			entryParameters = new Component[17];
-			
-			entryParameters[0]   = new TextField("C-Tags");
-			entryParameters[1]   = new TextField("N-Tags");
-			entryParameters[2]   = new TextField("Mutation");
-			entryParameters[3]   = new TextField("protein-family");
-			entryParameters[4]   = new TextField("vector");
-			entryParameters[5] = new TextField("protein");
-			entryParameters[6] = new TextField("domain");
-			
-			entryParameters[7] = new TextField("mutation");
-			entryParameters[8] = new TextField("backbone vector");
-			entryParameters[9] = new TextField("antibiotics");
-			
-			entryParameters[10] = new TextField("cloning sites");
-			entryParameters[11] = new OptionGroup("cloning types");
-			
-			entryParameters[12] = new TextField("used primer");
-			entryParameters[13] = new TextField("constructed from vector");
-			
-			entryParameters[14] = new TextField("concentration");
-			entryParameters[15] = new OptionGroup("cell stocks");
-			entryParameters[16] = new TextField("notes");
-			
-			((OptionGroup) entryParameters[15]).addItems("DH5A", "C+");
-			((OptionGroup) entryParameters[11]).addItems("classic", "QC", "RF");
-						
-	        this.changeViewLarge();
-	    }
-	    public void changeToEntryForm(){
-			this.removeAllComponents();
-			GridLayout grid = new GridLayout(4,14);
-			Label label1 = new Label("organisatory");
[…]

### 2016-01-10 poodle_project/webInterface/src/SearchForm/VectorParameter.java

@@ -1,80 +1,0 @@
-package SearchForm;
-
-import com.vaadin.ui.*;
-import javax.servlet.annotation.WebServlet;
-
-import com.vaadin.annotations.DesignRoot;
-import com.vaadin.annotations.Theme;
-import com.vaadin.annotations.VaadinServletConfiguration;
-import com.vaadin.server.VaadinRequest;
-import com.vaadin.server.VaadinServlet;
-import com.vaadin.ui.Button.ClickEvent;
-import com.vaadin.ui.declarative.Design;
-
-
-public class VectorParameter extends BasicParameters{
-	    public VectorParameter() {
-			parameters = new TextField[2];
-
-			//Search Parameter:
-			parameters[0]   = new TextField("Tags");
-			parameters[1]   = new TextField("Tev cleavage?");
-
-			
-			//entry Parameter:
-			entryParameters = new Component[17];
-			
-			entryParameters[0]   = new TextField("C-Term-Tags");
-			entryParameters[1]   = new TextField("N-Term-Tags");
-			entryParameters[2]   = new TextField("Construct cleavage?");
-			
-			entryParameters[3]   = new TextField("MCS");
-			entryParameters[4]   = new TextField("antibiotics");
-			
-			entryParameters[5] = new TextField("fw seq primer");
-			entryParameters[6] = new TextField("rv seq primer");
-			
-			entryParameters[7] = new TextField("vector map");
-			entryParameters[8] = new TextField("concentration");
-			entryParameters[9] = new OptionGroup("cell stock");
-			
-			entryParameters[10] = new TextField("notes");
-			
-			((OptionGroup) entryParameters[9]).addItems("DH5A", "C+");
-			
-			title = new Label("Vector Parameters");
-	        this.changeViewLarge();
-	    }
-	    public void changeToEntryForm(){
-			this.removeAllComponents();
-			GridLayout grid = new GridLayout(4,10);
-			Label label1 = new Label("construct specifications");
-			Label label2 = new Label("cloning");
-			Label label3 = new Label("sequencing");
-			Label label4 = new Label("specifications");
-
-			
-			grid.addComponent(label1, 0, 0);
-			grid.addComponent(entryParameters[0], 1, 1);
-			grid.addComponent(entryParameters[1], 2, 1);
-			grid.addComponent(entryParameters[2], 3, 1);	
-			
[…]

### 2016-01-10 poodle_project/webInterface/src/com/poodledb/PoodledbUI.java

@@ -20,7 +20,7 @@ import com.vaadin.ui.MenuBar.MenuItem;
 import com.vaadin.ui.declarative.Design;
 import com.vaadin.ui.themes.ValoTheme;
 
-import SearchForm.GeneralSearchParameter;
+import Forms.GeneralSearchParameter;
 import contentViews.BlastView;
 import contentViews.NewEntryView;
 import contentViews.SearchResultView;
@@ -49,7 +49,7 @@ public class PoodledbUI extends UI {
 	private SearchView searchView;	// the class which provides the normal search context
 	private NewEntryView newEntryView;	//class for newEntry 
 	private BlastView blastView;	//class for new Blast run.
-	
+
 	
 	//control elements
 	private Boolean viewIsReduced=false;
@@ -94,7 +94,7 @@ public class PoodledbUI extends UI {
 		//initial ContentContainer:
 		searchView = new SearchView(this);
 		newEntryView = new NewEntryView(this);
-		blastView = new BlastView();
+		blastView = new BlastView(this);
 		content= searchView;
 		
 		//whole building page, peace by peace
@@ -118,6 +118,8 @@ public class PoodledbUI extends UI {
 		layout.addComponent(navigationMenu);
 		layout.addComponent(serverTableSelection);
 		layout.addComponent(content);
+		layout.setDefaultComponentAlignment(Alignment.TOP_CENTER);
+		content.setDefaultComponentAlignment(Alignment.TOP_CENTER);
 	}
 	
 	

### 2016-01-10 poodle_project/webInterface/src/contentViews/NewEntryView.java

@@ -5,12 +5,12 @@ import com.vaadin.annotations.Push;
 import com.vaadin.ui.*;
 import com.vaadin.ui.Button.ClickEvent;
 
-import SearchForm.GeneralSearchParameter;
-import SearchForm.PrimerParameter;
-import SearchForm.ProteinConstructParameter;
-import SearchForm.VectorParameter;
+import Forms.GeneralSearchParameter;
+import Forms.PrimerParameter;
+import Forms.ProteinConstructParameter;
+import Forms.VectorParameter;
+import PackageCommunicators.SQLCommunicator;
 import pageElements.SearchBar;
-import sqlClasses.SQLCommunicator;
 
 public class NewEntryView extends VerticalLayout {
 		
@@ -43,10 +43,12 @@ public class NewEntryView extends VerticalLayout {
 			//Layout
 			this.setDefaultComponentAlignment(Alignment.TOP_CENTER);
 			this.setSpacing(true);
+			this.setMargin(true);
 
 			//Parameters
 			parameters = new VerticalLayout();
 			parameters.setSpacing(true);
+			
 			
 			//Buttons:
 			//newEntry Button 

### 2016-01-10 poodle_project/webInterface/src/contentViews/SearchResultView.java

@@ -5,14 +5,14 @@ import com.vaadin.annotations.Push;
 import com.vaadin.data.Container.Filter;
 import com.vaadin.ui.*;
 
-import SearchForm.GeneralSearchParameter;
-import SearchForm.PrimerParameter;
-import SearchForm.ProteinConstructParameter;
-import SearchForm.VectorParameter;
+import Forms.GeneralSearchParameter;
+import Forms.PrimerParameter;
+import Forms.ProteinConstructParameter;
+import Forms.VectorParameter;
+import PackageCommunicators.SQLCommunicator;
 import pageElements.NavigationBar;
 import pageElements.SearchBar;
 import specificValues.WiesnerTables;
-import sqlClasses.SQLCommunicator;
 
 @Push
 public class SearchResultView extends VerticalLayout{

### 2016-01-10 poodle_project/webInterface/src/contentViews/SearchView.java

@@ -5,14 +5,15 @@ import com.vaadin.annotations.Push;
 import com.vaadin.ui.Alignment;
 import com.vaadin.ui.Button;
 import com.vaadin.ui.Button.ClickEvent;
+
+import Forms.GeneralSearchParameter;
+import Forms.PrimerParameter;
+import Forms.ProteinConstructParameter;
+import Forms.VectorParameter;
+import PackageCommunicators.SQLCommunicator;
+
 import com.vaadin.ui.HorizontalLayout;
 import com.vaadin.ui.VerticalLayout;
-
-import SearchForm.GeneralSearchParameter;
-import SearchForm.PrimerParameter;
-import SearchForm.ProteinConstructParameter;
-import SearchForm.VectorParameter;
-import sqlClasses.SQLCommunicator;
 
 @Push
 public class SearchView extends BasicView{

### 2016-01-10 poodle_project/webInterface/src/pageElements/NavigationBar.java

@@ -22,6 +22,7 @@ public class NavigationBar extends MenuBar{
 	
 	
 	//Commands for Navigation Bar
+	//new Command for the searchPage link page
 	MenuBar.Command searchCommand = new MenuBar.Command() {
 	    public void menuSelected(MenuItem selectedItem) {
 	    	if(poodledb.getViewIsReduced()){
@@ -32,7 +33,7 @@ public class NavigationBar extends MenuBar{
 	    	poodledb.getServerTable().setForSearchView();
 	    }
 	};
-	
+	//new Command for the newEntry link page
 	MenuBar.Command newEntryCommand = new MenuBar.Command() {
 	    public void menuSelected(MenuItem selectedItem) {
 	    	poodledb.SetContentBox(poodledb.getNewEntryView());
@@ -40,7 +41,7 @@ public class NavigationBar extends MenuBar{
 	    	poodledb.getServerTable().setForNewEntryView();
 	    }
 	};
-	
+	//new Command for the Blast link page
 	MenuBar.Command blastCommand = new MenuBar.Command() {
 	    public void menuSelected(MenuItem selectedItem) {
 	    	poodledb.SetContentBox(poodledb.getBlastView());

### 2016-01-10 poodle_project/webInterface/src/pageElements/SearchBar.java

@@ -6,12 +6,12 @@ import com.vaadin.server.FileResource;
 import com.vaadin.ui.*;
 import com.vaadin.ui.Button.ClickEvent;
 
-import SearchForm.GeneralSearchParameter;
-import SearchForm.PrimerParameter;
-import SearchForm.ProteinConstructParameter;
-import SearchForm.VectorParameter;
+import Forms.GeneralSearchParameter;
+import Forms.PrimerParameter;
+import Forms.ProteinConstructParameter;
+import Forms.VectorParameter;
+import PackageCommunicators.SQLCommunicator;
 import contentViews.SearchResultView;
-import sqlClasses.SQLCommunicator;
 
 public class SearchBar extends HorizontalLayout {
 

### 2016-01-10 poodle_project/webInterface/src/sqlClasses/SQLCommunicator.java

@@ -1,233 +1,0 @@
-package sqlClasses;
-
-import java.sql.SQLException;
-
-import com.vaadin.data.Container.*;
-import com.vaadin.data.util.filter.Compare.Equal;
-import com.vaadin.data.util.filter.Like;
-import com.vaadin.data.util.sqlcontainer.SQLContainer;
-import com.vaadin.data.util.sqlcontainer.connection.*;
-import com.vaadin.data.util.sqlcontainer.query.TableQuery;
-import com.vaadin.server.VaadinService;
-
-import SearchForm.GeneralSearchParameter;
-import SearchForm.PrimerParameter;
-import SearchForm.ProteinConstructParameter;
-import SearchForm.VectorParameter;
-
-import org.sqlite.*;
-
-
-public class SQLCommunicator {
-
-	private JDBCConnectionPool pool;
-	private String db;
-	private String table;
-	private TableQuery tq;
-	private SQLContainer container;
-	private SQLContainer primerContainer;
-	private SQLContainer vectorContainer;
-	private SQLContainer proteinContainer;
-
-
-
-	public SQLCommunicator(String db){
-		this.setDb(db);
-		String basepath= VaadinService.getCurrent().getBaseDirectory().getAbsolutePath();
-		String dbPath = "/WEB-INF/db/poodle_sqlite3.dat";
-		try {
-			pool = new SimpleJDBCConnectionPool("org.sqlite.JDBC", "jdbc:sqlite:"+basepath+dbPath, "", "", 2, 5);
-		} catch (SQLException e) {
-			// TODO Auto-generated catch block
-			e.printStackTrace();
-		}
-	}
-
-	public void setTableQuerry(String a){
-		table = a;
-		TableQuery tq1;
-		TableQuery tq2;
-		TableQuery tq3;
-
-		switch(a){
-		case "all":
-			tq1= new TableQuery("Primer", pool);
-			tq1.setVersionColumn("OPTLOCK");
-			try {
-				primerContainer = new SQLContainer(tq1);
-			} catch (SQLException e) {
-				// TODO Auto-generated catch block
-				e.printStackTrace();
-			}
-
-			tq2= new TableQuery("cloningVectors", pool);
-			tq2.setVersionColumn("OPTLOCK");
-			try {
-				vectorContainer = new SQLContainer(tq2);
-			} catch (SQLException e) {
-				// TODO Auto-generated catch block
-				e.printStackTrace();
-			}
-
-			tq3= new TableQuery("proteinConstructs", pool);
[…]

### 2016-01-10 poodle_project/webInterface/src/Forms/BasicParameters.java
bla

@@ -1,0 +1,84 @@
+package Forms;
+
+import com.vaadin.ui.Component;
+import com.vaadin.ui.GridLayout;
+import com.vaadin.ui.Label;
+import com.vaadin.ui.TextField;
+import com.vaadin.ui.VerticalLayout;
+
+public abstract class BasicParameters extends VerticalLayout {
+	//Grid Layout:
+	protected GridLayout grid;
+	//Search Parameter:
+	protected TextField[] parameters;
+	protected Component[] entryParameters;
+	protected Label title = new Label("unknown");
+	//Rest Navigation
+	Label displays = new Label("General Parameters.");
+	public void fill(String[][] strings){
+		for(int j=0; j< strings.length; j++){
+			for(int i=0; i< parameters.length; i++){
+				if(parameters[i].getDescription().equals(strings[j][0])){
+					parameters[i].setValue(strings[j][1]);
+				}
+			}
+		}
+	}
+	public void changeViewSmall(){
+		this.removeAllComponents();
+		grid= new GridLayout(3,(parameters.length/3)+2);
+
+		int j=-1;
+		for(int i=0; i<parameters.length; i++){
+			if(i%3==0){
+				j++;
+			}
+			parameters[i].setWidth("175px");
+//			parameters[i].setHeight("25px");
+			grid.addComponent(parameters[i], j, i%3);
+		}
+		this.addComponent(grid);
+	}
+
+	public void changeViewLarge(){
+		this.removeAllComponents();
+
+		grid = new GridLayout(2,4);
+		
+		int j=-1;
+		for(int i=0; i<parameters.length; i++){
+			if(i%4==0){
+				j++;
+			}
+			grid.addComponent(parameters[i], j, i%4);
+		}
+		grid.setSpacing(true);
+		
+		this.addComponent(title);
+		this.addComponent(grid);
+	}
+	
+	public void changeToEntryForm(){
+		this.removeAllComponents();
+	}
+	
+	public String getParameter(int x){
+		return  parameters[x].getValue();
+	}
+	public String[][] getParamteters(){
+		String[][] entry = new String[parameters.length][2];
+		for (int i=0; i< entry.length; i++){
+			entry[i][0] = parameters[i].getCaption();
+			entry[i][1] = parameters[i].getValue();
+		}
+		return entry;
+	}
+	public void refreshTextfields(){
+		for(int i=0; i<parameters.length; i++){
+			parameters[i].setValue("");
+		}
+	}
[…]

### 2016-01-10 poodle_project/webInterface/src/Forms/BlastSeqField.java

@@ -1,0 +1,52 @@
+package Forms;
+
+import com.vaadin.server.Sizeable.Unit;
+import com.vaadin.server.UserError;
+import com.vaadin.ui.Alignment;
+import com.vaadin.ui.TextArea;
+
+public class BlastSeqField extends BasicParameters{
+	/**
+	 * 
+	 */
+	private static final long serialVersionUID = 1L;
+	private TextArea seq = new TextArea("Sequence");
+
+	public BlastSeqField(){
+
+		//Layout:
+		this.setDefaultComponentAlignment(Alignment.TOP_CENTER);
+
+		//Textfield Settings
+		seq.setInputPrompt("Here Sequence");
+		seq.setSizeFull();
+		seq.setWordwrap(true);
+		seq.setWidth((float) (this.getWidth()*0.75), Unit.PERCENTAGE);
+
+		//adding to layer
+		this.addComponent(seq);
+	}
+
+
+	public String evaluateSequence() throws Exception{
+		if(seq.getValue()==""){
+			seq.setComponentError(new UserError("This field is required!"));
+			throw new Exception("value Missing");
+		}
+		else{
+			return seq.getValue();
+		}
+	}
+
+	//------------------------------------------------------------------------------------------------------------------------
+	//Getter and Setter:
+	//------------------------------------------------------------------------------------------------------------------------		
+
+	public void setSeq(TextArea seq){
+		this.seq=seq;
+	}
+
+	public TextArea getSeq(){
+		return seq;
+	}
+}

### 2016-01-10 poodle_project/webInterface/src/Forms/GeneralSearchParameter.java

@@ -1,0 +1,110 @@
+package Forms;
+
+import com.vaadin.ui.*;
+
+import java.util.Date;
+
+import javax.servlet.annotation.WebServlet;
+
+import com.vaadin.annotations.DesignRoot;
+import com.vaadin.annotations.Theme;
+import com.vaadin.annotations.VaadinServletConfiguration;
+import com.vaadin.data.Property;
+import com.vaadin.server.UserError;
+import com.vaadin.server.VaadinRequest;
+import com.vaadin.server.VaadinServlet;
+import com.vaadin.ui.Button.ClickEvent;
+import com.vaadin.ui.Field.ValueChangeEvent;
+import com.vaadin.ui.declarative.Design;
+
+import PackageCommunicators.SQLCommunicator;
+
+
+public class GeneralSearchParameter extends BasicParameters{
+	private DateField date;
+
+	public GeneralSearchParameter() {
+		parameters = new TextField[7];
+		entryParameters = new TextField[5];
+
+		title = new Label("General Parameters");
+
+		//Parameters for a Search request!
+		parameters[0] = new TextField("Id");
+		parameters[1] = new TextField("box");
+		parameters[2] = new TextField("position");
+		parameters[3] = new TextField("name");
+		parameters[4] = new TextField("date");
+		parameters[5] = new TextField("author");
+		parameters[6] = new TextField("protein");
+
+		//Parameters for a New Entry
+		entryParameters[0] = new TextField("Id");
+		entryParameters[1] = new TextField("box");
+		entryParameters[2] = new TextField("position");
+		entryParameters[3] = new TextField("name");
+		entryParameters[4] = new TextField("author");
+		date = new DateField("date");
+
+
+		
+		// some adjustification for parameter fields:
+		this.fillID();
+		entryParameters[0].setEnabled(false);
+		
+		((TextField) entryParameters[1]).setNullSettingAllowed(false);
+		
+		date.setValue(new java.util.Date());
+		date.setImmediate(true);
+		date.setValidationVisible(true);
+
+		
+		this.changeViewLarge();         
+	}
+
+	public void changeToEntryForm(SQLCommunicator sqlC){
+		this.removeAllComponents();
+		GridLayout grid = new GridLayout(4,4);
+		grid.setSpacing(true);
+
+		Label label1 = new Label("General");
+		Label label2 = new Label("Location");
+
+		grid.addComponent(label1, 0, 0);
[…]

### 2016-01-10 poodle_project/webInterface/src/Forms/PrimerParameter.java

@@ -1,0 +1,81 @@
+package Forms;
+
+import com.vaadin.ui.Component;
+import com.vaadin.ui.GridLayout;
+import com.vaadin.ui.Label;
+import com.vaadin.ui.OptionGroup;
+import com.vaadin.ui.TextField;
+import com.vaadin.ui.VerticalLayout;
+
+public class PrimerParameter extends BasicParameters{
+
+	//Rest Navigation
+	Label     displays = new Label("Primer Parameters.");
+
+	public PrimerParameter() {
+		title = new Label("Primer Parameters");
+		parameters = new TextField[5];
+		entryParameters = new Component[13];
+		
+		//Search Parameter:
+		parameters[0] = new TextField("project");
+		parameters[1] = new TextField("organism");
+		parameters[2] = new TextField("protein");
+		parameters[3] = new TextField("domain");
+		parameters[4] = new TextField("restrictionSite");
+		
+		entryParameters[0] = new OptionGroup("cloning types");
+		entryParameters[1] = new TextField("restriction sites");
+		entryParameters[2] = new TextField("direction");
+		
+		entryParameters[3] = new TextField("melting temperatur");
+		entryParameters[4] = new TextField("concentration");
+		
+		entryParameters[5] = new TextField("primer Sequence");
+		entryParameters[6] = new TextField("protein sequence");
+		
+		entryParameters[7] = new TextField("notes");
+
+		((OptionGroup) entryParameters[0]).addItems("classic", "QC", "RF");
+		
+		addComponent(displays);
+		this.changeViewLarge();
+	}
+	public void changeToEntryForm(){
+		this.removeAllComponents();
+		GridLayout grid = new GridLayout(4,12);
+		Label label1 = new Label("organisatory");
+		Label label2 = new Label("biology");
+		Label label3 = new Label("cloning");
+		Label label4 = new Label("specifications");
+		Label label5 = new Label("sequences");
+		Label label6 = new Label("rest");
+		
+		grid.addComponent(label1, 0, 0);
+		grid.addComponent(parameters[0], 1, 1);
+		grid.addComponent(parameters[1], 2, 1);
+		grid.addComponent(parameters[2], 3, 1);
+		
+		grid.addComponent(label2, 0, 2);
+		grid.addComponent(parameters[3], 1, 3);
+		grid.addComponent(parameters[4], 2, 3);
+		
[…]

### 2016-01-10 poodle_project/webInterface/src/Forms/ProteinConstructParameter.java

@@ -1,0 +1,91 @@
+package Forms;
+
+import com.vaadin.ui.Component;
+import com.vaadin.ui.GridLayout;
+import com.vaadin.ui.Label;
+import com.vaadin.ui.OptionGroup;
+import com.vaadin.ui.TextField;
+import com.vaadin.ui.VerticalLayout;
+
+public class ProteinConstructParameter extends BasicParameters{
+
+	    public ProteinConstructParameter() {
+			title= new Label("Protein Construct Parameter");
+			
+			parameters = new TextField[5];
+			//Search Parameter:
+			parameters[0]   = new TextField("C-Tags");
+			parameters[1]   = new TextField("N-Tags");
+			parameters[2]   = new TextField("Mutation");
+			parameters[3]   = new TextField("protein-family");
+			parameters[4]   = new TextField("vector");			
+			
+			//entry Parameter:
+			entryParameters = new Component[17];
+			
+			entryParameters[0]   = new TextField("C-Tags");
+			entryParameters[1]   = new TextField("N-Tags");
+			entryParameters[2]   = new TextField("Mutation");
+			entryParameters[3]   = new TextField("protein-family");
+			entryParameters[4]   = new TextField("vector");
+			entryParameters[5] = new TextField("protein");
+			entryParameters[6] = new TextField("domain");
+			
+			entryParameters[7] = new TextField("mutation");
+			entryParameters[8] = new TextField("backbone vector");
+			entryParameters[9] = new TextField("antibiotics");
+			
+			entryParameters[10] = new TextField("cloning sites");
+			entryParameters[11] = new OptionGroup("cloning types");
+			
+			entryParameters[12] = new TextField("used primer");
+			entryParameters[13] = new TextField("constructed from vector");
+			
+			entryParameters[14] = new TextField("concentration");
+			entryParameters[15] = new OptionGroup("cell stocks");
+			entryParameters[16] = new TextField("notes");
+			
+			((OptionGroup) entryParameters[15]).addItems("DH5A", "C+");
+			((OptionGroup) entryParameters[11]).addItems("classic", "QC", "RF");
+						
+	        this.changeViewLarge();
+	    }
+	    public void changeToEntryForm(){
+			this.removeAllComponents();
+			GridLayout grid = new GridLayout(4,14);
+			Label label1 = new Label("organisatory");
[…]

### 2016-01-10 poodle_project/webInterface/src/Forms/VectorParameter.java

@@ -1,0 +1,80 @@
+package Forms;
+
+import com.vaadin.ui.*;
+import javax.servlet.annotation.WebServlet;
+
+import com.vaadin.annotations.DesignRoot;
+import com.vaadin.annotations.Theme;
+import com.vaadin.annotations.VaadinServletConfiguration;
+import com.vaadin.server.VaadinRequest;
+import com.vaadin.server.VaadinServlet;
+import com.vaadin.ui.Button.ClickEvent;
+import com.vaadin.ui.declarative.Design;
+
+
+public class VectorParameter extends BasicParameters{
+	    public VectorParameter() {
+			parameters = new TextField[2];
+
+			//Search Parameter:
+			parameters[0]   = new TextField("Tags");
+			parameters[1]   = new TextField("Tev cleavage?");
+
+			
+			//entry Parameter:
+			entryParameters = new Component[17];
+			
+			entryParameters[0]   = new TextField("C-Term-Tags");
+			entryParameters[1]   = new TextField("N-Term-Tags");
+			entryParameters[2]   = new TextField("Construct cleavage?");
+			
+			entryParameters[3]   = new TextField("MCS");
+			entryParameters[4]   = new TextField("antibiotics");
+			
+			entryParameters[5] = new TextField("fw seq primer");
+			entryParameters[6] = new TextField("rv seq primer");
+			
+			entryParameters[7] = new TextField("vector map");
+			entryParameters[8] = new TextField("concentration");
+			entryParameters[9] = new OptionGroup("cell stock");
+			
+			entryParameters[10] = new TextField("notes");
+			
+			((OptionGroup) entryParameters[9]).addItems("DH5A", "C+");
+			
+			title = new Label("Vector Parameters");
+	        this.changeViewLarge();
+	    }
+	    public void changeToEntryForm(){
+			this.removeAllComponents();
+			GridLayout grid = new GridLayout(4,10);
+			Label label1 = new Label("construct specifications");
+			Label label2 = new Label("cloning");
+			Label label3 = new Label("sequencing");
+			Label label4 = new Label("specifications");
+
+			
+			grid.addComponent(label1, 0, 0);
+			grid.addComponent(entryParameters[0], 1, 1);
+			grid.addComponent(entryParameters[1], 2, 1);
+			grid.addComponent(entryParameters[2], 3, 1);	
+			
[…]

### 2016-01-10 poodle_project/webInterface/src/PackageCommunicators/BlastCommunicator.java

@@ -1,0 +1,5 @@
+package PackageCommunicators;
+
+public class BlastCommunicator {
+
+}

### 2016-01-10 poodle_project/webInterface/src/PackageCommunicators/SQLCommunicator.java

@@ -1,0 +1,233 @@
+package PackageCommunicators;
+
+import java.sql.SQLException;
+
+import com.vaadin.data.Container.*;
+import com.vaadin.data.util.filter.Compare.Equal;
+import com.vaadin.data.util.filter.Like;
+import com.vaadin.data.util.sqlcontainer.SQLContainer;
+import com.vaadin.data.util.sqlcontainer.connection.*;
+import com.vaadin.data.util.sqlcontainer.query.TableQuery;
+import com.vaadin.server.VaadinService;
+
+import Forms.GeneralSearchParameter;
+import Forms.PrimerParameter;
+import Forms.ProteinConstructParameter;
+import Forms.VectorParameter;
+
+import org.sqlite.*;
+
+
+public class SQLCommunicator {
+
+	private JDBCConnectionPool pool;
+	private String db;
+	private String table;
+	private TableQuery tq;
+	private SQLContainer container;
+	private SQLContainer primerContainer;
+	private SQLContainer vectorContainer;
+	private SQLContainer proteinContainer;
+
+
+
+	public SQLCommunicator(String db){
+		this.setDb(db);
+		String basepath= VaadinService.getCurrent().getBaseDirectory().getAbsolutePath();
+		String dbPath = "/WEB-INF/db/poodle_sqlite3.dat";
+		try {
+			pool = new SimpleJDBCConnectionPool("org.sqlite.JDBC", "jdbc:sqlite:"+basepath+dbPath, "", "", 2, 5);
+		} catch (SQLException e) {
+			// TODO Auto-generated catch block
+			e.printStackTrace();
+		}
+	}
+
+	public void setTableQuerry(String a){
+		table = a;
+		TableQuery tq1;
+		TableQuery tq2;
+		TableQuery tq3;
+
+		switch(a){
+		case "all":
+			tq1= new TableQuery("Primer", pool);
+			tq1.setVersionColumn("OPTLOCK");
+			try {
+				primerContainer = new SQLContainer(tq1);
+			} catch (SQLException e) {
+				// TODO Auto-generated catch block
+				e.printStackTrace();
+			}
+
+			tq2= new TableQuery("cloningVectors", pool);
+			tq2.setVersionColumn("OPTLOCK");
+			try {
+				vectorContainer = new SQLContainer(tq2);
+			} catch (SQLException e) {
+				// TODO Auto-generated catch block
+				e.printStackTrace();
+			}
+
+			tq3= new TableQuery("proteinConstructs", pool);
[…]

### 2016-01-10 poodle_project/webInterface/src/contentViews/BlastResultView.java

@@ -1,0 +1,5 @@
+package contentViews;
+
+public class BlastResultView {
+
+}

### 2016-01-10 poodle_project/paper/main.tex
BlastSearch is back plus newest version of paper

@@
 	POODLE provides an easy-to-use and powerful interface to improve the work of your lab.\\
-\textbf{Results:} POODLE is a Java-based web interface, which allows you to intuitively access, update and 
-manipulate your data.\\
+\textbf{Results:} POODLE is a Java-based web interface, which allows intuitive access, update and 
+manipulation of data.\\
 \textbf{Contact:} \href{}{forename.surname@student.uni-tuebingen.de}\\
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text. Figure~\ref{fig:01}
-shows that the above method  Text Text Text Text  Text Text Text
-Text Text Text  Text Text.  \citep{Bag01} wants to know about
-{\ldots}{\ldots} text follows.
-\begin{equation}
-\sum \text{\it x}+ \text{\it y} =\text{\it Z}\label{eq:01}\vspace*{-10pt}
-\end{equation}
-
 %\enlargethispage{12pt}
@@
 
-There are a few obvious drawbacks with Excel files.
+As already wrote above many life-science laboratories use Excel files for storing and working with 
+data. But Excel files have a few drawbacks, which make working with them inconvenient. On of the 
+biggest problems occurs, if more than one member of the laboratory tries to access the file at the 
+same time. That can lead to inconsistent files. Second, searching in a Excel file is not as easy as 
+it could be. Furthermore, licenses for Excel are expensive and free software is not as powerful as 
+commercial ones. The reason for using Excel rather than a database system is that most life-scientist 
+are not familiar with database systems and therefor chooses the GUI of Excel to work with. We are 
+facing that problem by combining the functionality of a database system with an intuitive and 
+easy-to-learn handling.
 
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text
-text\vspace*{1pt}
+POODLE is build as a two-layer software. The first layer consists of the database and routines to 
+automatically build and update that database. The second layer consists of the web service that is 
+used to access, update and manipulate data. This is the front end layer and a user only interacts 
+with that layer. One major aspect of POODLE is the in-build BLAST function.
 
-\begin{itemize}
-\item for bulleted list, use itemize
-\item for bulleted list, use itemize
-\item for bulleted list, use itemize\vspace*{1pt}
-\end{itemize}
+\subsection{Database layer}
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text Text Text Text Text Text Text Text Text Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
+SQLite \footnote{http://www.sqlite.org/} is the database system running in the background. We chose 
+this software for several reasons. First, it is free of charge. Second, and more important SQLite is 
+a small and fast database system written in C. So the requirement in space is very low. Since, the 
+whole database is stored just in one file SQLite also has a incredibly good performance. Besides, 
+SQLite guaranties that all transactions are ACID even if a system crash or power failure occurs. So 
+we have a robust storage and access of data as well as a lot of functionality provided by the database 
+system.
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text\vadjust{\newpage}.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text Text Text Text Text Text Text Text Text Text Text.
-\citealp{Boffelli03} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-\subsection{This is subheading}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text
-text. Text Text Text Text Text Text  Text Text Text Text Text Text
-Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-\subsubsection{This is subsubheading}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text\break
-text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text
-textText Text Text Text Text Text  Text Text Text Text Text Text
-Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
+The build and update process is implemented in python. So the user does not have to have knowledge in 
+SQL coding but only has to execute one python script and everything is done automatically.
 
 \enlargethispage{6pt}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-\begin{table}[!t]
-\processtable{This is table caption\label{Tab:01}} {\begin{tabular}{@{}llll@{}}\toprule head1 &
-head2 & head3 & head4\\\midrule
-row1 & row1 & row1 & row1\\
-row2 & row2 & row2 & row2\\
-row3 & row3 & row3 & row3\\
-row4 & row4 & row4 & row4\\\botrule
-\end{tabular}}{This is a footnote}
-\end{table}
 

### 2016-01-10 poodle_project/BlastSearch/RunBlastSearch.java

@@ -1,0 +1,28 @@
+import java.io.*;
+import java.util.*;
+
+public class RunBlastSearch {
+
+  static public void main(String[] args) throws Exception {
+    String mode = args[0];
+    String program = args[1];
+    String sequence = args[2];
+    String database = args[3];
+    String query = args[4];
+    String blastResult = null;
+
+    if (mode.equals("local")) {
+      BlastSearch localBlast = new BlastSearch(sequence, database, program);
+      localBlast.runBlastSearch();
+      blastResult = localBlast.getResult();
+    }else if(mode.equals("NCBI")) {
+      // perform NCBI search
+      NCBIQBlastClass ncbiBlast = new NCBIQBlastClass();
+      //ncbiBlast.runBLASTRequest(program, sequence, database, query);
+      ncbiBlast.runBLASTRequest("blastp", "MKWVTFISLLFLFSSAYSRGVFRRDAHKSEVAHRFKDLGEENFKALVLIAFAQYLQQCP", "swissprot", "\"serum albumin\"[Protein name] AND mammals[Organism]");
+      blastResult = ncbiBlast.getResult();
+    }
+    
+    System.out.println(blastResult);
+  }
+}

### 2016-01-10 poodle_project/paper/main.tex
kleinere verädnerung bei BlastSearch

@@
 
-%\enlargethispage{12pt}
+\enlargethispage{12pt}
 
@@
 we have a robust storage and access of data as well as a lot of functionality provided by the database 
-system.
+system. In addition to the SQLite database POODLE's software creates a BLAST database for the provided 
+data, too. That database is needed for the BLAST function that comes with POODLE.
 
 The build and update process is implemented in python. So the user does not have to have knowledge in 
-SQL coding but only has to execute one python script and everything is done automatically.
+SQL coding but only has to execute one python script and everything is done automatically. This routine 
+ensures that the SQLite database and the BLAST database are always in the same state.
 
-\enlargethispage{6pt}
+\subsection{Web service}
+
+POODLE web service is build with Vaadin \footnote{https://vaadin.com/home}. This allows a safe 
+communication between the front end and the database layer as well as a smooth and easy handling of 
+the side.
 

### 2016-01-10 poodle_project/webInterface/BlastPackage/BlastSearch.java

@@ -103,7 +103,7 @@ public class BlastSearch {
     try {
       // set up Runtime
       Runtime rt = Runtime.getRuntime();
-      String execString = this.blastProgram + " -query " + queryFile + " -db " + this.blastDB + " -task " + this.task + " -outfmt 5";
+      String execString = this.blastProgram + " -query " + queryFile + " -db " + this.blastDB + " -task " + this.task + " -outfmt 13";
       System.out.println("Running " + execString + " ...");
       Process pr = rt.exec(execString);
       

### 2016-01-10 poodle_project/paper/main.tex
neue ncbi binaries ... und alle so yeah!

@@
 
-\title[POODLE]{POODLE - To the core of your data}
+\title[POODLE]{POODLE 1.0 - To the core of your data}
 \author[Ditz, Schroeder]{Jonas Ditz\,$^{\text{\sfb 1,}*}$ and Benjamin Schroeder\,$^{\text{\sfb 1,}*}$} 
@@
 automatically build and update that database. The second layer consists of the web service that is 
-used to access, update and manipulate data. This is the front end layer and a user only interacts 
-with that layer. One major aspect of POODLE is the in-build BLAST function.
+used to access, update and manipulate data. This is the front end layer and provides access to all 
+functions for the user. Because POODLE is not just a data storage software but also comes with useful 
+methods like a Blast search.
 
@@
 system. In addition to the SQLite database POODLE's software creates a BLAST database for the provided 
-data, too. That database is needed for the BLAST function that comes with POODLE.
+data, too.
 
-The build and update process is implemented in python. So the user does not have to have knowledge in 
+The build and update process is implemented in Python. So the user does not have to have knowledge in 
 SQL coding but only has to execute one python script and everything is done automatically. This routine 
-ensures that the SQLite database and the BLAST database are always in the same state.
+ensures that the SQLite database and the BLAST database are always in the same state. It also makes 
+the database a little bit safer, since changes can be reviewed before iserting them into the database.
 
@@
 communication between the front end and the database layer as well as a smooth and easy handling of 
-the side.
+the side. Since a website developed with Vaadin is highly modular, it is easy to extend the web 
+service in the future. That could be necessary, if new functionalities are required. Currently, 
+there are three pages with different roles. The search page provides a formula that can be used 
+to perform a simple SQL search in the local database. Therefor, different files are displayed and 
+can be filled by the user. A click on the search button will automatically build a SQL query and 
+results are displayed, if there are available results. The new entry page allows to insert a new 
+entry into the database. It also provide a Blast search against the NCBI databases to check, whether 
+there are available information about the current sequence or not. Last but not least, users can 
+perform a local Blast search against their one database or a remote Blast search against the NCBI 
+databases on the Blast page.
+
+\subsection{Blast functionality}
+
+Our software package provides not just a database functionality for powerful and secure data storage 
+and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This functionality 
+is implemented by a combination of Blast binaries provided by NCBI and the Biojava Api 
+(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
+is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search.
 
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
-\subsection{Test1}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
-
 \section{Discussion}
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
+\citealp{Bag01} might want to know about  text text text text
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
+\citealp{Bag01} might want to know about  text text text text
 Text Text Text Text Text Text Text Text Text Text.
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
+\citealp{Bag01} might want to know about  text text text text
 Text Text Text Text Text Text Text Text Text Text Text Text Text
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about  text text text text
+\citealp{Bag01} might want to know about  text text text text
 
@@
 above method  Text Text Text Text Text Text Text Text Text Text
-Text Text.  \citealp{Boffelli03} might want to know about text
+Text Text.  \citealp{Bag01} might want to know about text
 text text text Text Text Text Text Text Text  Text Text Text Text
@@
 Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Boffelli03} might want to know about text text text text
+\citealp{Bag01} might want to know about text text text text
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
@@
 
-Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text
+Text Text Text Text Text Text  Text Text.  \citealp{Bag01} might want to know about  text
 text text text\vspace*{-12pt}
@@
 
-This work has been supported by the... Text Text  Text Text.\vspace*{-12pt}
+This work has been supported by ... nobody. Seriously, not anybody. We know that is sad but it is hard 
+to convince people giving their money away.
 
@@
 
-\bibitem[Bofelli {\it et~al}., 2000]{Boffelli03}
-Bofelli,F., Name2, Name3 (2003) Article title, {\it Journal Name}, {\bf 199}, 133-154.
+\bibitem[Altschul {\it et~al}., 1990]{Altschul01}
+Altschul, S.F., Gish, W., Miller, W., Myers, E.W., Lipman, D.J. (1990) Basic local alignment search tool., {\it J. Mol. Biol.}, {\bf 215}, 403-410.
+
+\bibitem[Prli\'{c} {\it et~al}., 2012]{Prlic01}
+Prli\'{c}, A., Yates, A., Bliven, S.
+E., Rose, P.
+W., Jacobsen, J., Troshin, P.
+V., ...
+Willis, S.
+(2012) BioJava: an open-source framework for bioinformatics in 2012.
+{\it Bioinformatics}, {\bf 28(20)}, 2693-2695.
+http://doi.org/10.1093/bioinformatics/bts494
 

### 2016-01-10 poodle_project/paper/main.tex
hoffe jetzt passt alles

@@
 
-SQLite \footnote{http://www.sqlite.org/} is the database system running in the background. We chose 
+SQLite\footnote{http://www.sqlite.org/} is the database system running in the background. We chose 
 this software for several reasons. First, it is free of charge. Second, and more important SQLite is 
@@
 
-POODLE web service is build with Vaadin \footnote{https://vaadin.com/home}. This allows a safe 
+POODLE web service is build with Vaadin\footnote{https://vaadin.com/home}. This allows a safe 
 communication between the front end and the database layer as well as a smooth and easy handling of 
@@
 is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search. 
+The remote Blast search is not a fully functional copy of the NCBI web service but can used to 
+perform a quick and simply search against NCBI databases, e.g. Swissprot (\citealp{Doni01}). But we do not recommend to 
+overuse that because too many requests may cause a blacklisting by NCBI.
 
@@
 (2012) BioJava: an open-source framework for bioinformatics in 2012.
-{\it Bioinformatics}, {\bf 28(20)}, 2693-2695.
+{\it Bioinformatics}, {\bf 28}(20), 2693-2695.
 http://doi.org/10.1093/bioinformatics/bts494
+
+\bibitem[O'Donavan {\it et~al}., 2002]{Doni01}
+O'Donovan, C., Martin, M.J., Gattiker, A., Gasteiger, E., Bairoch, A., Apweiler, R.
+(2002) High-quality protein knowledge resource: SWISS-PROT and TrEMBL {\it Brief.
+Bioinform.}  {\bf 3} (3), 275-284.
+doi: 10.1093/bib/3.3.275
 

### 2016-01-11 poodle_project/paper/main.tex

@@
 ensures that the SQLite database and the BLAST database are always in the same state. It also makes 
-the database a little bit safer, since changes can be reviewed before iserting them into the database.
+the database a little bit safer, since changes can be reviewed before inserting them into the database.
 
@@
 The remote Blast search is not a fully functional copy of the NCBI web service but can used to 
-perform a quick and simply search against NCBI databases, e.g. Swissprot (\citealp{Doni01}). But we do not recommend to 
-overuse that because too many requests may cause a blacklisting by NCBI.
+perform a quick and simply search against databases provided by NCBI, e.g. Swissprot (\citealp{Doni01}). But we 
+do not recommend to overuse that because too many requests may cause a blacklisting by NCBI. This 
+remote Blast routine is mainly for the insertion of a new entry. The idea is to check whether there 
+are information about the new sequence. The local Blast routine does everything someone would 
+expect from a Blast search but against the local database, hence local Blast.
 
@@
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text.
-
-Table~\ref{Tab:01} shows that Text Text Text Text Text  Text Text
-Text Text Text Text. Figure~2\vphantom{\ref{fig:02}} shows that
-the above method Text Text. Text Text Text  Text Text Text Text
-Text Text. Figure~2\vphantom{\ref{fig:02}} shows that the above
-method Text Text. Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method Text
-Text.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%     please remove the " % " symbol from \centerline{\includegraphics{fig01.eps}}
-%     as it may ignore the figures.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusion}
 
-(Table~\ref{Tab:01}) Text Text Text Text Text Text  Text Text Text
-Text Text Text Text Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
-
-\begin{enumerate}
-\item this is item, use enumerate
-\item this is item, use enumerate
-\item this is item, use enumerate
-\end{enumerate}
-
-Text Text Text Text Text Text Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows\vadjust{\pagebreak} that the
-above method  Text Text Text Text Text Text Text Text Text Text
-Text Text.  \citealp{Bag01} might want to know about text
-text text text Text Text Text Text Text Text  Text Text Text Text
-Text Text Text Text Text Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text Text Text Text Text Text\break Text.
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text
-Text Text  Text Text Text Text Text Text.
-Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
-Text Text Text\vspace*{-10pt}
-
 \section*{Acknowledgements}
-
-Text Text Text Text Text Text  Text Text.  \citealp{Bag01} might want to know about  text
-text text text\vspace*{-12pt}
 

### 2016-01-11 poodle_project/paper/main.tex
paper topics

--- 2016-01-10 poodle_project/paper/main.tex
@@
 
-\title[POODLE]{POODLE 1.0 - To the core of your data}
+\title[POODLE]{POODLE - To the core of your data}
 \author[Ditz, Schroeder]{Jonas Ditz\,$^{\text{\sfb 1,}*}$ and Benjamin Schroeder\,$^{\text{\sfb 1,}*}$} 
@@
 
+\subsection{A real world pipeline}
+function study
+\subsection{cloning as lab strategy}
+Toolkit idea
+\subsection{cloning methods}
+Classsic Cloning, Quickchange, Restriction free cloning
+
+\subsection{The resulting data}
+primer
+cloningVectors
+proteinConstructs
+
 \enlargethispage{12pt}
@@
 automatically build and update that database. The second layer consists of the web service that is 
-used to access, update and manipulate data. This is the front end layer and provides access to all 
-functions for the user. Because POODLE is not just a data storage software but also comes with useful 
-methods like a Blast search.
+used to access, update and manipulate data. This is the front end layer and a user only interacts 
+with that layer. One major aspect of POODLE is the in-build BLAST function.
 
@@
 system. In addition to the SQLite database POODLE's software creates a BLAST database for the provided 
-data, too.
+data, too. That database is needed for the BLAST function that comes with POODLE.
 
-The build and update process is implemented in Python. So the user does not have to have knowledge in 
+The build and update process is implemented in python. So the user does not have to have knowledge in 
 SQL coding but only has to execute one python script and everything is done automatically. This routine 
-ensures that the SQLite database and the BLAST database are always in the same state. It also makes 
-the database a little bit safer, since changes can be reviewed before iserting them into the database.
+ensures that the SQLite database and the BLAST database are always in the same state.
 
@@
 communication between the front end and the database layer as well as a smooth and easy handling of 
-the side. Since a website developed with Vaadin is highly modular, it is easy to extend the web 
-service in the future. That could be necessary, if new functionalities are required. Currently, 
-there are three pages with different roles. The search page provides a formula that can be used 
-to perform a simple SQL search in the local database. Therefor, different files are displayed and 
-can be filled by the user. A click on the search button will automatically build a SQL query and 
-results are displayed, if there are available results. The new entry page allows to insert a new 
-entry into the database. It also provide a Blast search against the NCBI databases to check, whether 
-there are available information about the current sequence or not. Last but not least, users can 
-perform a local Blast search against their one database or a remote Blast search against the NCBI 
-databases on the Blast page.
-
-\subsection{Blast functionality}
-
-Our software package provides not just a database functionality for powerful and secure data storage 
-and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This functionality 
-is implemented by a combination of Blast binaries provided by NCBI and the Biojava Api 
-(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
-is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search.
+the side.
 
@@
 
+Text Text Text Text Text Text  Text Text Text Text Text Text Text
+Text Text  Text Text Text Text Text Text.
+Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
+Text Text Text  Text Text Text Text Text Text  Text Text.
+\citealp{Boffelli03} might want to know about  text text text text
+Text Text Text Text Text Text  Text Text Text Text Text Text Text
+Text Text  Text Text Text Text Text Text.
+Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
+Text Text Text  Text Text Text Text Text Text  Text Text.
+\citealp{Boffelli03} might want to know about  text text text text
+Text Text Text Text Text Text Text Text Text Text Text Text Text
+Text Text  Text Text Text Text Text Text.
+Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
+Text Text Text  Text Text Text Text Text Text  Text Text.
+\citealp{Boffelli03} might want to know about  text text text text
+
+\subsection{Test1}
+
+Text Text Text Text Text Text  Text Text Text Text Text Text Text
+Text Text  Text Text Text Text Text Text.
+Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
+Text Text Text  Text Text Text Text Text Text  Text Text.
+\citealp{Boffelli03} might want to know about  text text text text
+Text Text Text Text Text Text  Text Text Text Text Text Text Text
+Text Text  Text Text Text Text Text Text.
+Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
+Text Text Text  Text Text Text Text Text Text  Text Text.
+\citealp{Boffelli03} might want to know about  text text text text
+Text Text Text Text Text Text Text Text Text Text Text Text Text
+Text Text  Text Text Text Text Text Text.
+Figure~2\vphantom{\ref{fig:02}} shows that the above method  Text
+Text Text Text  Text Text Text Text Text Text  Text Text.
+\citealp{Boffelli03} might want to know about  text text text text
+
 \section{Discussion}
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
+\citealp{Boffelli03} might want to know about  text text text text
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
+\citealp{Boffelli03} might want to know about  text text text text
 Text Text Text Text Text Text Text Text Text Text.
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
+\citealp{Boffelli03} might want to know about  text text text text
 Text Text Text Text Text Text Text Text Text Text Text Text Text
@@
 Text Text Text  Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about  text text text text
+\citealp{Boffelli03} might want to know about  text text text text
 
@@
 above method  Text Text Text Text Text Text Text Text Text Text
-Text Text.  \citealp{Bag01} might want to know about text
+Text Text.  \citealp{Boffelli03} might want to know about text
 text text text Text Text Text Text Text Text  Text Text Text Text
@@
 Text Text Text Text Text Text Text Text Text  Text Text.
-\citealp{Bag01} might want to know about text text text text
+\citealp{Boffelli03} might want to know about text text text text
 Text Text Text Text Text Text  Text Text Text Text Text Text Text
@@
 
-Text Text Text Text Text Text  Text Text.  \citealp{Bag01} might want to know about  text
+Text Text Text Text Text Text  Text Text.  \citealp{Boffelli03} might want to know about  text
 text text text\vspace*{-12pt}
@@
 
-This work has been supported by ... nobody. Seriously, not anybody. We know that is sad but it is hard 
-to convince people giving their money away.
+This work has been supported by the... Text Text  Text Text.\vspace*{-12pt}
 
@@
 
-\bibitem[Altschul {\it et~al}., 1990]{Altschul01}
-Altschul, S.F., Gish, W., Miller, W., Myers, E.W., Lipman, D.J. (1990) Basic local alignment search tool., {\it J. Mol. Biol.}, {\bf 215}, 403-410.
-
-\bibitem[Prli\'{c} {\it et~al}., 2012]{Prlic01}
-Prli\'{c}, A., Yates, A., Bliven, S.
-E., Rose, P.
-W., Jacobsen, J., Troshin, P.
-V., ...
-Willis, S.
-(2012) BioJava: an open-source framework for bioinformatics in 2012.
-{\it Bioinformatics}, {\bf 28(20)}, 2693-2695.
-http://doi.org/10.1093/bioinformatics/bts494
+\bibitem[Bofelli {\it et~al}., 2000]{Boffelli03}
+Bofelli,F., Name2, Name3 (2003) Article title, {\it Journal Name}, {\bf 199}, 133-154.
 

### 2016-01-11 poodle_project/webInterface/src/Forms/BasicParameters.java
added autoID, blastLoading

@@ -1,5 +1,6 @@
 package Forms;
 
+import com.vaadin.server.UserError;
 import com.vaadin.ui.Component;
 import com.vaadin.ui.GridLayout;
 import com.vaadin.ui.Label;
@@ -34,7 +35,7 @@ public abstract class BasicParameters extends VerticalLayout {
 				j++;
 			}
 			parameters[i].setWidth("175px");
-//			parameters[i].setHeight("25px");
+			//			parameters[i].setHeight("25px");
 			grid.addComponent(parameters[i], j, i%3);
 		}
 		this.addComponent(grid);
@@ -44,7 +45,7 @@ public abstract class BasicParameters extends VerticalLayout {
 		this.removeAllComponents();
 
 		grid = new GridLayout(2,4);
-		
+
 		int j=-1;
 		for(int i=0; i<parameters.length; i++){
 			if(i%4==0){
@@ -53,15 +54,15 @@ public abstract class BasicParameters extends VerticalLayout {
 			grid.addComponent(parameters[i], j, i%4);
 		}
 		grid.setSpacing(true);
-		
+
 		this.addComponent(title);
 		this.addComponent(grid);
 	}
-	
+
 	public void changeToEntryForm(){
 		this.removeAllComponents();
 	}
-	
+
 	public String getParameter(int x){
 		return  parameters[x].getValue();
 	}
@@ -78,7 +79,43 @@ public abstract class BasicParameters extends VerticalLayout {
 			parameters[i].setValue("");
 		}
 	}
-	public void evaluate() throws Exception {
-		throw new Exception("No Validation is available!");	
+	public boolean evaluate(boolean focus) throws Exception {
+		boolean focused =focus;
+		for(int i=0; i< entryParameters.length; i++){
+			if((entryParameters[i] instanceof TextField)){
+				if(((TextField) entryParameters[i]).getValue().equals("") || ((TextField) entryParameters[i]).getValue().equals(null) || ((TextField) entryParameters[i]).getValue().equals("")){
+					((TextField) entryParameters[i]).setComponentError(new UserError("This Field is required!"));
+					if(!focused){
+						focused=true;
+						((TextField) entryParameters[i]).focus();
+					}
+				}
+				else{
+					if((((TextField) entryParameters[i]).isValid())){
+						((TextField) entryParameters[i]).setComponentError(null);
+						continue;
+					}
+					else{
+						((TextField) entryParameters[i]).setConversionError("OH OH");	
[…]

### 2016-01-11 poodle_project/webInterface/src/Forms/GeneralSearchParameter.java

@@ -39,26 +39,24 @@ public class GeneralSearchParameter extends BasicParameters{
 		parameters[6] = new TextField("protein");
 
 		//Parameters for a New Entry
-		entryParameters[0] = new TextField("Id");
-		entryParameters[1] = new TextField("box");
-		entryParameters[2] = new TextField("position");
-		entryParameters[3] = new TextField("name");
-		entryParameters[4] = new TextField("author");
+		
+		entryParameters[0] = new TextField("name");
+		entryParameters[1] = new TextField("author");
 		date = new DateField("date");
+				
+		entryParameters[2] = new TextField("Id");
+		entryParameters[3] = new TextField("box");
+		entryParameters[4] = new TextField("position");
 
 
-		
 		// some adjustification for parameter fields:
-		this.fillID();
-		entryParameters[0].setEnabled(false);
-		
-		((TextField) entryParameters[1]).setNullSettingAllowed(false);
-		
+		entryParameters[2].isReadOnly();
+
 		date.setValue(new java.util.Date());
 		date.setImmediate(true);
 		date.setValidationVisible(true);
 
-		
+
 		this.changeViewLarge();         
 	}
 
@@ -67,32 +65,32 @@ public class GeneralSearchParameter extends BasicParameters{
 		GridLayout grid = new GridLayout(4,4);
 		grid.setSpacing(true);
 		grid.setWidth(90, Unit.PERCENTAGE);
-		
+
 		Label label1 = new Label("General");
 		Label label2 = new Label("Location");
 
 		grid.addComponent(label1, 0, 0);
-		grid.addComponent(entryParameters[3], 1,1);
+		grid.addComponent(entryParameters[0], 1,1);
 		grid.addComponent(date, 2,1);
-		grid.addComponent(entryParameters[4], 3,1);
+		grid.addComponent(entryParameters[1], 3,1);
 
 		grid.addComponent(label2, 1,2);
-		grid.addComponent(entryParameters[0], 1,3);
-		grid.addComponent(entryParameters[1], 2,3);
-		grid.addComponent(entryParameters[2], 3,3);
+		grid.addComponent(entryParameters[2], 1,3);
+		grid.addComponent(entryParameters[3], 2,3);
+		grid.addComponent(entryParameters[4], 3,3);
 
 		this.addComponent(grid);
 	}
 
-	private void fillID() {
-		((TextField) entryParameters[0]).setValue("xxx");
-	}
-
-	public void evaluate() throws Exception {
[…]

### 2016-01-11 poodle_project/webInterface/src/Forms/PrimerParameter.java

@@ -1,5 +1,6 @@
 package Forms;
 
+import com.vaadin.server.UserError;
 import com.vaadin.server.Sizeable.Unit;
 import com.vaadin.ui.Alignment;
 import com.vaadin.ui.Component;
@@ -62,13 +63,13 @@ public class PrimerParameter extends BasicParameters{
 		Label label6 = new Label("rest");
 		
 		grid.addComponent(label1, 0, 0);
-		grid.addComponent(parameters[0], 1, 1);
-		grid.addComponent(parameters[1], 2, 1);
-		grid.addComponent(parameters[2], 3, 1);
+		grid.addComponent(entryParameters[0], 1, 1);
+		grid.addComponent(entryParameters[1], 2, 1);
+		grid.addComponent(entryParameters[2], 3, 1);
 		
 		grid.addComponent(label2, 0, 2);
-		grid.addComponent(parameters[3], 1, 3);
-		grid.addComponent(parameters[4], 2, 3);
+		grid.addComponent(entryParameters[3], 1, 3);
+		grid.addComponent(entryParameters[4], 2, 3);
 		
 		grid.addComponent(label3, 0, 4);
 		grid.addComponent(entryParameters[5], 1, 5);

### 2016-01-11 poodle_project/webInterface/src/contentViews/BlastView.java

@@ -8,6 +8,7 @@ import com.vaadin.ui.GridLayout;
 import com.vaadin.ui.HorizontalLayout;
 import com.vaadin.ui.Label;
 import com.vaadin.ui.NativeSelect;
+import com.vaadin.ui.ProgressBar;
 import com.vaadin.ui.TextArea;
 import com.vaadin.ui.TextField;
 import com.vaadin.ui.VerticalLayout;
@@ -15,6 +16,7 @@ import com.vaadin.ui.VerticalLayout;
 import BlastClasses.BlastSearch;
 
 import com.vaadin.ui.Button.ClickEvent;
+import com.vaadin.ui.Component;
 
 import Forms.BlastSeqField;
 import Forms.GeneralSearchParameter;
@@ -27,6 +29,8 @@ public class BlastView extends VerticalLayout {
 	private BlastSeqField seq;
 	private Button blast;
 	private PoodledbUI poodleUI;
+	private ProgressBar loadBar;
+	private Label working;
 
 	public BlastView(PoodledbUI pooldeUI, BlastBar blastBar){
 		//initialization
@@ -47,28 +51,49 @@ public class BlastView extends VerticalLayout {
 		//LAyout
 		//function:
 		blast.addClickListener(new Button.ClickListener() {
+
 			public void buttonClick(ClickEvent event) {
 				try{
+					
 					String querry= seq.evaluateSequence();
-					Label working = new Label ("still working on");
-					BlastCommunicator blast = new BlastCommunicator(blastBar.getMode(),blastBar.getProgram(), querry, blastBar.getDB(), blastBar.getDBTable(), blastBar.getQuerry());
+					
+					getBlastView().removeComponent(blast);
+					loadBar = new ProgressBar();
+					loadBar.setIndeterminate(true);
+					addComponent(loadBar);
+					
+					working = new Label ("Loading");
+					working.addStyleName("center");
 					addComponent(working);
+					
+					BlastCommunicator blastC = new BlastCommunicator(blastBar.getMode(),blastBar.getProgram(), querry, blastBar.getDB(), blastBar.getDBTable(), blastBar.getQuerry());
+					
 					try{
-						
 					}catch(Exception e){
 						System.out.println("System-Error"+e);
 					}
 				}catch(Exception e){
 					System.out.println("User-Error"+e);
+					getBlastView().refresh();
 				}
 			}
 		});
 
-		addComponent(title);
-		addComponent(blastBar);
[…]

### 2016-01-11 poodle_project/webInterface/src/pageElements/ServerTableSelection.java

@@ -127,6 +127,12 @@ public class ServerTableSelection extends HorizontalLayout{
 				newEntry.modifyToProteinParamAdvanced();
 				break;
 			}
+	    	try {
+				poodledb.getNewEntryView().setAutomaticID();
+			} catch (Exception e) {
+				System.out.println("The ID finding process failed: "+e);
+				e.printStackTrace();
+			}
 		}
 	}
 }

### 2016-01-11 poodle_project/webInterface/WebContent/WEB-INF/db/buildDatabase.py
primary keys sind jetzt integers

@@ -13,6 +13,10 @@ DATA_PATH = '../data/'
 
 GROUP1 = 'Wiesner/'
 
+# type of the Blast database
+BLAST_TYPE_NUCL = 'nucl'
+BLAST_TYPE_PROT = 'prot'
+
 #
 #---------------------------------------------------------------------------------------------------------------------
 #
@@ -22,7 +26,7 @@ def createProtConTable(db):
     # drop table if exists
     db.execute('drop table if exists proteinConstructs')
     # create table proteinConstructs
-    db.execute('CREATE table proteinConstructs (id Primary Key,box,position,protein,domain,protein_family,mutation,backbone_vector,antibiotics,cloning_sites,QC,RF,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,project,date,author,notes)')
+    db.execute('CREATE table proteinConstructs (id Integer Primary Key,box,position,protein,domain,protein_family,mutation,backbone_vector,antibiotics,cloning_sites,QC,RF,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,project,date,author,notes)')
     values = []
     protConFile = open(DATA_PATH + 'protein_constructs/protein_constructs.csv','r')
     for line in protConFile.readlines():
@@ -43,7 +47,7 @@ def createClonVecTable(db):
     # drop table, if it already exists
     db.execute('drop table if exists cloningVectors')
     # create table cloningVectors
-    db.execute('create table cloningVectors (id Primary Key,box,position,name,size,C_Term_Tags,N_Term_Tags,construct_cleavable,MCS,antibiotics,fw_seq_primer,rv_seq_primer,vector_map,concentration,DH5A_stock,date,author,notes)')
+    db.execute('create table cloningVectors (id Integer Primary Key,box,position,name,size,C_Term_Tags,N_Term_Tags,construct_cleavable,MCS,antibiotics,fw_seq_primer,rv_seq_primer,vector_map,concentration,DH5A_stock,date,author,notes)')
     values = []
     clonVecFile = open(DATA_PATH + 'cloning_vectors/cloning_vectors.csv', 'r')
     for line in clonVecFile.readlines():
@@ -64,7 +68,7 @@ def createPrimTable(db):
     # drop table, if already exists
     db.execute('drop table if exists primer')
     # create table primer
[…]

### 2016-01-11 poodle_project/paper/main.tex

--- 2016-01-11 poodle_project/paper/main.tex
@@
 	This leads to a huge workload for maintenance as well as a inconvenient access and update routine. 
-	POODLE provides an easy-to-use and powerful interface to improve the work of your lab.\\
+	POODLE provides an easy-to-use and powerful interface to improve the cloning work of your lab.\\
 \textbf{Results:} POODLE is a Java-based web interface, which allows intuitive access, update and 
-manipulation of data.\\
+manipulation of data for cloning.\\
 \textbf{Contact:} \href{}{forename.surname@student.uni-tuebingen.de}\\
-\textbf{Supplementary information:} Supplementary data are available at \textit{https://github.com/derjedi/BioinformaticsI\-Assigments/tree/master/poodle\_project}
+\textbf{Supplementary information:} Supplementary data and the code are available at \textit{https://github.com/derjedi/BioinformaticsI\-Assigments/tree/master/poodle\_project}
 online.}
@@
 \enlargethispage{12pt}
+
+\subsection{A real world pipeline}
+function study
+\subsection{cloning as lab strategy}
+Toolkit idea
+\subsection{cloning methods}
+Classsic Cloning, Quickchange, Restriction free cloning
+
+\subsection{The resulting data}
+primer
+cloningVectors
+proteinConstructs
 
@@
 a small and fast database system written in C. So the requirement in space is very low. Since, the 
-whole database is stored just in one file SQLite also has a incredibly good performance. Besides, 
+whole database is stored just in one file SQLite also has a incredibly good performance. And there 
+is the possibility to create a mobile version of POODLE without changing the whole database system, 
+which may be interesting in the future. Besides, 
 SQLite guaranties that all transactions are ACID even if a system crash or power failure occurs. So 
@@
 
-POODLE web service is build with Vaadin\footnote{https://vaadin.com/home}. This allows a safe 
+POODLE web service is build with Vaadin\footnote{https://vaadin.com/home}. We chose that framework 
+because it allows a safe 
 communication between the front end and the database layer as well as a smooth and easy handling of 
@@
 there are three pages with different roles. The search page provides a formula that can be used 
-to perform a simple SQL search in the local database. Therefor, different files are displayed and 
+to perform a simple SQL search in the local database. Therefor, different fields are displayed and 
 can be filled by the user. A click on the search button will automatically build a SQL query and 
@@
 entry into the database. It also provide a Blast search against the NCBI databases to check, whether 
-there are available information about the current sequence or not. Last but not least, users can 
+there are already available information about the new sequence or not. Last but not least, users can 
 perform a local Blast search against their one database or a remote Blast search against the NCBI 
-databases on the Blast page.
+databases on the Blast page. That functionality can be found on the Blast page.
 
@@
 Our software package provides not just a database functionality for powerful and secure data storage 
-and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This functionality 
-is implemented by a combination of Blast binaries provided by NCBI and the Biojava Api 
+and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This function 
+is implemented by using a combination of Blast binaries provided by NCBI and the Biojava Api 
 (\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
@@
 remote Blast routine is mainly for the insertion of a new entry. The idea is to check whether there 
-are information about the new sequence. The local Blast routine does everything someone would 
-expect from a Blast search but against the local database, hence local Blast.
+are information about the new sequence. But it can also used separated from the new entry routine. 
+The local Blast routine does everything someone would 
+expect from a Blast search but against the local database, hence local Blast. There a several programs, 
+e.g. blastn or blastp, available for both Blast methods.
 
@@
 
+POODLE is completely open-source. So the user can adapt the code at any point of the software. To make 
+this adaption as easy as possible for the user we chose to use widely known software inside of POODLE. 
+Most scientist have heard of SQL as a database managment system. So it is not to dangerous to assume 
+that there are people with basic SQL knowledge in most of the laboratories. And that means these 
+laboratories do not have to use POODLE as a black box. We chose SQLite over all other SQL databases 
+for the reasons described in the method section.
+
+The build up process of the database is written in Python. There are two reasons for that. First, 
+Python is a easy and powerful language which makes it possible for the user to adapt the build up 
+process without detailed programming knowledge. And second there is almost no 
+Server without a Python2.7 or higher environment.
+
+Vaadin was chose as the framework to be for several reasons. Java is a widely used programming language 
+in the scientific world. So there is a relative high chance for a person in the laboratory, who speaks 
+Java. Again we want to make adaption as easy as possible for the user. Furthermore, Vaadin needs a 
+tomcat server. Such a server is provided free of charge by Apache\footnote{http://www.apache.org/}. 
+So the user does not have to face extra charges just to be able to use POODLE. More reasons for 
+Vaadin are discussed in the method section.
+
 \section{Conclusion}
 
+POODLE provides a secure storage of cloning data as well as a easy-to-use interface for 
+interacting with these data. Besides, it comes with functionalities like local and remote Blast 
+search that can improve the workflow during cloning.
+
+It is our goal to improve the software in the future by adding new functionalities like a chromatogram 
+viewer and the possibility to add annotations to sequences.
+
 \section*{Acknowledgements}
+
+We would like to thank Silke Wiesner and her group at the Max-Plack-Institute for Developmental Biology 
+in T\"{u}bingen for providing us with real-world data and fruitful discussions.
 
@@
 
-\bibitem[Bag {\it et~al}., 2001]{Bag01}
-Bag,M., Name2, Name3 (2001) Article title, {\it Journal Name}, {\bf 99}, 33-54.
-
-\bibitem[Yoo \textit{et~al}., 2003]{Yoo03}
-Yoo,M.S. \textit{et~al}. (2003) Oxidative stress regulated genes
-in nigral dopaminergic neurnol cell: correlation with the known
-pathology in Parkinson's disease. \textit{Brain Res. Mol. Brain
-Res.}, \textbf{110}(Suppl. 1), 76--84.
-
-\bibitem[Lehmann, 1986]{Leh86}
-Lehmann,E.L. (1986) Chapter title. \textit{Book Title}. Vol.~1, 2nd edn. Springer-Verlag, New York.
-
-\bibitem[Crenshaw and Jones, 2003]{Cre03}
-Crenshaw, B.,III, and Jones, W.B.,Jr (2003) The future of clinical
-cancer management: one tumor, one chip. \textit{Bioinformatics},
-doi:10.1093/bioinformatics/btn000.
-
-\bibitem[Auhtor \textit{et~al}. (2000)]{Aut00}
-Auhtor,A.B. \textit{et~al}. (2000) Chapter title. In Smith, A.C.
-(ed.), \textit{Book Title}, 2nd edn. Publisher, Location, Vol. 1, pp.
-???--???.
-
-\bibitem[Bardet, 1920]{Bar20}
-Bardet, G. (1920) Sur un syndrome d'obesite infantile avec
-polydactylie et retinite pigmentaire (contribution a l'etude des
-formes cliniques de l'obesite hypophysaire). PhD Thesis, name of
-institution, Paris, France.
-
 \end{thebibliography}

### 2016-01-12 poodle_project/paper/main.tex
verbesserungen von alex und das logo sind ins paper eingebaut

@@
 \abstract{\textbf{Motivation:} Many life science laboratories are still using Excel files do organize their data. 
-	This leads to a huge workload for maintenance as well as a inconvenient access and update routine. 
+	This leads to a huge workload for maintenance as well as an inconvenient access and update routine. 
 	POODLE provides an easy-to-use and powerful interface to improve the cloning work of your lab.\\
@@
 
-As already wrote above many life-science laboratories use Excel files for storing and working with 
-data. But Excel files have a few drawbacks, which make working with them inconvenient. On of the 
+As already mentioned above many life-science laboratories use Excel files for storing and working with 
+data. But Excel files have a few drawbacks, which make working with them inconvenient. One of the 
 biggest problems occurs, if more than one member of the laboratory tries to access the file at the 
-same time. That can lead to inconsistent files. Second, searching in a Excel file is not as easy as 
-it could be. Furthermore, licenses for Excel are expensive and free software is not as powerful as 
-commercial ones. The reason for using Excel rather than a database system is that most life-scientist 
-are not familiar with database systems and therefor chooses the GUI of Excel to work with. We are 
-facing that problem by combining the functionality of a database system with an intuitive and 
+same time. Inconsistent files can be the result of a simultaneous access. Second, searching in a Excel file is not as easy as 
+it could be. Furthermore, licenses for Excel are expensive and switching to a free software solution 
+saves a lot of money. The reason for using Excel rather than a database system is that most life-scientist 
+are not familiar with database systems and prefer the GUI of Excel to work with. We are 
+trying to solve that problem by combining the functionality of a database system with an intuitive and 
 easy-to-learn handling.
@@
 used to access, update and manipulate data. This is the front end layer and provides access to all 
-functions for the user. Because POODLE is not just a data storage software but also comes with useful 
-methods like a Blast search.
+functions for the user, such as accessing the database, manipulating data and using the in-build 
+Blast functionality.
 
@@
 this software for several reasons. First, it is free of charge. Second, and more important SQLite is 
-a small and fast database system written in C. So the requirement in space is very low. Since, the 
-whole database is stored just in one file SQLite also has a incredibly good performance. And there 
+a small and fast database system written in C. Since, the whole database is stored just in one file
+SQLite has a incredibly good performance combined with a really small among of required space. And there 
 is the possibility to create a mobile version of POODLE without changing the whole database system, 
 which may be interesting in the future. Besides, 
-SQLite guaranties that all transactions are ACID even if a system crash or power failure occurs. So 
+SQLite guaranties that transactions have all ACID (Atomicity, Consistency, Isolation and Durability) properties even if a system crash or power failure occurs. So 
 we have a robust storage and access of data as well as a lot of functionality provided by the database 
@@
 
-The build and update process is implemented in Python. So the user does not have to have knowledge in 
-SQL coding but only has to execute one python script and everything is done automatically. This routine 
-ensures that the SQLite database and the BLAST database are always in the same state. It also makes 
-the database a little bit safer, since changes can be reviewed before inserting them into the database.
+The build and update process is implemented in Python. POODLE combines a SQL database with several 
+local Blast databases and this routine 
+ensures that the SQLite database and BLAST databases are always in the same state. 
+It also makes the database a little bit safer, since changes can be reviewed before inserting them 
+into the database. Furthermore, the user does not need detailed knowledge about SQL to create the 
+database, which may be helpful for many laboratories.
 
@@
 because it allows a safe 
-communication between the front end and the database layer as well as a smooth and easy handling of 
-the side. Since a website developed with Vaadin is highly modular, it is easy to extend the web 
+communication between the front end and the database layer as well as a smooth and intuitive user 
+interface. Since a website developed with Vaadin is highly modular, it is easy to extend the web 
 service in the future. That could be necessary, if new functionalities are required. Currently, 
@@
 
-Our software package provides not just a database functionality for powerful and secure data storage 
-and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This function 
+Our software package provides not just a database functionality for powerful and safe data storage 
+and an easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This function 
 is implemented by using a combination of Blast binaries provided by NCBI and the Biojava Api 
@@
 is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search. 
-The remote Blast search is not a fully functional copy of the NCBI web service but can used to 
-perform a quick and simply search against databases provided by NCBI, e.g. Swissprot (\citealp{Doni01}). But we 
+The remote Blast search is not a fully functional copy of the NCBI web service but can be used to 
+perform a quick and simple search against databases provided by NCBI, e.g. Swissprot (\citealp{Doni01}). But we 
 do not recommend to overuse that because too many requests may cause a blacklisting by NCBI. This 
@@
 
-\begin{figure}[!tpb]%figure1
-\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
-235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
-\end{minipage}}
+%\begin{figure}[!tpb]%figure1
+%\fboxsep=0pt\colorbox{gray}{\begin{minipage}[t]{235pt} \vbox to 100pt{\vfill\hbox to
+%235pt{\hfill\fontsize{24pt}{24pt}\selectfont FPO\hfill}\vfill}
+%\end{minipage}}
 %\centerline{\includegraphics{fig01.eps}}
-\caption{Caption, caption.}\label{fig:01}
-\end{figure}
+%\caption{Caption, caption.}\label{fig:01}
+%\end{figure}
 
@@
 this adaption as easy as possible for the user we chose to use widely known software inside of POODLE. 
-Most scientist have heard of SQL as a database managment system. So it is not to dangerous to assume 
+Most scientist have heard of SQL as a database managment system. So it is not too venture to assume 
 that there are people with basic SQL knowledge in most of the laboratories. And that means these 
@@
 The build up process of the database is written in Python. There are two reasons for that. First, 
-Python is a easy and powerful language which makes it possible for the user to adapt the build up 
-process without detailed programming knowledge. And second there is almost no 
-Server without a Python2.7 or higher environment.
+Python is an easy and powerful language which makes it possible for the user to adapt the build up 
+process without detailed programming knowledge. And second Python2.7 is a default package of most 
+operating systems installed on a server. We tried to make POODLE as platform independent as possible 
+and that helps to reach our goal.
 
-Vaadin was chose as the framework to be for several reasons. Java is a widely used programming language 
-in the scientific world. So there is a relative high chance for a person in the laboratory, who speaks 
+Vaadin was chosen as the running framework for several reasons. Java is a widely used programming language 
+in the scientific world. So there is a relative high chance for a person in the laboratory, who 
+is able to work with
 Java. Again we want to make adaption as easy as possible for the user. Furthermore, Vaadin needs a 
@@
 So the user does not have to face extra charges just to be able to use POODLE. More reasons for 
-Vaadin are discussed in the method section.
+Vaadin are discussed above.
 
@@
 
-POODLE provides a secure storage of cloning data as well as a easy-to-use interface for 
+POODLE provides a safe storage of cloning data as well as a easy-to-use interface for 
 interacting with these data. Besides, it comes with functionalities like local and remote Blast 

### 2016-01-12 poodle_project/documents/paper/main.tex
tarting my paper par

--- 2016-01-11 poodle_project/paper/main.tex
@@
 
-\abstract{\textbf{Motivation:} Many life science laboratories are still using Excel files do organize their data. 
+\abstract{\textbf{Motivation:} Many life science laboratories are still using Excel files to organize their data. 
 	This leads to a huge workload for maintenance as well as a inconvenient access and update routine. 
-	POODLE provides an easy-to-use and powerful interface to improve the cloning work of your lab.\\
+	POODLE provides an easy-to-use and powerful interface to improve the cloning work of a lab.\\
 \textbf{Results:} POODLE is a Java-based web interface, which allows intuitive access, update and 
@@
 \enlargethispage{12pt}
+The POODLE project is a project which deals with really daily duty in a bio laboratory.
+Due to the data managment aspect of sequences and the task providing information fast, the project is clearly settled in the computer science field.
+The background data, which was obtained, was focussed on cloning for protein function studies or structure elucidation.
+Therefore we will focus on this application of the POODLE.
 
 \subsection{A real world pipeline}
-function study
+The cloning procedure is a standard strategy, which is used in nearly every life science lab.
+One possible application is in protein structure-function relationship studies.
+These studies use proteins, with a known sequence and start to modify the sequence with mutationsin order to observe changes  in the protein structure or functional bahaviour.
+The general pipeline of such an experiment could be, introducing the mutation via cloning, isolating the mutated protein and visualisation of differences via several methods.
+The visualisation for example could be an NMR interaction study or via X-Ray-Crystallography or any other essay.
+POODLE trys to manage the first  step of this pipeline, which is not only in this pieline the basic step.
 \subsection{cloning as lab strategy}
-Toolkit idea
+Cloning is the key to a huge ammount of variety in the resulting protein constructs.
+Via cloning, it is possible to remove a function, add a function to a protein or influence the structure.
+Today, there are many different cloning methods available, like the classical restriction approach, the site directed mutagenisis method, restriction free cloning or the Crisp-Cas system.
+All mehtods have a specific task and are chosen in various situation.
+For this paper we want to stick to the site directed mutagenisis, which was initially developed by stratagene as QuickChange site-directed mutagensis kit.
+This method allow to introduce small directed mutation into a protein on DNA level.
+these mutations can be used to perform point mutations or switch single or multiple amino acids.
+
+\begin{figure}
+	\include{"../img/QC-cloning.png}{width=\textwidth}
+	\caption{Schema of QC}
+	\label{QC-pic}
+\end{figure}
+
 \subsection{cloning methods}
@@
 
+\bibitem{Alberts {\it et~al}., 200b2}
+Alberts B, Johnson A, Lewis J, et al.
+Molecular Biology of the Cell.
+4th edition.
+New York: Garland Science; 2002.
+Studying Gene Expression and Function.
+Available from: http://www.ncbi.nlm.nih.gov/books/NBK26818/
+
 \end{thebibliography}

### 2016-01-12 poodle_project/documents/paper/main.tex
more text ;)

@@
 these mutations can be used to perform point mutations or switch single or multiple amino acids.
+For this process, a primer is designed containing the new information and annealing sites, which are site-directing for targeted mutation.
+The primer and the target vector are now used in a poly-chain-reaction (PCR).
+This steps generates an amplified product, which contains now the changed sequence.
 
@@
 
-\subsection{cloning methods}
-Classsic Cloning, Quickchange, Restriction free cloning
-
 \subsection{The resulting data}
+The nucleic acids from the cloning process can be characterized in three categories. The first category is the primer-category.
 primer

### 2016-01-12 poodle_project/paper/main.tex
paper auf dem neuesten stand und format ein bisschen angepasst

@@
 
-\abstract{\textbf{Motivation:} Many life science laboratories are still using Excel files do organize their data. 
-	This leads to a huge workload for maintenance as well as an inconvenient access and update routine. 
-	POODLE provides an easy-to-use and powerful interface to improve the cloning work of your lab.\\
+\abstract{\textbf{Motivation:} Many life science laboratories are still using Excel files to organize their data. 
+	This leads to a huge workload for maintenance as well as a inconvenient access and update routine. 
+	POODLE provides an easy-to-use and powerful interface to improve the cloning work of a lab.\\
 \textbf{Results:} POODLE is a Java-based web interface, which allows intuitive access, update and 
@@
 \enlargethispage{12pt}
+The POODLE project is a project which deals with really daily duty in a bio laboratory.
+Due to the data managment aspect of sequences and the task providing information fast, the project is clearly settled in the computer science field.
+The background data, which was obtained, was focussed on cloning for protein function studies or structure elucidation.
+Therefore we will focus on this application of the POODLE.
 
 \subsection{A real world pipeline}
-function study
+The cloning procedure is a standard strategy, which is used in nearly every life science lab.
+One possible application is in protein structure-function relationship studies.
+These studies use proteins, with a known sequence and start to modify the sequence with mutationsin order to observe changes  in the protein structure or functional bahaviour.
+The general pipeline of such an experiment could be, introducing the mutation via cloning, isolating the mutated protein and visualisation of differences via several methods.
+The visualisation for example could be an NMR interaction study or via X-Ray-Crystallography or any other essay.
+POODLE trys to manage the first  step of this pipeline, which is not only in this pieline the basic step.
 \subsection{cloning as lab strategy}
-Toolkit idea
+Cloning is the key to a huge ammount of variety in the resulting protein constructs.
+Via cloning, it is possible to remove a function, add a function to a protein or influence the structure.
+Today, there are many different cloning methods available, like the classical restriction approach, the site directed mutagenisis method, restriction free cloning or the Crisp-Cas system.
+All mehtods have a specific task and are chosen in various situation.
+For this paper we want to stick to the site directed mutagenisis, which was initially developed by stratagene as QuickChange site-directed mutagensis kit.
+This method allow to introduce small directed mutation into a protein on DNA level.
+these mutations can be used to perform point mutations or switch single or multiple amino acids.
+
+\begin{figure}
+	\includegraphics[width=0.4\textwidth]{"../Documents/img/QC-cloning.png}
+	\caption{Schema of QC}
+	\label{QC-pic}
+\end{figure}
+
 \subsection{cloning methods}
@@
 The remote Blast search is not a fully functional copy of the NCBI web service but can be used to 
-perform a quick and simple search against databases provided by NCBI, e.g. Swissprot (\citealp{Doni01}). But we 
+perform a quick and simple search against databases provided by NCBI, e.g. Swissprot (\citealp{Donavan01}). But we 
 do not recommend to overuse that because too many requests may cause a blacklisting by NCBI. This 
@@
 
-\bibitem[O'Donavan {\it et~al}., 2002]{Doni01}
+\bibitem[O'Donavan {\it et~al}., 2002]{Donavan01}
 O'Donovan, C., Martin, M.J., Gattiker, A., Gasteiger, E., Bairoch, A., Apweiler, R.
@@
 
+\bibitem[Alberts {\it et~al}., 2002]{Alberts01}
+Alberts B, Johnson A, Lewis J, et al.
+(2002) Molecular Biology of the Cell.
+4th edition.
+{\it New York: Garland Science}.
+Studying Gene Expression and Function.
+Available from: http://www.ncbi.nlm.nih.gov/books/NBK26818/
+
 \end{thebibliography}

### 2016-01-12 poodle_project/documents/paper/main.tex

--- 2016-01-12 poodle_project/paper/main.tex
@@
 \access{}%Advance Access Publication Date: Day Month Year}
-\appnotes{}%Manuscript Category}
+\appnotes{Original Paper}%Manuscript Category}
 
@@
 \enlargethispage{12pt}
+The POODLE project is a project which deals with really daily duty in a bio laboratory.
+Due to the data managment aspect of sequences and the task providing information fast, the project is clearly settled in the computer science field.
+The background data, which was obtained, was focussed on cloning for protein function studies or structure elucidation.
+Therefore we will focus on this application of the POODLE.
 
 \subsection{A real world pipeline}
-function study
+The cloning procedure is a standard strategy, which is used in nearly every life science lab.
+One possible application is in protein structure-function relationship studies.
+These studies use proteins, with a known sequence and start to modify the sequence with mutationsin order to observe changes  in the protein structure or functional bahaviour.
+The general pipeline of such an experiment could be, introducing the mutation via cloning, isolating the mutated protein and visualisation of differences via several methods.
+The visualisation for example could be an NMR interaction study or via X-Ray-Crystallography or any other essay.
+POODLE trys to manage the first  step of this pipeline, which is not only in this pieline the basic step.
 \subsection{cloning as lab strategy}
-Toolkit idea
+Cloning is the key to a huge ammount of variety in the resulting protein constructs.
+Via cloning, it is possible to remove a function, add a function to a protein or influence the structure.
+Today, there are many different cloning methods available, like the classical restriction approach, the site directed mutagenisis method, restriction free cloning or the Crisp-Cas system.
+All mehtods have a specific task and are chosen in various situation.
+For this paper we want to stick to the site directed mutagenisis, which was initially developed by stratagene as QuickChange site-directed mutagensis kit.
+This method allow to introduce small directed mutation into a protein on DNA level.
+these mutations can be used to perform point mutations or switch single or multiple amino acids.
+
+\begin{figure}
+	\includegraphics[width=0.4\textwidth]{"../../Documents/img/QC-cloning.png}
+	\caption{Schema of QC}
+	\label{QC-pic}
+\end{figure}
+
 \subsection{cloning methods}

### 2016-01-12 poodle_project/documents/proposal/Project_proposal_revise.tex
ich hoffe jetzt ist alles auf dem aktuellen stand

--- 2015-11-06 project/proposal/Project_proposal.tex
@@
 \maketitle
+
 \begin{figure}[h]
 	\centering
-	\includegraphics[scale=0.35]{img/logo_poodle.png}
+	\includegraphics[scale=0.35]{../img/logo_poodle.png}
 \end{figure}
@@
 \end{abstract}
+\newpage
+
+\section*{Contact persons} Alexander Seitz, alexander.seitz@uni-tuebingen.de
+\subsection*{Prerequisites}
+\begin{itemize}
+	\item Interest in SQL-Databases.
+	\item Interest in programming GUIs with Java - Vaadin.
+	\item Interest in integrating bioinformatic tools
+	\item Interest in working with a potential user.Interest in working with a potential user.
+\end{itemize}
 
@@
 Our idea is to create an open source tool, which tries to optimize the organization and speed of getting to the desired data.
+
+\subsection*{Challenges of this project}
+\begin{itemize}
+	\item the communication with the life-scientist.
+	\item communication between the database and graphical interface.
+\end{itemize}
 
@@
 This is useful for designing new Arrays or modifying plasmids, because it's is wanted to do the changes in the least amount of steps, which is of only possible if the most similar sequence is known.\\
-Also an alignment tool can be very useful to visualize the found results. For the alignments the Hirschberg algorithm should be used.\\
-The last module idea was to integrate information to the data from other DBs.
+Another module idea was to integrate information to the data from other DBs.
 If for example a certain protein or domain is incorporated into a plasmid it is useful to have the PDB reference or even integrated information’s of the proteins.
 
+	\subsection*{Tasks}
+	\begin{itemize}
+		\item Communiation with potential Users
+		\item Set-up a SQLite Database
+		\item Write WebBrowser application
+		\item Add Applications to Core programm
+	\end{itemize}
+
 	\begin{figure}[h]
-		\includegraphics[width=\textwidth]{img/Structure.png}
+		\includegraphics[width=\textwidth]{../img/Structure.png}
 	\end{figure}
@@
 It should be easy to set the DB up from the data we might get from our eventually partner lab.
-At the same time and through the whole project time, we want to work on the GUI.
+At the same time and through the whole p	roject time, we want to work on the GUI.
 Because of adding of new functional modules also needs to happen in the GUI.
@@
 	\begin{figure}[h]
-		\includegraphics[width=\textwidth]{img/Time.png}
+		\includegraphics[width=\textwidth]{../img/Time.png}
 	\end{figure}

### 2016-01-12 poodle_project/documents/paper/main.tex
ich hoffe jetzt ist alles auf dem aktuellen stand
paper text benni finisched, please review

@@
 \enlargethispage{12pt}
-The POODLE project is a project which deals with really daily duty in a bio laboratory.
-Due to the data managment aspect of sequences and the task providing information fast, the project is clearly settled in the computer science field.
-The background data, which was obtained, was focussed on cloning for protein function studies or structure elucidation.
-Therefore we will focus on this application of the POODLE.
+POODLE is a software suite which deals with a real problem in a nearly every life science laboratory.
+Due to the data management aspect of sequences and the task of fast information providing.
+The background data, which was obtained, is focussed on cloning for protein structure-function-relationship-studies or structure elucidation.
+Therefore we will focus on this application field.
 
 \subsection{A real world pipeline}
-The cloning procedure is a standard strategy, which is used in nearly every life science lab.
+The cloning procedure is a basic strategy, which is used in nearly every life science lab, independent of the laboratory orientation.
 One possible application is in protein structure-function relationship studies.
-These studies use proteins, with a known sequence and start to modify the sequence with mutationsin order to observe changes  in the protein structure or functional bahaviour.
-The general pipeline of such an experiment could be, introducing the mutation via cloning, isolating the mutated protein and visualisation of differences via several methods.
-The visualisation for example could be an NMR interaction study or via X-Ray-Crystallography or any other essay.
-POODLE trys to manage the first  step of this pipeline, which is not only in this pieline the basic step.
+These studies use recombinant proteins and start to modify the sequence with mutations in order to observe changes  in the protein structure or functional behaviour.
+\cite{Clark1} An example pipeline of such an experiment can be deuced from a publication of our collaborating lab.
+In short: Introducing the mutation via cloning, isolating the mutated expressed protein and visualisation of differences of wild type and mutated protein via several methods.
+\cite{Mira} The visualisation for example could be an NMR interaction study, a X-ray-crystallography study or any kind of essay.
+POODLE tries to manage the design of the first step of this pipeline.
+
 \subsection{cloning as lab strategy}
-Cloning is the key to a huge ammount of variety in the resulting protein constructs.
+Cloning is the key to a huge amount of variety in the resulting protein constructs.
 Via cloning, it is possible to remove a function, add a function to a protein or influence the structure.
-Today, there are many different cloning methods available, like the classical restriction approach, the site directed mutagenisis method, restriction free cloning or the Crisp-Cas system.
-All mehtods have a specific task and are chosen in various situation.
-For this paper we want to stick to the site directed mutagenisis, which was initially developed by stratagene as QuickChange site-directed mutagensis kit.
-This method allow to introduce small directed mutation into a protein on DNA level.
-these mutations can be used to perform point mutations or switch single or multiple amino acids.
+\cite{clark} Today, there are many different cloning methods available, like the classical restriction approach \cite{clark}, the site directed mutagenesis method or QuikChange\textregistered \cite{Quik}, restriction free cloning \cite{Van den Ent} or the Gateway system \cite{clark}.
+In aspect of understanding the importance of cloning, we will take a closer look to one certain method the site directed mutagenesis or QuikChange\textregistered.
+This method allows to introduce a small directed mutation into a protein on DNA level.
+These mutations can be used to switch single or multiple amino acids.
+Procedure is started with designing a primer, which contains the same sequnce as the targeted site except for the mutation, which should be introduced.
+The designed primer is mixed with the target DNA-plasmid and a polymerase chain reaction (PCR) is started.
+In this PCR the primer first does not completely fit to the target, but still good enough for triggering the replication process.
+Already in the first replication cycle the product does contain the mutated sequence.
+In all following cycles an amplification is caused by the primer to enhance the concentration of product plasmid (Figure \ref{QC-pic}).
+\cite{Quik} The product plasmid from the QuikChange\textregistered finally needs to be introduced to the expression organism cells, which can be accomplished for example by electroporation.
+The cells containing the plasmid can finally be used to express recombinantly the desired protein construct.\cite{Mülhardt1}
 
 \begin{figure}
-	\includegraphics[width=0.4\textwidth]{"../../Documents/img/QC-cloning.png}
-	\caption{Schema of QC}
+	\includegraphics[width=0.4\textwidth]{"../img/QC-cloning.png}
+	\caption{Schema of a QuikChange\textregistered  }
 	\label{QC-pic}
@@
 
-\subsection{cloning methods}
-Classsic Cloning, Quickchange, Restriction free cloning
-
-\subsection{The resulting data}
-primer
-cloningVectors
-proteinConstructs
-
 \section{Approach}
-
 As already mentioned above many life-science laboratories use Excel files for storing and working with 
@@
 Blast functionality.
+
+\subsection{Data}
+The nucleic acids used in the cloning process described earlier can be ordered to  three categories, which are used during the cloning process.
+These describe the nucleic acids used for cloning and are primer, cloning-vectors( bought commercially) and protein-construct-plasmids.
+Each category has different specifications and therefore has it's own table in the sql database.
+This implies the exclusion of other materials, like buffers or enzymes.
+These categories can be added later, but do not play a major role in designing or planing experiments, as a opposite to the execution planning.\\
+For consistency reasons and to enable a possible linkage of the data, we decided to place general parameters, which are defined in every data entry.
+Additionally to these general parameters, like name or author.
+Each category has also specific parameters, like primer posses annealing temperature or size as parameters.
 
@@
 
-\bibitem[Alberts {\it et~al}., 2002]{Alberts01}
-Alberts B, Johnson A, Lewis J, et al.
-(2002) Molecular Biology of the Cell.
-4th edition.
-{\it New York: Garland Science}.
-Studying Gene Expression and Function.
-Available from: http://www.ncbi.nlm.nih.gov/books/NBK26818/
+\bibitem[Mülhardt, 2013]{Mülhardt1}
+Mülhardt, Cornel (2013) 
+Der Experimentator Molekularbiologie Genomics,
+{\it Springer Spektrum} 7. Edition,
+ISBN: 978-3-642-34636-1
+
+\bibitem[Clark {\it et~al}, 2009]{Clark1}
+Clark, D. P., Pzdernik, N.J.(2009) 
+Molekulare Biotechnologie - Grundlagen und Anwendungen, 
+{\it Springer Spektrum},
+ISBN: 978-3-8274-2128-9
+
+\bibitem[Stoffregen {\it et~al}.,2012]{Mira}
+Mira C.
+Stoffregen and Matthias M.
+Schwer and Fabian A.
+Renschler and Silke Wiesner (2012) Methionine Scanning as an \{NMR\} Tool for Detecting and Analyzing Biomolecular Interaction Surfaces {\it Structure} {\bf 20} (4), 573-581.
+doi: http://dx.doi.org/10.1016/j.str.2012.02.012
+
+\bibitem[Strattagene, 2007]{Quik}
+Stratagene (2007) QuikChange\textregistered Site-Directed Mutagenesis Kit 
+ http://www.genomics.agilent.com/files/Manual/200521_C.pdf
+
+ \bibitem[Van den Ent {\it et~al}, 2006]{Van den Ent}
+ Van den Ent, F., & Löwe, J.
+(2006).
+RF cloning: a restriction-free method for inserting target genes into plasmids.
+Journal of Biochemical and Biophysical Methods, 67(1), 67–74.
+doi:10.1016/j.jbbm.2005.12.008
 

### 2016-01-12 poodle_project/webInterface/BlastPackage/BlastClasses/NCBIQBlastClass.java

@@ -59,6 +59,7 @@ public class NCBIQBlastClass {
     BufferedReader reader = null;
     try {
       // send blast request and save request id
+    	System.out.println("sequence:"+sequence+"\n props"+props);
       rid = service.sendAlignmentRequest(sequence, props);
  
       // wait until results become available. Alternatively, one can do other computations/send other alignment requests

### 2016-01-12 poodle_project/webInterface/src/contentViews/BlastResultView.java

@@ -91,8 +91,8 @@ public class BlastResultView extends BasicView{
 			}
 		}
 		title = new Label("Result of the BLAST");
-		
-		poodleUI.getPage().open("file:///"+basepath+qfPath+"BlastResult.html", "_blank");
+		title = new Label(resultPrimer+this.resultProtein+this.resultVector+this.resultBlast);
+		poodleUI.getPage().open("file:///"+basepath+qfPath+"BlastResult.html", "_parent");
 		
 //		System.out.println(resultPrimer);
 //		JsonParser jsonParser = new JsonParser();

### 2016-01-12 poodle_project/webInterface/src/contentViews/NewEntryView.java

@@ -66,9 +66,9 @@ public class NewEntryView extends BasicView {
 				addComponent(working);
 				try{
 					fieldValdiation();
-					try{
-						File page = new File(basepath+"/WEB-INF/db/Wiesner/");
-					}
+//					try{
+//						File page = new File(basepath+"/WEB-INF/db/Wiesner/");
+//					}
 				}
 				catch(Exception e){
 					Label error = new Label ("Fields are not correct!");

### 2016-01-12 poodle_project/documents/paper/main.tex
neue ordnung in database

@@
 	This leads to a huge workload for maintenance as well as a inconvenient access and update routine. 
-	POODLE provides an easy-to-use and powerful interface to improve the cloning work of a lab.\\
+	POODLE provides an easy-to-use and powerful interface to improve the cloning work of a laboratory.\\
 \textbf{Results:} POODLE is a Java-based web interface, which allows intuitive access, update and 
 manipulation of data for cloning.\\
-\textbf{Contact:} \href{}{forename.surname@student.uni-tuebingen.de}\\
+\textbf{Contact:} \href{}{jonas.ditz@student.uni-tuebingen.de, benjamin.schroeder@student.uni-tuebingen.de}\\
 \textbf{Supplementary information:} Supplementary data and the code are available at \textit{https://github.com/derjedi/BioinformaticsI\-Assigments/tree/master/poodle\_project}
@@
 \enlargethispage{12pt}
-POODLE is a software suite which deals with a real problem in a nearly every life science laboratory.
-Due to the data management aspect of sequences and the task of fast information providing.
-The background data, which was obtained, is focussed on cloning for protein structure-function-relationship-studies or structure elucidation.
-Therefore we will focus on this application field.
+POODLE is a software suite which deals with a real world problem in a nearly every life science 
+laboratory. This problem occurs due to the data management aspect of sequences and the task of fast 
+information providing. The background data, which was obtained, is focused on cloning for protein 
+structure-function-relationship-studies or structure elucidation.
 
 \subsection{A real world pipeline}
-The cloning procedure is a basic strategy, which is used in nearly every life science lab, independent of the laboratory orientation.
-One possible application is in protein structure-function relationship studies.
-These studies use recombinant proteins and start to modify the sequence with mutations in order to observe changes  in the protein structure or functional behaviour.
-\cite{Clark1} An example pipeline of such an experiment can be deuced from a publication of our collaborating lab.
-In short: Introducing the mutation via cloning, isolating the mutated expressed protein and visualisation of differences of wild type and mutated protein via several methods.
-\cite{Mira} The visualisation for example could be an NMR interaction study, a X-ray-crystallography study or any kind of essay.
-POODLE tries to manage the design of the first step of this pipeline.
+The cloning procedure is a basic strategy, which is used in nearly every life science lab, 
+independent of the laboratory's orientation. One possible application is in protein 
+structure-function-relationship-studies. These studies use recombinant proteins and start to modify 
+the sequence with mutations in order to observe changes in the structure or functional 
+behavior of the protein (\citealp{Clark1}). An example of a pipeline for such an experiment can be 
+deduced from a publication of our collaborating lab (\citealp{Mira}). A brief summary of such a procedure would consists 
+of the following three steps: 
+\begin{enumerate}
+ \item Introducing the mutation via cloning
+ \item Isolating the mutated expressed protein
+ \item Visualization of differences of wild type and mutated protein via several methods
+\end{enumerate}   
+The visualization for example could be an NMR interaction study, a X-ray-crystallography study or 
+any kind of essay. POODLE tries to manage the design of the first step of this pipeline.
 
 \subsection{cloning as lab strategy}
-Cloning is the key to a huge amount of variety in the resulting protein constructs.
-Via cloning, it is possible to remove a function, add a function to a protein or influence the structure.
-\cite{clark} Today, there are many different cloning methods available, like the classical restriction approach \cite{clark}, the site directed mutagenesis method or QuikChange\textregistered \cite{Quik}, restriction free cloning \cite{Van den Ent} or the Gateway system \cite{clark}.
-In aspect of understanding the importance of cloning, we will take a closer look to one certain method the site directed mutagenesis or QuikChange\textregistered.
-This method allows to introduce a small directed mutation into a protein on DNA level.
-These mutations can be used to switch single or multiple amino acids.
-Procedure is started with designing a primer, which contains the same sequnce as the targeted site except for the mutation, which should be introduced.
-The designed primer is mixed with the target DNA-plasmid and a polymerase chain reaction (PCR) is started.
-In this PCR the primer first does not completely fit to the target, but still good enough for triggering the replication process.
-Already in the first replication cycle the product does contain the mutated sequence.
-In all following cycles an amplification is caused by the primer to enhance the concentration of product plasmid (Figure \ref{QC-pic}).
-\cite{Quik} The product plasmid from the QuikChange\textregistered finally needs to be introduced to the expression organism cells, which can be accomplished for example by electroporation.
-The cells containing the plasmid can finally be used to express recombinantly the desired protein construct.\cite{Mülhardt1}
+Cloning is the key to a huge amount of variety in the resulting protein constructs. Via cloning, it 
+is possible to remove a function, add a function to a protein or influence the structure (\citealp{Clark1}). 
+Today, there are many different cloning methods available, like the classical restriction approach 
+(\citealp{Clark1}), the site directed mutagenesis method or QuikChange\textregistered (\citealp{Quik}), 
+restriction free cloning (\citealp{VanDenEnt}) or the Gateway system (\citealp{Clark1}). In aspect 
+of understanding the importance of cloning, we will take a closer look to one certain method, the 
+site directed mutagenesis or QuikChange\textregistered. This method allows to introduce a small 
+directed mutation into a protein on DNA level. These mutations can be used to switch single or 
+multiple amino acids. Procedure is started with designing a primer, which contains the same sequence 
+as the targeted site except for the mutation, which should be introduced. The designed primer is 
+mixed with the target DNA-plasmid and a polymerase chain reaction (PCR) is started. In this PCR, the 
+primer first does not completely fit to the target, but still good enough for triggering the replication 
+process. Already in the first replication cycle the product does contain the mutated sequence. In 
+all following cycles an amplification is caused by the primer to enhance the concentration of 
+product plasmid (\citealp{Quik}) (see Figure \ref{QC-pic}). The product plasmid from the QuikChange\textregistered 
+finally needs to be introduced to the expression organism cells, which can be accomplished for example 
+by electroporation. The cells containing the plasmid can finally be used to express recombinantly 
+the desired protein construct (\citealp{Mülhardt1}).
 
@@
 \subsection{Data}
-The nucleic acids used in the cloning process described earlier can be ordered to  three categories, which are used during the cloning process.
-These describe the nucleic acids used for cloning and are primer, cloning-vectors( bought commercially) and protein-construct-plasmids.
-Each category has different specifications and therefore has it's own table in the sql database.
-This implies the exclusion of other materials, like buffers or enzymes.
-These categories can be added later, but do not play a major role in designing or planing experiments, as a opposite to the execution planning.\\
-For consistency reasons and to enable a possible linkage of the data, we decided to place general parameters, which are defined in every data entry.
-Additionally to these general parameters, like name or author.
-Each category has also specific parameters, like primer posses annealing temperature or size as parameters.
+The nucleic acids used in the cloning process described earlier can be ordered to  three categories, 
+which are used during the cloning process. These describe the nucleic acids used for cloning and 
+are primer, cloning-vectors( bought commercially) and protein-construct-plasmids. Each category has 
+different specifications and therefore has it's own table in the SQL database. This implies the 
+exclusion of other materials, like buffers or enzymes. These categories can be added later, but do 
+not play a major role in designing or planing experiments, as a opposite to the execution planning.
+
+For consistency reasons and to enable a possible linkage of the data, we decided to place general 
+parameters, which are defined in every data entry. Additionally to these general parameters, like 
+name or author each category has also specific parameters, like primer posses annealing temperature 
+or size as parameters.
 
@@
 
-\bibitem[Mülhardt, 2013]{Mülhardt1}
-Mülhardt, Cornel (2013) 
-Der Experimentator Molekularbiologie Genomics,
-{\it Springer Spektrum} 7. Edition,
-ISBN: 978-3-642-34636-1
+\bibitem[M\"{u}lhardt, 2013]{Mülhardt1}
+M\"{u}lhardt, Cornel (2013) Der Experimentator Molekularbiologie Genomics,{\it Springer Spektrum} 7. Edition,ISBN: 978-3-642-34636-1
 
-\bibitem[Clark {\it et~al}, 2009]{Clark1}
-Clark, D. P., Pzdernik, N.J.(2009) 
-Molekulare Biotechnologie - Grundlagen und Anwendungen, 
-{\it Springer Spektrum},
-ISBN: 978-3-8274-2128-9
+\bibitem[Clark {\it et~al}., 2009]{Clark1}
+Clark, D. P., Pzdernik, N.J.(2009) Molekulare Biotechnologie - Grundlagen und Anwendungen, {\it Springer Spektrum}, ISBN: 978-3-8274-2128-9
 
-\bibitem[Stoffregen {\it et~al}.,2012]{Mira}
-Mira C.
-Stoffregen and Matthias M.
-Schwer and Fabian A.
-Renschler and Silke Wiesner (2012) Methionine Scanning as an \{NMR\} Tool for Detecting and Analyzing Biomolecular Interaction Surfaces {\it Structure} {\bf 20} (4), 573-581.
-doi: http://dx.doi.org/10.1016/j.str.2012.02.012
+\bibitem[Stoffregen {\it et~al}., 2012]{Mira}
+Stoffregen, M.
+C., Schwer, M.
+M., Renschler, F.
+A., Wiesner, S.
+(2012) Methionine Scanning as an NMR Tool for Detecting and Analyzing Biomolecular Interaction Surfaces {\it Structure} {\bf 20} (4), 573-581.
+doi: 10.1016/j.str.2012.02.012
 
-\bibitem[Strattagene, 2007]{Quik}
-Stratagene (2007) QuikChange\textregistered Site-Directed Mutagenesis Kit 
- http://www.genomics.agilent.com/files/Manual/200521_C.pdf
+\bibitem[Stratagene, 2007]{Quik}
+Stratagene (2007) QuikChange\textregistered Site-Directed Mutagenesis Kit {\it http://www.genomics.agilent.com/files/Manual/200521\_C.pdf}
 
- \bibitem[Van den Ent {\it et~al}, 2006]{Van den Ent}
- Van den Ent, F., & Löwe, J.
+\bibitem[Van den Ent {\it et~al}., 2006]{VanDenEnt}
+Van den Ent, F.,  L\"{o}we, J.
 (2006).
 RF cloning: a restriction-free method for inserting target genes into plasmids.
-Journal of Biochemical and Biophysical Methods, 67(1), 67–74.
+{\it Journal of Biochemical and Biophysical Methods}, {\bf 67}(1), 67–74.
 doi:10.1016/j.jbbm.2005.12.008

### 2016-01-12 poodle_project/webInterface/WebContent/WEB-INF/db/buildDatabase.py

@@ -50,7 +50,7 @@ def createProtConTable(db):
     # drop table if exists
     db.execute('drop table if exists proteinConstructs')
     # create table proteinConstructs
-    db.execute('CREATE table proteinConstructs (id Integer Primary Key,box,position,protein,domain,protein_family,mutation,backbone_vector,antibiotics,cloning_sites,QC,RF,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,project,date,author,notes,name,C_Term_Tag,N_Term_Tag,vector,cloning_information,organism,protein_sequence)')
+    db.execute('CREATE table proteinConstructs (id Integer Primary Key,name,author,date,box,position,protein,domain,protein_family,mutation,backbone_vector,antibiotics,cloning_sites,QC,RF,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,project,notes,C_Term_Tag,N_Term_Tag,vector,cloning_information,organism,protein_sequence)')
     values = []
     protConFile = open(DATA_PATH + 'protein_constructs/protein_constructs.csv','r')
     for line in protConFile.readlines():
@@ -65,7 +65,7 @@ def createProtConTable(db):
             values.append(tuple(lineSplit))
 
     # insert values into table
-    db.execute('insert into proteinConstructs (id,box,position,protein,domain,protein_family,mutation,backbone_vector,antibiotics,cloning_sites,QC,RF,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,project,date,author,notes,name,C_Term_Tag,N_Term_Tag,vector,cloning_information,organism,protein_sequence) values (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', values)
+    db.execute('insert into proteinConstructs (id,name,author,date,box,position,protein,domain,protein_family,mutation,backbone_vector,antibiotics,cloning_sites,QC,RF,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,project,notes,C_Term_Tag,N_Term_Tag,vector,cloning_information,organism,protein_sequence) values (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', values)
 
 
 # function to create table of cloning vectors
@@ -73,7 +73,7 @@ def createClonVecTable(db):
     # drop table, if it already exists
     db.execute('drop table if exists cloningVectors')
[…]

### 2016-01-12 poodle_project/documents/paper/main.tex
alles wieder repariert

@@
 service in the future. That could be necessary, if new functionalities are required. Currently, 
-there are three pages with different roles. The search page provides a formula that can be used 
+there are three pages with different roles. The search page (see Figure \ref{fig:poodleMain}) provides a formula that can be used 
 to perform a simple SQL search in the local database. Therefor, different fields are displayed and 
@@
 databases on the Blast page. That functionality can be found on the Blast page.
+
+\begin{figure}[!tpb]
+ \centering
+ \includegraphics[width=0.3\textwidth]{../img/Poodle_MainPage.png}
+ \caption{Main page of POODLE's webservice. Users can perform a SQL search against the local database on this page.}
+ \label{fig:poodleMain}
+\end{figure}
 
@@
 Java. Again we want to make adaption as easy as possible for the user. Furthermore, Vaadin needs a 
-tomcat server. Such a server is provided free of charge by Apache\footnote{http://www.apache.org/}. 
+tomcat server. Such a server is provided free of charge by Apache (for more detail visit http://www.apache.org/). 
 So the user does not have to face extra charges just to be able to use POODLE. More reasons for 

### 2016-01-12 poodle_project/webInterface/WebContent/WEB-INF/db/buildDatabase.py

@@ -65,7 +65,7 @@ def createProtConTable(db):
             values.append(tuple(lineSplit))
 
     # insert values into table
-    db.execute('insert into proteinConstructs (id Integer Primary Key,name,author,date,box,position,project,organism,protein,domain,protein_family,mutation,backbone_vector,antibiotics,restriction,QC,RF,cloning_information,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,notes,C_Term_Tag,N_Term_Tag,protein_sequence) values (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', values)
+    db.execute('insert into proteinConstructs (id,name,author,date,box,position,project,organism,protein,domain,protein_family,mutation,backbone_vector,antibiotics,restriction,QC,RF,cloning_information,used_primer,constructed_from,concentration,DH5A_stock,Cplus_stock,notes,C_Term_Tag,N_Term_Tag,protein_sequence) values (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', values)
 
 
 # function to create table of cloning vectors
@@ -88,7 +88,7 @@ def createClonVecTable(db):
             values.append(tuple(lineSplit))
 
     # insert values into table
-    db.execute('insert into cloningVectors (id,name,author,date,box,position,C_Term_Tags,N_Term_Tags,construct_cleavable,MCS,antibiotics,fw_seq_primer,rv_seq_primer,vector_map,size,concentration,DH5A_stock,notes,vector_sequence) values (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', values)
+    db.execute('insert into cloningVectors (id,name,author,date,box,position,C_Term_Tags,N_Term_Tags,construct_cleavable,MCS,antibiotics,fw_seq_primer,rv_seq_primer,vector_map,size,concentration,DH5A_stock,notes,vector_sequence) values (?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?,?)', values)
 
 
 # function to create table of primer
@@ -109,7 +109,7 @@ def createPrimTable(db):
             values.append(tuple(lineSplit))
 
     # insert values into table
[…]

### 2016-01-16 AssignmentIX/Assignment9-Ditz_Schroeder-WS15-16.tex
bonus aufgabe angefangen aber evtl fallen dir ja noch weitere probleme ein, die wir hier aufschreiben koennen

--- 2015-12-09 AssignmentVIII/Assignment8-Ditz_Schroeder-WS15-16.tex
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{8}{Alexander Seitz}{14. December 2015}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
+\header{9}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{4}
 
-\section*{Theoretical Assignment - \textit{Suffix tree construction and application}}
+\section*{Theoretical Assignment - \textit{Overlap and Layout}}
 
-\subsection*{a - \textit{Suffix tree construction}}
-\subsubsection*{i}
-If one uses the naive approach to construct the suffix tree of ``CTAGTAGCAG'', the result would look 
-like Figure \ref{fig:naiveImpl}.
+\section*{Theoretical Assignment - \textit{Overlap graph figure}}
 
-\begin{figure}[ht]
- \centering
- \subfigure[step 1]{
-  \includegraphics[width=0.15\textwidth]{tast1ai/tree_step01.png}
- }
- \subfigure[step 2]{
-  \includegraphics[width=0.25\textwidth]{tast1ai/tree_step02.png}
- }
- \subfigure[step 3]{
-  \includegraphics[width=0.35\textwidth]{tast1ai/tree_step03.png}
- }
- \subfigure[step 4]{
-  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step04.png}
- }
- \subfigure[step 5]{
-  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step05.png}
- }
- \subfigure[step 6]{
-  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step06.png}
- }
- \subfigure[step 7]{
-  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step07.png}
- }
- \subfigure[step 8]{
-  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step08.png}
- }
- \subfigure[step 9]{
-  \includegraphics[width=0.45\textwidth]{tast1ai/tree_step09.png}
- }
- \subfigure[step 10]{
-  \includegraphics[width=0.7\textwidth]{tast1ai/tree_step10.png}
- }
- \subfigure[step 11]{
-  \includegraphics[width=0.7\textwidth]{tast1ai/tree_step11.png}
- }
- \caption{All steps of the naive implementation of suffix tree construction for the string ``CTAGTAGCAG''.}
- \label{fig:naiveImpl}
-\end{figure}
+\section*{Theoretical Assignment - \textit{Computing all overlaps using suffix tree}}
 
-\subsubsection*{ii}
+Finding all overlaps is basically a APSP (All-pairs-suffix-prefix) problem. Solving such a problem 
+with a suffix tree approach has a time complexity of $O(n + k^2)$ where $n$ is the total length of 
+all strings and $k$ is the count of strings. First all reads will be concatenated with a separation 
+character between all reads and a terminal character at the end. Now it is rather simple to check, 
+whether the prefix of one read matches with the suffix of another read. This can be done using the 
+suffix tree since we know that each prefix starts with an separation character (one could put one 
+separation character at the beginning of the string to make this statement true) and every suffix 
+ends ether with the separation character or the terminal character. Since one has to go trough the 
+whole concatenated string and compare the prefix of each read with the suffix of every other read, 
+this approach has a total runtime complexity of $O(n+k^2)$.
 
-\subsection*{b - \textit{Main data table of WOTD}}
+\section*{Bonus - \textit{Challenges of your Project}}
 
-\subsection*{c - \textit{Suffix tree application}}
-
-\section*{Theoretical Assignment - \textit{Runtime and space complexity of suffix trees}}
-
-\subsection*{a}
-
-\subsection*{b}
-
-\subsection*{c}
+One of the biggest challenges during our project was the framework we chose, Vaadin. We were not able 
+to get it working of all computers we used. So in the end it was just one of us, who was able to work 
+on the front-end layer. That slowed us down a lot. If we would start this project again from the scratch, 
+Django would be a better choice. This framework comes with a development server and, therefore, would 
+maybe make developing together easier. In the end we wasted a lot of time with Eclipse/Vaadin/Eclipse+Vaadin 
+problems. Another challenge was the database schema for POODLE. We, especially Benjamin, talked a lot 
+with people from Silke Wiesner's group at the MPI for Developmental Biology and that resulted in 
+several schema changes during our project time.
 

### 2016-01-20 AssignmentIX/Assignment11-Ditz_Schroeder-WS15-16.tex
erste aufgabe des neuen blatts ist fertig

--- 2016-01-16 AssignmentIX/Assignment9-Ditz_Schroeder-WS15-16.tex
@@
   \begin{vartab}{\thecolmns}
-    \numbers{#1} & $\sum$ (6+2)\\\hline
+    \numbers{#1} & $\sum$ (10)\\\hline
     \emptyLine{\thecolmns}\\
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{9}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{4}
+\header{11}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
 
-\section*{Theoretical Assignment - \textit{Overlap and Layout}}
+\section*{Theoretical Assignment - \textit{Assembly using de Bruijn graph}}
 
-\section*{Theoretical Assignment - \textit{Overlap graph figure}}
+The de Bruijn graph for the reads provided on the assignment sheet would look like the graph in
+Figure \ref{fig:4mere}, if one chooses $k = 4$. As one can see easily, there are not just one but 
+four different Eulerian paths in the graph. Each path results in one of the following superstring:
 
-\section*{Theoretical Assignment - \textit{Computing all overlaps using suffix tree}}
+\begin{align}
+ S_1 &= AACCGTTAACGTAAACGT \nonumber \\
+ S_2 &= AACCGTAAACGTTAACGT \nonumber \\
+ S_3 &= AACCGTTAAACGTAACGT \nonumber \\
+ S_4 &= AACCGTAACGTTAAACGT \nonumber
+\end{align}
 
-Finding all overlaps is basically a APSP (All-pairs-suffix-prefix) problem. Solving such a problem 
-with a suffix tree approach has a time complexity of $O(n + k^2)$ where $n$ is the total length of 
-all strings and $k$ is the count of strings. First all reads will be concatenated with a separation 
-character between all reads and a terminal character at the end. Now it is rather simple to check, 
-whether the prefix of one read matches with the suffix of another read. This can be done using the 
-suffix tree since we know that each prefix starts with an separation character (one could put one 
-separation character at the beginning of the string to make this statement true) and every suffix 
-ends ether with the separation character or the terminal character. Since one has to go trough the 
-whole concatenated string and compare the prefix of each read with the suffix of every other read, 
-this approach has a total runtime complexity of $O(n+k^2)$.
+This happens due to the fact that there are nodes with more than one outgoing an incoming edge. If
+one chooses $k = 5$ the resulting de Bruijn graph would look like the graph in Figure \ref{fig:5mere}.
+It is obvious that the number of nodes is depended on $k$. With a bigger $k$ there are more nodes in 
+the resulting de Bruijn graph. But in this case there is one problem. Since there are more than two 
+unbalanced nodes in the de bruijn graph there is no Eulerian path.
 
-\section*{Bonus - \textit{Challenges of your Project}}
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=0.7\textwidth]{deBruijnGraph_4mere.png}
+ \caption{De Bruijn graph for the given reads and $k = 4$.}
+ \label{fig:4mere}
+\end{figure}
 
-One of the biggest challenges during our project was the framework we chose, Vaadin. We were not able 
-to get it working of all computers we used. So in the end it was just one of us, who was able to work 
-on the front-end layer. That slowed us down a lot. If we would start this project again from the scratch, 
-Django would be a better choice. This framework comes with a development server and, therefore, would 
-maybe make developing together easier. In the end we wasted a lot of time with Eclipse/Vaadin/Eclipse+Vaadin 
-problems. Another challenge was the database schema for POODLE. We, especially Benjamin, talked a lot 
-with people from Silke Wiesner's group at the MPI for Developmental Biology and that resulted in 
-several schema changes during our project time.
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=1\textwidth]{deBruijnGraph_5mere.png}
+ \caption{De Bruijn graph for the given reads and $k = 5$.}
+ \label{fig:5mere}
+\end{figure}
+
+\section*{Practical Assignment - \textit{Assemble the human mitochondrial genome}}
 

### 2016-01-20 AssignmentIX/deBrujinApproach.py

@@ -3,30 +3,57 @@
 import sys
 import os
 
+from graphviz import Digraph
+
 def kMinus1List(reads, k):
   kMinus1 = []
 
   for read in reads:
+    print "work on Read "+read+"..."
     i = 0
-    while i+k < len(read):
+    while i+k <= len(read):
       kMer = read[i:i+k]
       if kMer[:-1] not in kMinus1:
         kMinus1.append(kMer[:-1])
       if kMer[1:] not in kMinus1:
         kMinus1.append(kMer[1:])
+      i = i + 1
 
+  print "all computed k-1 mere:"
+  print kMinus1
   return kMinus1
 
+
+def drawDeBruijn(kMinus1, k):
+  deBruijn = Digraph(comment='de Bruijn graph for given reads', format='png')
+  deBruijn.graph_attr['rankdir'] = 'LR'
+  
+  # insert nodes
+  for mer in kMinus1:
+    deBruijn.node(mer, mer)
+  
+  # insert edges
+  for mer1 in kMinus1:
+    for mer2 in kMinus1:
+      if mer1 == mer2:
+        continue
+      if mer1[1:] == mer2[:-1]:
+        deBruijn.edge(mer1, mer2)  
+ 
+  # print graph
+  deBruijn.render(filename="deBruijnGraph_"+str(k)+"mere")
 
 
 if __name__ == '__main__':
   # check whether k was given or not
   if len(sys.argv) < 2:
-    sys.exit('USAGE: %s <k>', % system.argv[0])
+    sys.exit("USAGE: "+sys.argv[0]+" <k>")
 
   try:
     k = int(sys.argv[1])
   except ValueError:
     sys.exit('k has to be a integer')
 
-  
+  reads = ['ACCGT', 'CGTAACGTT', 'ACGTTA', 'GTTAA', 'TAAACTG']
+  kMinus1Mere = kMinus1List(reads, k)
+  drawDeBruijn(kMinus1Mere, k)

### 2016-01-21 AssignmentIX/Assignment9-Ditz_Schroeder-WS15-16.tex
final

@@
 \section*{Theoretical Assignment - \textit{Overlap and Layout}}
+\subsection*{graphs}
+The graphs from the exercise are shown in Figure 1-2. Figure \ref{fig:og} is the overlap grap with minimal spanning tree (red edges) and Figure \ref{fig:layout} shows the layout.
 
+\begin{figure}[h]
+	\includegraphics[width=\textwidth]{minimal-Spanning-Tree.png}
+	\caption{Minimal-spanning-tree}
+	\label{fig:og}
+\end{figure}
+
+\begin{figure}[h]
+	\includegraphics[width=\textwidth]{layout.png}
+	\caption{layout}
+	\label{fig:layout}
+\end{figure}
+
+\subsection*{Is the Layout consitent?}
+One overlap ($f_6$ and $f_8$) is not consistent, because:
+\begin{equation*}
+o(3'f_6 - 3'f_8)=80
+\end{equation*}
 \section*{Theoretical Assignment - \textit{Overlap graph figure}}
+
+A Figure for a paper would look like Figure \ref{fig:paper}.
+
+\begin{figure}[h]
+	\centering
+	\subfigure{
+		\includegraphics[width=0.45\textwidth]{minimal-Spanning-Tree.png}
+	}
+	\subfigure{
+		\includegraphics[width=0.45\textwidth]{layout.png}
+	}
+	\caption{\textbf{left}: Overlap Graph with minimal spanning tree in red. \textbf{right}: Layout computed with the minimal spanning tree shown on the left site.}
+	\label{fig:paper}
+\end{figure}
 

### 2016-01-21 AssignmentX/Assignment10-Ditz_Schroeder-WS15-16.tex

--- 2016-01-20 AssignmentIX/Assignment11-Ditz_Schroeder-WS15-16.tex
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{11}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
+\header{10}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
 
@@
 \begin{align}
- S_1 &= AACCGTTAACGTAAACGT \nonumber \\
- S_2 &= AACCGTAAACGTTAACGT \nonumber \\
- S_3 &= AACCGTTAAACGTAACGT \nonumber \\
- S_4 &= AACCGTAACGTTAAACGT \nonumber
+ S_1 &= ACCGTTAACGTAAACGT \nonumber \\
+ S_2 &= ACCGTAAACGTTAACGT \nonumber \\
+ S_3 &= ACCGTTAAACGTAACGT \nonumber \\
+ S_4 &= ACCGTAACGTTAAACGT \nonumber
 \end{align}
@@
 It is obvious that the number of nodes is depended on $k$. With a bigger $k$ there are more nodes in 
-the resulting de Bruijn graph. But in this case there is one problem. Since there are more than two 
-unbalanced nodes in the de bruijn graph there is no Eulerian path.
+the resulting de Bruijn graph. The resulting graph for $k = 5$ is non-connected. So the superstring 
+for this graph is not just one but three strings:
+
+\begin{align}
+ S_{part_1} &= TAAACTG \nonumber \\
+ S_{part_2} &= CGTAACGTTAA \nonumber \\
+ S_{part_3} &= ACCGT \nonumber
+\end{align}
+
+One can see that $S_{part_1} = f_5$ and $S_{part_3} = f_1$, while $S_{part_2}$ is the result of an 
+overlap alignment between $f_2$, $f_3$ and $f_4$. In general the second graph is more realistic. 
+It is very unlikely to get a connected graph with real-life data. So it is possible that just $f_2$, 
+$f_3$ and $f_4$ come from the same area in the target DNA. $f_1$ and $f_5$ could come from a different 
+contig and, hence, result in this graph (Figure \ref{fig:5mere}). Since this is a minimal example 
+the first graph (Figure \ref{fig:4mere}) is not wrong but one should not expect to get a connected 
+graph all the time. In fact a connected graph is suspicious, normally.
 
@@
  \centering
- \includegraphics[width=0.7\textwidth]{deBruijnGraph_4mere.png}
+ \includegraphics[width=1\textwidth]{deBruijnGraph_4mere.png}
  \caption{De Bruijn graph for the given reads and $k = 4$.}

### 2016-01-21 AssignmentX/exercise2/R-script.R
start of exercise 2

@@ -1,0 +1,46 @@
+wd<-"C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2"
+setwd(wd)
+library(plotrix)
+
+
+
+#velvetPlots:
+velvet7results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_7/stats.txt", header =TRUE)
+velvet15results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_15/stats.txt", header = TRUE)
+velvet23results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_23/stats.txt", header = TRUE)
+velvet31results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_31/stats.txt", header = TRUE)
+
+png("velvet/velvet7kmersCoverage.png")
+velvet7Hist <- hist(velvet7results$short1_cov, xlim=range(0,120), breaks=1000, main="coverage for 7 k-mers")
+dev.off()
+
+png("velvet/velvet7kmersWheightedCoverage.png")
+velvet7HistWheight <- weighted.hist(velvet7results$short1_cov, velvet7results$lgth, breaks=0:50, main="coverage for wheighted 7 k-mers")
+dev.off()
+
+png("velvet/velvet15kmersCoverage.png")
+velvet15Hist <- hist(velvet15results$short1_cov, xlim=range(0,70), breaks=1000, main="coverage for 15 k-mers")
+dev.off()
+
+png("velvet/velvet15kmersWeightedCoverage.png")
+velvet15HistWheight <- weighted.hist(velvet15results$short1_cov, velvet15results$lgth, breaks=0:50, main="coverage for wheighted 15 k-mers")
+dev.off()
+
+png("velvet/velvet23kmersCoverage.png")
+velvet23Hist <- hist(velvet23results$long_cov, xlim=range(0,80), breaks=1000, main="coverage for 21 k-mers")
+dev.off()
+
+png("velvet/velvet23kmersWeightedCoverage.png")
[…]

### 2016-01-24 AssignmentX/Assignment10-Ditz_Schroeder-WS15-16.tex
added all data for ex 2 Assignment 10

@@
 \section*{Practical Assignment - \textit{Assemble the human mitochondrial genome}}
+\subsubsection*{Introduction}
+The mitochondrial genome is rather a small genome in our world.
+But even this rather small genome, with its $10^4$ basepairs is a though nut, when trying to discover its sequence from reads \cite{!!!!}.
+For this purpose we used two different alignment algorithms.
+The Velvet algorithm by Zebrino and Birney is using de Bruijn graphs to assemble the reads.\cite{VelvetProgram}
+Likewise does the SOAP algotihm by Luo et al. use a de Bruijn graph \cite{SOAPProgram}. The differences of both algorithms lie in their detailed structure.
+
+\subsubsection*{Results}
+both algorithms were used to calculate the assembly of the mitochondrial genome seperatley.
+The velvet algorithm was computed on the homesource with 4 k-mer sizes (from 7 to 31 bases).
+as a result of the lacking hardware and the missing password for the WSI-Server, the resulting data from the SOAP algorithm was thankfully provided by Sanja Koehlers goup.
+
+\subsubsection*{Discussion}
+
+\subsubsection*{Acknowledgement}
+Thanks again to Sanja Koehler an her group, who enabled this phenomenal sucess of publishing this paper.
+
+\begin{thebibliography}{20}
+	\bibitem{VelvetProgram} Velvet: algorithms for de novo short read assembly using de Bruijn graphs. D.R. Zerbino and E. Birney. Genome Research 18:821-829. 
+	\bibitem{SOAPProgram} SOAPdenovo2: an empirically improved memory-efficient short-read de novo assembler. Luo et al. GigaScience 2012 1:18.
+\end{thebibliography}
 

### 2016-01-24 AssignmentX/exercise2/R-script.R

@@ -1,46 +1,57 @@
-wd<-"C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2"
+wd<-"C:/Users/benja/Desktop/material"
 setwd(wd)
 library(plotrix)
 
+#velvet coverage
+velvet7results <- read.delim(c(wd,"/velvet/velvet_result_7/stats.txt"), header =TRUE)
+velvet15results <- read.delim("C:/Users/benja/Desktop/material/velvet/velvet_result_15/stats.txt", header = TRUE)
+velvet23results <- read.delim("C:/Users/benja/Desktop/material/velvet/velvet_result_23/stats.txt", header = TRUE)
+velvet31results <- read.delim("C:/Users/benja/Desktop/material/velvet/velvet_result_31/stats.txt", header = TRUE)
 
 
-#velvetPlots:
-velvet7results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_7/stats.txt", header =TRUE)
-velvet15results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_15/stats.txt", header = TRUE)
-velvet23results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_23/stats.txt", header = TRUE)
-velvet31results <- read.delim("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/material/velvet_result_31/stats.txt", header = TRUE)
+#Soap k-mer Freq => cov
+Soap35mer<- read.table("C:/Users/benja/Desktop/material/SOAP/35soap/35soap.kmerFreq", quote="\"", comment.char="")
+Soap43mer<- read.table("C:/Users/benja/Desktop/material/SOAP/43soap/43soap.kmerFreq", quote="\"", comment.char="")
+Soap45mer<- read.table("C:/Users/benja/Desktop/material/SOAP/45soap/45soap.kmerFreq", quote="\"", comment.char="")
+Soap47mer<- read.table("C:/Users/benja/Desktop/material/SOAP/47soap/47soap.kmerFreq", quote="\"", comment.char="")
[…]

### 2016-01-25 AssignmentX/Assignment10-Ditz_Schroeder-WS15-16.tex
my part is finiiiiiiiiiisched ;)my part is finiiiiiiiiiisched ;)

--- 2016-01-21 AssignmentX/Assignment10-Ditz_Schroeder-WS15-16.tex
@@
 %\usetikzlibrary{automata,arrows}
-\usepackage{subfigure}
+\usepackage{caption}
+\usepackage{units}
+\usepackage{subcaption}
 
@@
 \section*{Practical Assignment - \textit{Assemble the human mitochondrial genome}}
+\subsubsection*{Introduction}
+The mitochondrial genome is rather a small genome in our world.
+But even this rather small genome, with its $10^4$ basepairs is a though nut, when trying to discover its sequence from reads.
+For this purpose we used two different alignment algorithms.
+The Velvet algorithm by Zebrino and Birney is using de Bruijn graphs to assemble the reads.\cite{VelvetProgram}
+Likewise does the short oligonucleotide alignment program (SOAP) denovo2 algorithm by Luo et al.
+use a de Bruijn graph \cite{SOAP2Program}.
+The differences of both algorithms lie in their detailed structure.\\
+The Velvet program starts with building an de Bruijn graph, in which each node has a so called twin node, which represents the reverse complement of the node.
+Both nodes are called block.
+The construction of the de Broijn graph happens via two databases.
+one is a hash table fo r the k-mers, and the second recording the overlaps of the k-mers of a read with other reads.
+Next a simplification step follows.
+After this two construction steps, the Error removal starts.
+The error removing focuses on to three aspects, the removing of tips, bubbles and erroneous connections.
+There are two rules for tip removing, one is the length is smaller than 2k and the other is called minority count.
+The minority count is true, if there is an alternative path, which is more common.
+Bubbles are redundant paths, which are removed via the Tour Bus algorithm.
+The last correction, removing erroneous connections is based on a threshold which is user set.
+\cite{VelvetProgram}
+The SOAP program is structured in six modules, which handle read error correction, de Bruijn graph construction, contig assembly, paired-end reads mapping, scaffold construction and gap closure.
+The de Bruijn graph is since SOAPdenovo2 part of the program.\cite{SOAP2Program} Like velvet, does SOAP use a hash table to build up a de Bruijn graph.\cite{SOAP1Program} But before a correction of the sequencing takes place.
+and afterwards again corrections are applied.
+
+\subsubsection*{Results}
+Both algorithms were used to calculate the assembly of the mitochondrial genome separatly.
+The velvet algorithm was computed on the home source with four different k-mer sizes (from 7 to 31 bases).
+As a result of the lacking hardware and the missing password for the WSI-Server, the resulting data from the SOAP algorithm was thankfully provided by Sanja Koehlers goup.
+The statistics for each algorithm are shown in figure \ref{Velvet-Results} and \ref{SOAP-Results}.
+The for the Velvet program are from the stats.txt and for the SOAP from the XYsoap.contig.
+The coverage was isolated via a java script (see attachment).
+
+\begin{figure}[h]
+	\begin{subfigure}[t] {0.2\textwidth}
+	\includegraphics[width=\textwidth]{exercise2/velvet7kmersCoverage.png}
+	\caption{k-mer size: 7}
+	\label{Velvet-7-mers-coverage}
+	\end{subfigure}
+	\begin{subfigure}[t] {0.2\textwidth}
+		\includegraphics[width=\textwidth]{exercise2/velvet15kmersCoverage.png}
+		\caption{k-mer size: 15}
+		\label{Velvet-15-mers-coverage}
+	\end{subfigure}
+	\begin{subfigure}[t] {0.2\textwidth}
+		\includegraphics[width=\textwidth]{exercise2/velvet23kmersCoverage.png}
+		\caption{k-mer size: 23}
+		\label{Velvet-23-mers-coverage}
+	\end{subfigure}
+	\begin{subfigure}[t] {0.2\textwidth}
+		\includegraphics[width=\textwidth]{exercise2/velvet31kmersCoverage.png}
+		\caption{k-mer size: 31}
+		\label{Velvet-31-mers-coverage}
+	\end{subfigure}
+
+	\caption{The figures show the coverage from the Soap program with differing k-mer size for the mitochondrial DNA assembly.}
+		\label{Velvet-Results}
+\end{figure}
+
+\begin{figure}[h]
+	\begin{subfigure}[t] {0.2\textwidth}
+		\includegraphics[width=\textwidth]{exercise2/Soap35merCoverage.png}
+		\caption{k-mer size: 35}
+		\label{SOAP-25-mers-coverage}
+	\end{subfigure}
+	\begin{subfigure}[t] {0.2\textwidth}
+		\includegraphics[width=\textwidth]{exercise2/Soap43merCoverage.png}
+		\caption{k-mer size: 43}
+		\label{SOAP-43-mers-coverage}
+	\end{subfigure}
+	\begin{subfigure}[t] {0.2\textwidth}
+		\includegraphics[width=\textwidth]{exercise2/Soap45merCoverage.png}
+		\caption{k-mer size: 45}
+		\label{SOAP-45-mers-coverage}
+	\end{subfigure}
+	\begin{subfigure}[t] {0.2\textwidth}
+		\includegraphics[width=\textwidth]{exercise2/Soap47merCoverage.png}
+		\caption{k-mer size: 47}
+		\label{SOAP-47-mers-coverage}
+	\end{subfigure}
+
+	\caption{The figures show the coverage from the Soap program with differing k-mer size for the mitochondrial DNA assembly.}
+		\label{SOAP-Results}
+\end{figure}
+
+\subsubsection*{Discussion}
+The smaller the k-mer the more contigs are the result as it is visible in figure \ref{Velvet-7-mers-coverage}.
+Larger k-mers have as result more unique contigs \cite{VelvetProgram}.
+Generally we can not conclude anything from our results for the quality of the algorithms, because we did not use the same k-mer length.
+But an optimal k-mer size is a compromise between uniqueness of the k-mer (longer) and resulting amount of contigs (shorter).
+
+\subsubsection*{Acknowledgement}
+Thanks again to Sanja Koehler an her group for the SOAP-data.
+
+\begin{thebibliography}{20}
+	\bibitem{VelvetProgram} Velvet: algorithms for de novo short read assembly using de Bruijn graphs. D.R. Zerbino and E. Birney. Genome Research 18:821-829. 
+	\bibitem{SOAP2Program} SOAPdenovo2: an empirically improved memory-efficient short-read de novo assembler. Luo et al. GigaScience 2012 1:18.
+	\bibitem{SOAP1Program}SOAP: short oligonucleotide alignment program" (2008) BIOINFORMATICS,Vol. 24 no.5 2008, pages 713–714 doi:10.1093/bioinformatics/btn025
+
+\end{thebibliography}
 

### 2016-01-25 AssignmentVII/src/Export/ExportFasta.java

@@ -1,112 +1,0 @@
-package Export;
-
-import java.io.BufferedWriter;
-import java.io.File;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.util.ArrayList;
-
-public class ExportFasta {
-	private ArrayList<String>[] set;
-	private String name1;
-	private String name2;
-	private String motif;
-	private int[][] pos;
-	
-	public ExportFasta(ArrayList<String>[] set, int[][] pos, ArrayList<String> m, String outPath, int l, int d){
-	this.set=set;	
-	this.name1 = outPath+"_marked";
-	this.name2 = outPath;
-	this.motif=m.toString();
-	this.pos=pos;
-	
-	File output1=null;
-	File output2=null;
-	boolean alreadyExists=true;
-	int i=1;
-	
-
-	while(alreadyExists){
-		output1 = new File(name1);
-		output2 = new File(name2);
-		if(!output1.exists()){
-
-			alreadyExists=false;
-		}
-		else{
-			name1=outPath+"_marked_"+i;
-			name2=outPath+i;
-			i++;
-		}
-	}
-	name1= name1+".txt";
-	name2= name2+".fasta";
-	try {
-		output1.createNewFile();
-		FileWriter fw= new FileWriter(output1.getAbsoluteFile());
-		BufferedWriter bw = new BufferedWriter(fw);
-		
-		String fileHeader= ";Here are "+set.length+" random Sequences with a planted Motif \n "
-				+ ";Motif Base: "+motif+"\n"
-				+ "; Motif was with a length of: "+l+" and possible deviations up to: "+d;
-		String seqHeader;
-		String sequence;
-		
-		bw.newLine();
-		bw.write(fileHeader);
-		bw.newLine();
-		
-		for(i=0; i<set.length; i++){
-			seqHeader= ">Sequence "+i+" Motif was entered from "+pos[i][0]+" to "+pos[i][1];
-			sequence= set[i].toString();
-			sequence = sequence.substring(1, sequence.length()-1);
-			sequence= sequence.replaceAll("\\,", "");
-			sequence= sequence.replaceAll("\\s+", "");
-			sequence= sequence.trim();
-
-			bw.write(seqHeader);
-			bw.newLine();
-			bw.write(sequence);
-			bw.newLine();
-		}
-		bw.close();
-		
-		
-		//Real Fasta File!
-		output2.createNewFile();
[…]

### 2016-01-25 AssignmentX/exercise2/R-script.R

@@ -1,6 +1,7 @@
 wd<-"C:/Users/benja/Desktop/material"
 setwd(wd)
 library(plotrix)
+x<-t(t(seq(1, 23)))
 
 #velvet coverage
 velvet7results <- read.delim(c(wd,"/velvet/velvet_result_7/stats.txt"), header =TRUE)
@@ -10,18 +11,14 @@ velvet31results <- read.delim("C:/Users/benja/Desktop/material/velvet/velvet_res
 
 
 #Soap k-mer Freq => cov
-Soap35mer<- read.table("C:/Users/benja/Desktop/material/SOAP/35soap/35soap.kmerFreq", quote="\"", comment.char="")
-Soap43mer<- read.table("C:/Users/benja/Desktop/material/SOAP/43soap/43soap.kmerFreq", quote="\"", comment.char="")
-Soap45mer<- read.table("C:/Users/benja/Desktop/material/SOAP/45soap/45soap.kmerFreq", quote="\"", comment.char="")
-Soap47mer<- read.table("C:/Users/benja/Desktop/material/SOAP/47soap/47soap.kmerFreq", quote="\"", comment.char="")
-Soap55mer<- read.table("C:/Users/benja/Desktop/material/SOAP/55soap/55soap.kmerFreq", quote="\"", comment.char="")
+Soap35mer<- read.table("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/35soap-cov.csv", quote="\"", comment.char="")
+Soap43mer<- read.table("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/43soap-cov.csv", quote="\"", comment.char="")
+Soap45mer<- read.table("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/45soap-cov.csv", quote="\"", comment.char="")
+Soap47mer<- read.table("C:/Users/benja/Documents/Git/BioinformaticsI-Assigments/AssignmentX/exercise2/47soap-cov.csv", quote="\"", comment.char="")
+
 
 #pictures SOAP
-barplot(Soap35mer$V1[1:23], main="K-mer Frequencies - Soap - 35mers")
-barplot(Soap43mer$V1[1:23], main="K-mer Frequencies - Soap - 43mers")
-barplot(Soap45mer$V1[1:23], main="K-mer Frequencies - Soap - 45mers")
[…]

### 2016-01-28 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
the laaaaaaaaast one

--- 2016-01-21 AssignmentX/Assignment10-Ditz_Schroeder-WS15-16.tex
@@
   \begin{vartab}{\thecolmns}
-    \numbers{#1} & $\sum$ (10)\\\hline
+    \numbers{#1} & $\sum$ (6)\\\hline
     \emptyLine{\thecolmns}\\
@@
 %\header{Blatt}{Tutor}{Abgabedatum}{Vorlesung}{Bearbeiter}{Semester}{Anzahl Aufgaben}
-\header{10}{Alexander Seitz}{18. January 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{2}
+\header{11}{Alexander Seitz}{1. Februar 2016}{Bioinformatics I}{\\Jonas Ditz \\\& Benjamin Schroeder}{WS 15/16}{3}
 
-\section*{Theoretical Assignment - \textit{Assembly using de Bruijn graph}}
+\section{Coverage statistics}
+\subsection{title}
+\subsection{title}
+\subsection{title}
+\section{Application of the arrival statistic for unitigs}
 
-The de Bruijn graph for the reads provided on the assignment sheet would look like the graph in
-Figure \ref{fig:4mere}, if one chooses $k = 4$. As one can see easily, there are not just one but 
-four different Eulerian paths in the graph. Each path results in one of the following superstring:
+\section{On distances}
+\subsection{title}
+\subsection{title}
+\begin{thebibliography}{20}
 
-\begin{align}
- S_1 &= ACCGTTAACGTAAACGT \nonumber \\
- S_2 &= ACCGTAAACGTTAACGT \nonumber \\
- S_3 &= ACCGTTAAACGTAACGT \nonumber \\
- S_4 &= ACCGTAACGTTAAACGT \nonumber
-\end{align}
-
-This happens due to the fact that there are nodes with more than one outgoing an incoming edge. If
-one chooses $k = 5$ the resulting de Bruijn graph would look like the graph in Figure \ref{fig:5mere}.
-It is obvious that the number of nodes is depended on $k$. With a bigger $k$ there are more nodes in 
-the resulting de Bruijn graph. The resulting graph for $k = 5$ is non-connected. So the superstring 
-for this graph is not just one but three strings:
-
-\begin{align}
- S_{part_1} &= TAAACTG \nonumber \\
- S_{part_2} &= CGTAACGTTAA \nonumber \\
- S_{part_3} &= ACCGT \nonumber
-\end{align}
-
-One can see that $S_{part_1} = f_5$ and $S_{part_3} = f_1$, while $S_{part_2}$ is the result of an 
-overlap alignment between $f_2$, $f_3$ and $f_4$. In general the second graph is more realistic. 
-It is very unlikely to get a connected graph with real-life data. So it is possible that just $f_2$, 
-$f_3$ and $f_4$ come from the same area in the target DNA. $f_1$ and $f_5$ could come from a different 
-contig and, hence, result in this graph (Figure \ref{fig:5mere}). Since this is a minimal example 
-the first graph (Figure \ref{fig:4mere}) is not wrong but one should not expect to get a connected 
-graph all the time. In fact a connected graph is suspicious, normally.
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=1\textwidth]{deBruijnGraph_4mere.png}
- \caption{De Bruijn graph for the given reads and $k = 4$.}
- \label{fig:4mere}
-\end{figure}
-
-\begin{figure}[h]
- \centering
- \includegraphics[width=1\textwidth]{deBruijnGraph_5mere.png}
- \caption{De Bruijn graph for the given reads and $k = 5$.}
- \label{fig:5mere}
-\end{figure}
-
-\section*{Practical Assignment - \textit{Assemble the human mitochondrial genome}}
+\end{thebibliography}
 

### 2016-01-28 AssignmentX/exercise2/R-script.R

@@ -57,17 +57,17 @@ dev.off()
 #pictures SOAP
 
 png("Soap35merCoverage.png")
-velvet7Hist <- hist(as.double(Soap35mer$V1), ylim=range(0,100), breaks=145, main="coverage for 7 k-mers")
+hist(as.double(Soap35mer$V1), ylim=range(0,100), breaks=145, main="coverage for 35 k-mers")
 dev.off()
 
 png("Soap43merCoverage.png")
-velvet7Hist <- hist(as.double(Soap35mer$V1), ylim=range(0,100), breaks=145, main="coverage for 7 k-mers")
+hist(as.double(Soap43mer$V1), ylim=range(0,100), breaks=8, main="coverage for 43 k-mers")
 dev.off()
 
 png("Soap45merCoverage.png")
-velvet7Hist <- hist(as.double(Soap35mer$V1), ylim=range(0,100), breaks=145, main="coverage for 7 k-mers")
+hist(as.double(Soap45mer$V1), ylim=range(0,100), breaks=8, main="coverage for 45 k-mers")
 dev.off()
 
 png("Soap47merCoverage.png")
-velvet7Hist <- hist(as.double(Soap35mer$V1), ylim=range(0,100), breaks=145, main="coverage for 7 k-mers")
+ hist(as.double(Soap47mer$V1), ylim=range(0,100), breaks=8, main="coverage for 47 k-mers")
 dev.off()

### 2016-01-28 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
aufgabe 3 a ist fertig

@@
 \usepackage{amsmath}
+\usepackage{amssymb}
 \usepackage{hyperref}
@@
   \begin{vartab}{\thecolmns}
-    \numbers{#1} & $\sum$ (6)\\\hline
+    \numbers{#1} & $\sum$ (7)\\\hline
     \emptyLine{\thecolmns}\\
@@
 
-\section{Coverage statistics}
+\section{Theoretical Assignment - \textit{Coverage statistics}}
+\subsection{}
+\subsection{}
+\subsection{}
+\section{Theoretical Assignment - \textit{Application of the arrival statistic for unitigs}}
+
+\section{Theoretical Assignment - \textit{On distances}}
 \subsection{title}
-\subsection{title}
-\subsection{title}
-\section{Application of the arrival statistic for unitigs}
 
-\section{On distances}
-\subsection{title}
-\subsection{title}
+Consider a tree $T$ constructed with $D$ and the four nodes $i,j,k,l \in T$. Since $D$ is ultrametric, 
+the following four inequalities have to hold:
+\begin{align}
+ d(i,j) &\le max \left\lbrace d(i,k), d(j,k) \right\rbrace \nonumber \\
+ d(i,j) &\le max \left\lbrace d(i,l), d(j,l) \right\rbrace \nonumber \\
+ d(k,l) &\le max \left\lbrace d(i,k), d(i,l) \right\rbrace \nonumber \\
+ d(k,l) &\le max \left\lbrace d(j,k), d(j,l) \right\rbrace \nonumber
+\end{align}
+W.l.o.g we can assume that $d(i,k) = d(j,k) = d(i,l) = d(j,l)$. With that assumption we can rewrite 
+the inequalities as
+\begin{align}
+ d(i,j) + d(i,j) &\le d(i,k) + d(j,l) \nonumber \\
+ d(k,l) + d(k,l) &\le d(i,l) + d(j,k) \nonumber
+\end{align}
+And also the following inequality is valid:
+\begin{equation}
+ d(i,j) + d(k,l) \le max \left\lbrace d(i,k) + d(j,l), d(i,l) + d(j,k) \right\rbrace \nonumber
+\end{equation}
+As one can see, that is the Four-Point-Condition (4PC) and a metric fulfill 4PC if and only if it is 
+additive. So $D$ is a tree metric $\square$
+
+To show the back direction one consider the four elements $A, B, C, D \in X$ of a taxa $X$ and the 
+following distance matrix:
+\begin{equation}
+ D = \begin{bmatrix}
+        & B & C & D \\
+      A & 7 & 6 & 5 \\
+      B &   & 3 & 6 \\
+      C &   &   & 5
+     \end{bmatrix} \nonumber
+\end{equation}
+One can see in the script of this lecture that $D$ is a tree metric. But the Three-Point-Condition 
+(3PC) is not fulfilled as can be easily shown. To fulfill 3PC the following inequality has to be 
+valid:
+\begin{equation}
+ d(A,B) \le max \left\lbrace d(A,C), d(B,C) \right\rbrace \nonumber
+\end{equation}
+but
+\begin{equation}
+ 7 \nleq max \left\lbrace 6, 3  \right\rbrace \nonumber
+\end{equation}
+So $D$ does not fulfill 3PC and thus $D$ is not ultra metric. $\square$
+
+\subsection{}
+
 \begin{thebibliography}{20}

### 2016-01-29 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
aufgabe 3 ist fertig

@@
 \renewcommand{\baselinestretch}{1.3}\normalsize
+\renewcommand{\thesubsection}{\thesection\alph{subsection}}
 
@@
 \section{Theoretical Assignment - \textit{On distances}}
-\subsection{title}
+\subsection{}
 
@@
 
-\begin{thebibliography}{20}
+\begin{figure}[t]
+ \centering
+ \includegraphics[width=0.6\textwidth]{exec3bFigure.png}
+ \caption{Behavior of observed distance $p$ and expected genetic distance $d$ of two non-saturated sequences. Both sequences are of length 200.}
+ \label{fig:pdRelationship}
+\end{figure}
 
-\end{thebibliography}
+There are different methods to estimate the (evolutionary) distance between two sequences. The easiest 
+one is to simply calculate the Hamming distance. This is called the observed or $p$-distance. $p$-distance 
+is just suitable for closely related species, since it is not able to detect superimposed mutations, i.e. 
+mutations that happened at a position that was already mutated, previously. A correction for observed 
+distance was formulated by Jukes and Cantor. The Jukes-Cantor transformation corrects the $p$-distance 
+to take, among others, superimposed events into account. This correct distance is called the expected 
+genetic distance $d$. An important note is that JC transformation does 
+not work for sequences that are saturated w.r.t. each other. So Figure \ref{fig:pdRelationship} shows 
+the relationship between $d$ and $p$ for non-saturated sequences of length 200. As one can see the 
+observed distance $p$ is constantly underestimating the genetic distance for more distant sequences. 
+Especially, if both sequences are close to be saturated, the difference between $d$ and $p$ shows 
+that $p$ cannot give a reliable result. So for sequences/species that are evolutionary close to each 
+other both measurements $d$ and $p$ give almost the same result. But the further away the last common 
+ancestor of both sequences the larger is the difference between observed distance and expected genetic 
+distance.
+
+%\begin{thebibliography}{20}
+%	
+%\end{thebibliography}
 

### 2016-01-29 AssignmentXI/exercise3b.py

@@ -33,7 +33,7 @@ if __name__ == '__main__':
 
   plt.plot(t, ham, 'bs', label='observed distance p')
   plt.plot(t, jc, 'g^', label='expected genetic distance d')
-  plt.xlabel('difference of two sequences')
+  plt.xlabel('number of differences between two sequences')
   plt.ylabel('distance')
   plt.legend(loc='best')
   plt.show()

### 2016-01-30 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
aufgabe 2 ist fertig

@@
 
+The probability whether a unitig is unique can be done with a formula derived from the Lander-Waterman 
+model for shotgun sequencing. This formula is
+\begin{equation}
+ \frac{e^{-c} c^k}{k!}\text{, with } c = \frac{\rho R}{L} \nonumber
+\end{equation}
+for non-oversampled unitigs and
+\begin{equation}
+ \frac{e^{-2c} (2c)^k}{k!} \nonumber
+\end{equation}
+for unitigs that are the result of collapsing two repeats. In these formulas $R$ is the number of reads, $L$ is the length 
+of target sequence, $\rho$ is the length of the unitig and $k$ is the number of reads contained by the 
+unitig.
+
+In this task we consider a source sequence of length $L = 2Mb$ and $R = 22000$ reads. The length of 
+the unitig is $\rho = 3000bp$ and it consists of $k = 100$ reads. With the formulas mentioned above, the 
+probability of this specific unitig to be unique is
+\begin{equation}
+ \frac{e^{-\frac{3000 \cdot 22000}{3000000}} \cdot (\frac{3000 \cdot 22000}{3000000})^{100}}{100!} \approx 5.221 \cdot 10^{-34} \nonumber
+\end{equation}
+for the case that our unitig is not oversampled and 
+\begin{equation}
+ \frac{e^{-2\frac{3000 \cdot 22000}{3000000}} \cdot (2\frac{3000 \cdot 22000}{3000000})^{100}}{100!} \approx 1.846 \cdot 10^{-13} \nonumber
+\end{equation}
+for the case that our unitig is the result of collapsing to repeats.
+
 \section{Theoretical Assignment - \textit{On distances}}

### 2016-02-01 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
number 1

@@
 \section{Theoretical Assignment - \textit{Coverage statistics}}
+\subsection{fraction sequenced}
+The used equation is from the script(equation \ref{fraction}.\\	
+	\begin{eqnarray}
+		f=1-e^{-c} \label{fraction}\\
+	\end{eqnarray}
+\\	
+As a result of using the given coverages $c=1,2,4,8, 14$, table \ref{fractionsTable} is deduced.
+The last column shows the bases which are not covered when the sequence length is  $L= 248956422 bp$ like in the human chromosome 1.
+\\
+\begin{tabular}{|c|c|c|c|}
+	\hline coverage & fraction covered f & fraction not covered & bases not covered [bp] \\ 
+	\hline 1 & 0.63212 & 0.36788 & 91586089 \\ 
+	\hline 2 & 0.86466 & 0.13534 & 33693762 \\ 
+	\hline 4 & 0.98168 & 0.01832 & 4650882 \\ 
+	\hline 8 & 0.99966 & 0.00034 & 84645 \\ 
+	\hline 14 & 0.99995 & 0.00005 & 12448 \\ 
+	\hline 
+	\label{fractionsTable}
+\end{tabular} 
+\\
+The Treponema pallidum chromosome has a length of 1,139,633 bp.
+If now less than one base can be missed, the not covered fraction is $\leq\frac{1}{1,139,633} =7.16*10^{-6}$.
+This results in a positive fraction of at least 0.999993.
+The coverage is determined with the transformed equation \ref{transformedEquation1} and has a value of 11.87.
+\\
+\begin{equation}
+c=-ln(1-f)
+\label{transformedEquation1}
+\end{equation}
+\\
+\subsection{times sequenced}
+If there is a coverage of $c=10$, a base has been exactly been sequenced three times with a probability p(3)=0.015 according to the poisson distribution (equation \ref{pois}).
+\\
+\begin{equation}
+p(x)=\frac{c^x}{x!} e^{-c} \label{pois}
+\end{equation}
+\begin{equation}
+p(x)=\frac{10^3}{3!} e^{-10} = 0.015
+\end{equation}
+The next question was at most three times covered. This can be calculated with equation \ref{poisD}. F(3) has a value of $F(3)=0.018$.
+
+\begin{equation}
+	F(n)= \sum_{x=0}^{3} p(x) \label{poisD}	
+\end{equation}
+\begin{equation}
+	F(3)= \frac{10^0}{0!}*e^{-10}+\frac{10^1}{1!}*e^{-10}+\frac{10^2}{2!}*e^{-10}+\frac{10^3}{3!}*e^{-10} = 0.018 \label{poisD}	
+\end{equation}
+\\
 \subsection{}
-\subsection{}
-\subsection{}
+expected number of gaps
+mean contig size
+\\
 \section{Theoretical Assignment - \textit{Application of the arrival statistic for unitigs}}
